### 2020-06-26 abstract.tex
Initial Overleaf Import

\begin{abstract}
The development of cyber-physical systems (CPS) is challenging due to the heterogeneity of the different subsystems. To assist in the development process, co-simulation can be used, where models of constituents of a CPS are coupled to jointly simulate the behavior of the full system. However, a trustworthy result of the co-simulation is only obtained if all of the simulation units are initialized correctly and in the correct order. In this work, we consider co-simulation where the simulation units are described as Functional Mock-up Units (FMU). The Functional Mock-up Interface specification specifies constraints to the initialization of variables in the scope of a single FMU. However, it does not consider the initialization of interconnected variables between instances of FMUs. Such interconnected variables place particular constraints on the initialization order of the FMUs.\\
The approach taken to calculate a correct initialization order is based on predicates from the specification and the topological ordering of both internal connections and interconnected variables. Circular dependencies between FMU variables are dismissed. %This approach has been compared to other already existing approaches for FMI initialization. 
The approach has been realized as a plugin for the open-source INTO-CPS Maestro 2 Co-simulation framework. It has been tested for various scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial application. The approach has also been directly tested against an established co-simulation algorithm generator implemented in Prolog.

\keywords{Co-simulation \and Initialization \and Topological ordering \and FMI}
\end{abstract}

%The correct initialization of a co-simulation depends not only on the value being assigned to each port but also the order in which the ports are initialized.

### 2020-06-26 conclusion.tex
Initial Overleaf Import

\section{Concluding remarks}\label{sc:summary}
This work used a topological ordering based on the interconnected FMUs variable and internal FMU variable connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario. The calculated initialization order is optimized to group similar variables to perform fewest possible operations.
This approach ensures absence of cycles between interconnected FMU variables by defining the criteria for valid co-simulation scenarios.
This approach can be combined with an arbitrary master algorithm to run the co-simulation. \\
The approach was realized as a plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation algorithm generator and verifier implemented in Prolog using an integration.\\
Future work includes formally verifying the plugin, and its implementation of the algorithm used to calculate the topological ordering using the Logika framework.
Future work will also look into generation of a verification strategy for the whole Maestro 2 framework to explore how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.

\paragraph*{\textbf{Acknowlegements.}}We would like to thank Stefan Hallerstede, Peter Gorm Larsen and Claudio Gomes for providing valuable input to this paper and the developed plugin.

### 2020-06-26 introduction.tex
Initial Overleaf Import

\section{Introduction}\label{sc:introduction}
Cyber-physical systems (CPS) are becoming ever more sophisticated, while market pressure shortens the available development time. One of the tools used to manage the increasing complexity of such systems is co-simulation since it addresses their various parts of heterogeneous nature. Co-simulation is a technique to combine multiple black-box simulation units to simulate/compute the behavior of the combined models as a discrete trace\cite{Kubler2000}. The simulation units, often developed independently from each other, are coupled using a master algorithm, also often developed independently,
that communicates with each simulation unit via its interface. This interface comprises functions for setting/getting inputs/outputs, and computing the associated model behavior over a given interval of time. \\
The Functional Mock-up Interface (FMI) standard \cite{Blochwitz2012, fmi_2019} is such an interface describing how to communicate with each simulation unit. This interface can be used to connect different simulation units (called Functional Mock-up Units or FMUs) and exchange values between them and make them progress in time. \\
A typical co-simulation consists of three phases: Initialization, simulation, and teardown. This work concentrates on the first of these phases - the initialization phase. FMI specifies criteria for how an FMU shall be initialized. However, the FMI standard is not concerned with how a connected system of multiple FMUs should be correctly initialized as a whole. 
The way a system of multiple FMUs should be initialized and interacted with depends on each FMUs implementation and interconnections to other FMUs \cite{gomes_lucio_vangheluwe_2019}, since these place precedence constraints between the FMU variables. The precedence constraints make specific system configurations and initialization orders of a system invalid due to cyclic dependencies and dependencies among the interconnected variables. An appropriate order of initialization is vital for the correctness of the co-simulation \cite{Thule2018} because it ensures a variable is never read before it is set like the classical \textit{readers–writers problem}. Circular dependencies are important to avoid in a co-simulation scenario since they reduces the ability of a co-simulation to converge \cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}.\\

This paper describes an approach for the initialization of an FMI-based co-simulation in linear time of the number of interconnected variables. The approach complies with the semantics of FMI and ensures the absence of cycles in the system. The approach does not put any constraints on choosing a master algorithm that should be used to carry out the simulation. This means that the approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobian \cite{Palensky2017}. The approach has been realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2). The realized plugin has been tested for various co-simulation scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial applications. Gomes et al. have created a co-simulation algorithm generator and verifier\cite{gomes_lucio_vangheluwe_2019} in Prolog an integration to this realization has been crated as a part of the plugin. This integration is used to verify the calculated initialization order against an already established method for calculating the initialization order.\\

The paper is structured as follows: Section \ref{sc:background} gives a brief background of the formalization of FMUs and Maestro 2. Section \ref{sc:initilization} describes the approach taken to calculate the initialization order. This is followed by section \ref{sc:implementation}, where the realization of the approach is presented. Finally, section \ref{sc:summary} provides concluding remarks and describes future work.

### 2020-06-26 paper.tex
Initial Overleaf Import

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}

\usepackage{graphicx}
\usepackage{ae,aecompl}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{amstext}
\usepackage{bm} 
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{siunitx}
\usepackage{mathrsfs}
\usepackage{wrapfig}
\usepackage{minted}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{semantic}
\usepackage[dvipsnames]{xcolor}
\usepackage{paralist}
\usepackage{cite}
\usepackage{url}
\usepackage{todonotes}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\input{commands}

\begin{document}
%
\title{An FMI-Based Initialization Plugin for INTO-CPS Maestro 2}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Simon Thrane Hansen\inst{1} \and
Casper Thule\inst{1},
Claudio Gomes \inst{1}}
%
\authorrunning{S. Thrane and C. Thule}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{DIGIT, Department of Engineering, Aarhus University, \email{\{sth, casper.thule\}@eng.au.dk\}}}
%
\maketitle              % typeset the header of the contribution
%

\input{abstract.tex}

\input{introduction.tex}

\section{Background}\label{sc:background}
In this section, we provide a formalization of FMI co-simulation and a short background on INTO-CPS Maestro 2.

\subsection{FMU definitions}
To describe the formalization of FMUs, the vocabulary from Gomes et al\cite{gomes_lucio_vangheluwe_2019, Gomes2018} is adopted. The main definitions of relevance to this paper will be presented, but readers are referred to the original publications for more information. This paper is only concerned with the initialization-phase of a co-simulation. All information about the time of an FMU and master algorithms is of no relevance and will not be discussed in more detail. 
\begin{definition}[FMU]\label{def:fmu}
  An FMU with identifier $c$ is represented by the tuple   
  $$\tuple{\stateset{c}, \inputs{c}, \outputs{c}, \fset{c}, \fget{c}},$$
  where:
  \begin{inparadesc}
    \item $\stateset{c}$ represents the state space;
    \item $\inputs{c}$ and $\outputs{c}$ the set of input and output variables, respectively;
    \item $\fset{c} : \stateset{c} \times \inputs{c} \times \values \to \stateset{c}$ and $\fget{c}: \stateset{c} \times \outputs{c} \to \values$ are functions to set the inputs and get the outputs, respectively (we abstract the set of values that each input/output variable can take as $\values$).
  \end{inparadesc}
\end{definition}

\begin{definition}[Scenario]\label{def:cosim_scenario}
  A scenario is a structure $\tuple{\fmus, \coupling}$ where each identifier $c \in \fmus$ is associated with an FMU, as defined in \ref{def:fmu}, and $\coupling(u)=y$ means that the output $y$ is connected to input $u$.
  Let $\allinputs = \bigcup_{c \in \fmus} \inputs{c}$ and $\alloutputs = \bigcup_{c \in \fmus} \outputs{c}$, then $\coupling : \allinputs \to \alloutputs$.
\end{definition}

The following definitions correspond to the operations that are permitted in the initialization phase of a co-simulation.

\begin{definition}[Step]\label{def:cosim_step}
  Given a scenario $\tuple{\fmus, \coupling}$, a co-simulation step, or just step, is a finite ordered sequence of FMU function calls $\sequence{\functioncall_i}_{i \in \setnat} = \functioncall_0, \functioncall_1, \ldots$ with
  $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}},$
  and $i$ denoting the order of the function call.
\end{definition}

\begin{definition}[Initialization]\label{def:initialization}
  Given a scenario $\tuple{\fmus, \coupling}$, we define the initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ in the same way as a step, with $\initcall_i \in \allfunctioncalls$.
\end{definition}

\begin{definition}[Feed-through]\label{def:feedthrough}
  The input $\inputvar{c} \in \inputs{c}$ feeds through to output $\outputvar{c} \in \outputs{c}$, that is, $(\inputvar{c},\outputvar{c}) \in \feedthrough{c}$, when there exists $v_1, v_2 \in \values$ and $\state{c} \in \stateset{c}$, such that
  $
  \fget{c} (\fset{c}(\state{c}, \inputvar{c}, v_1), \outputvar{c}) \neq \fget{c} (\fset{c}(\state{c}, \inputvar{c}, v_2), \outputvar{c}).
  $
\end{definition}

\begin{figure}
    \centering
    \includegraphics{images/FMU_legendpdf.pdf}
    \caption{FMU representation}
    \label{fig:fmu_legend}
\end{figure}

An FMU can visually be displayed as in Figure \ref{fig:fmu_legend} where a simple co-simulation scenario is shown.

\begin{definition}[Output Computation]\label{def:getout}
The $\fget{c}(\dontcare, \outputvar{c})$ represents the calculation of output $\outputvar{c}$ of $c \in \fmus$. Given a co-simulation state, it checks whether all inputs that feed-through to $\outputvar{c}$ are defined.
\end{definition}

\begin{definition}[Input Computation]\label{def:setin}
The $\fset{c}(\dontcare, \inputvar{c}, \inputV)$ represents the setting of input $\inputvar{c}$  of $c \in \fmus$. Given a co-simulation state, it checks whether all outputs connected to $\inputvar{c}$ are defined.
\end{definition}

\begin{definition}[Interconnected variable]
An interconnected variable v of a co-simulation scenario $\tuple{\fmus, \coupling}$ is defined as $v \in \allinputs \cup \alloutputs$, then $\coupling : \allinputs \to \alloutputs$.
\end{definition}

\subsection{INTO-CPS Maestro 2}\todo{We can have some more in this section - potentially half a page?}
INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}}\cite{thule_maestro2_2019} is an FMI-based co-simulation framework set to supersede Maestro\cite{Maestro}. The philosophy of the framework is to apply plugins to generate co-simulation specifications expressed in the domain specific language called Maestro Base Language (MaBL). Such specifications are then interpreted and executed resolving in the execution of a co-simulation.

\section{Generation of an Initialization Order}\label{sc:initilization}
FMI defines certain information about the initialization order described through different states of a co-simulation. The initialization phase covers the two states (in chronological order):
\begin{itemize}
    \item \textit{Instantiated}
    \item \textit{Initialization Mode}
\end{itemize}
In each of the two states, different groups of FMU variables can be assigned a value. The groups are defined by FMI based on predicates on the characteristics of the variables (\textit{causality}, \textit{initial} and \textit{variability}). These predicates have been extracted and used in the implementation. 
An example of a group is the \textit{INI}-group that consists of FMU variables with $initial = exact\, \lor initial = \,approx $  and $variability \neq constant$. All variables of this group should be set in the \textit{Instantiated}-phase of a co-simulation, and since they have no dependencies/connections to other FMU variables, the order is insignificant. However, all variables of each FMU are group together to perform the fewest possible operations in the initialization. The FMI specification does allow multiple variables of a single FMU to be set in parallel.

In the \textit{Initialization Mode} state, the variables of all FMUs should be defined if no circular dependencies exist. 
The variables with \textit{causality = parameter} of each FMU are set first, and the order of which they are set is again insignificant as they are independent.
Afterwards the interconnected variables should be defined, but as stated by the definitions \ref{def:feedthrough}, \ref{def:getout} and \ref{def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order.

The correct initialization order of these interconnected variables has been calculated using the method described in Gomes et al. \cite{Gomes2019b}. The method is to use a topological ordering as the initialization order. The topological ordering is based on a graph of the interconnected FMU variables and internal connections. 
The calculation of an initialization order can be performed in linear based on the number of both external and internal connections. The calculation should also identify circular dependencies between the interconnected FMU variables since they would invalidate the co-simulation result. This paper's main contribution is to calculate an initialization order of a co-simulation and guarantee absence of cycles in a system being simulated.

\subsection{Structure of the graph}
The graph is constructed based on the interconnected variables and internal connections (feed-through). Each interconnected variable in the system represents a node, and the edges are based on these connections. The edges of this graph represent precedence constraints based on the algebraic dependencies of the interconnected variables. Please see definition \ref{def:initialization_graph} for a formal definition of the graph.

\begin{definition}[Initialization Graph]\label{def:initialization_graph}
  Given a co-simulation scenario $\tuple{\fmus, \coupling}$, and a set of feed-through dependencies $\bigcup_{c \in \fmus} \set{\feedthrough{c}}$, we define the Initialization Graph where each node represents a port $\outputvar{c} \in \outputs{c}$ or $\inputvar{c} \in \inputs{c}$ of some fmu $c \in \fmus$. The edges are created according to the following rules:
  \begin{compactenum}
    \item For each $c \in \fmus$ and $\inputvar{c} \in \inputs{c}$, if $\coupling(\inputvar{c}) = \outputvar{d}$, add an edge $\outputvar{d} -> \inputvar{c}$.
    \item For each $c \in \fmus$ and $(\inputvar{c},\outputvar{c}) \in \feedthrough{c}$, add an edge $\inputvar{c} -> \outputvar{c}$.
  \end{compactenum}
\end{definition}

\noindent As previously stated, a valid initialization order can only be calculated from an Initialization Graph if it does not contain any strongly connected components. This insight can be used to specify for which co-simulation scenarios a correct initialization order can be generated. A valid co-simulation scenario to calculate an initialization order from is defined in definition \ref{def:valid_graph}.

\begin{definition}[Validity criteria for Generation of an Initialization Graph]\label{def:valid_graph}
  The Initialization Graph is valid if the given a co-simulation scenario $\tuple{\fmus, \coupling}$, and a set of feed-through dependencies $\bigcup_{c \in \fmus} \set{\feedthrough{c}}$.
  $\forall c \in \fmus \implies \nexists \inputvar{} \in \inputs{c}, \outputvar{} \in \outputs{c}: (\inputvar{},\outputvar{}) \in \feedthrough{c} \land Path(\outputvar{}, \inputvar{})$\\
  Where Paths is defined as the transitive closure of $Path = L \cup \bigcup_{c \in \fmus} \set{\feedthrough{c}}$
\end{definition}

All co-simulation scenarios satisfying definition \ref{def:valid_graph} is guaranteed to have a valid initialization order.

\subsection{Three Tank Example}
The structure of the Initialization Graph will be described using a small example. 
The example is based on three water tanks that are filled and emptied. The first tank is filled from a source with a valve that may be turned on and off. The outflow of the first tank constitutes the inflow of the second, and so forth. A discrete-event controller monitors the level of the third tank and controls a valve to a drain. When the water level of the tank reaches a particular level (defined in the controller), the controller sends a command to the tank to empty using an exit valve. An illustration of the three water tanks can be seen in Figure \ref{fig:watertank}. A diagram of the FMUs showing the interconnections of the FMU variables in the system can be in Figure \ref{fig:watertank}. It should be noted that all internal connections that do not \textit{feed-through} have been omitted to simplify the diagram since they do not influence the initialization order and are not included in the graph defined in definition \ref{def:initialization_graph}.

\begin{figure}[H]
    \begin{minipage}{0.40\textwidth}
    \centering
        \centering
    \includegraphics[width=1\textwidth]{images/ttwt_overview.pdf}
    \end{minipage}
    \begin{minipage}{0.60\textwidth}
        \centering
    \includegraphics[width=1\textwidth]{images/threetank_FMU.pdf}
    \end{minipage}
    \caption{Three tank case study}
    \label{fig:watertank}
\end{figure}

\noindent A correct initialization order can be calculated since there are no circular dependencies in the system, the Initialization Graph is valid based on definition \ref{def:valid_graph}. The corresponding Initialization Graph of the three tank system can be seen in figure \ref{fig:initilizationGraph}. As it can be seen from the Initialization Graph, it is a disconnected graph meaning there are no limitations on the order of the initialization between the two sub-graphs. Nevertheless, in this case, an optimization of the initialization order can be made, using the fact that the FMI specification allows the set/get variables of the same FMU to be performed in bulk. This optimization can be made by setting the two inputs of \textit{T2} simultaneously (by the same operation). The definition of the optimization can be found in definition \ref{def:optimization}.
It is not challenging to calculate the initialization order in this simple example. However, knowledge about the internal connections of each FMU is needed in order to calculate the initialization order due to \textit{feed-through} in FMU \textit{T2}. The strategy for calculating the initialization order scales to more advanced systems with an arbitrary number of FMUs and interconnected variables. Furthermore, an initialization order can be found as long a the Initialization Graph satisfies the criteria of definition \ref{def:valid_graph}.

\begin{figure}
    \centering
      \includegraphics[width=0.95\textwidth]{images/threetank_initialization.pdf}
    \caption{Initialization Graph of three tank}
  \label{fig:initilizationGraph}
\end{figure}

\begin{definition}[Optimization of a Initialization procedure]\label{def:optimization}
  Given an initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ with a finite ordered sequence of FMU function calls $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}},$ and $i$ denoting the order of the function call. It can be optimized if $\exists \functioncall_i, \functioncall_{i +1} \in \allfunctioncalls : \exists c \in \fmus :(\functioncall_i \in {\fset{c}} \land \functioncall_{i+1} \in {\fset{c}}) \lor (\functioncall_i \in {\fget{c}} \land \functioncall_{i+1} \in {\fget{c}})$
\end{definition}
This optimization uses the fact that the FMI specification allows to \textit{set} or \textit{get} variables of the same FMU to be performed in bulk by grouping interconnected variables of the same FMU with others with similar characteristic.
Since an Initialization procedure is defined in the same they as other co-simulation steps. The optimization process described in definition \ref{def:optimization} is valid for an arbitrary co-simulation step. The only difference between an arbitrary co-simulation step and an initialization procedure is the size of the graph on which the topological sorting is performed. 
The correctness of this optimization can be established by the proof of using the Initialization Graph's topological ordering as the initialization order described by Gomes et al. This proof is still valid since this optimization does not change the structure of the Initialization Graph. 
This optimization strategy potentially will not find all valid optimizations of a co-simulation scenario since it works on a co-simulation step (a topological order of a graph), which is not necessarily unique for a given co-simulation scenario/graph. To perform all possible optimizations of a co-simulation step, a more advanced optimization strategy should be used, or the optimization should be performed on the set of all valid co-simulation steps.

\section{Realization of a Maestro 2 Plugin}\label{sc:implementation}
This approach has been realized as a Maestro 2 plugin that generates the \textit{Initialization}-phase of a co-simulation specification expressed in MaBL. It calculates the specification based on a list of FMU-components, the simulation scenario as defined in definition \ref{def:cosim_scenario}, and a specific plugin-configuration to let the user supply initial values of FMU variables with $causality=parameter$. The plugin optimizes the initialization order of the initialization by grouping operations that can be executed in \textit{parallel} to take advantage of FMI's ability to set or get multiple variables in bulk from the same FMU. The criteria for this optimization is defined in definition \ref{def:optimization}. 
The developed plugin has been tested on numerous co-simulation examples from the INTO-CPS universe\todo{should I add a footnote} and compared with the existing \textit{Initializer} of Maestro. The plugin has been tested in the whole Maestro 2 pipeline to practically verify that it can be used in a co-simulation where the generated initialization procedure is integrated as a part of a complete co-simulation to verify the initialization procedure's integration with a master algorithm.

\subsection{Topological sorting}
The algorithm for calculating the topological order of the Initialization Graph defined in definition \ref{def:initialization_graph} is Tarjan's algorithm\cite{tarjan_1972}. The algorithm was selected since it solves two of the central issues of the initialization-phase of the co-simulation.
\begin{itemize}
    \item Identifies circular dependencies between interconnected variables (strongly connected components)
    \item Performs a topological sorting of the Initialization Graph
\end{itemize}
The algorithm is furthermore well-established, and there exist formal proofs of its correctness and properties\cite{stefan_merz}.

The topological sorting algorithm was implemented in Scala. The choice of Scala is motivated by the relation to JVM and the connection to Slang and the Logika framework\cite{inbook}. The connection to Slang and Logika will be used in the future work of formally verifying the plugin and explore how the contract-based nature of Slang can be used to obtain more trustworthy results of co-simulations.

\subsection{Verification of the approach}
The plugin and the approach behind it have been verified in several different ways. Gomes et al. have in \cite{gomes_lucio_vangheluwe_2019} proved the correctness of using the topological order of a similar graph to generate not only the initialization order but also the order for a co-simulation master-algorithm. The purpose of the publication by Gomes et al. is a little different from the one of this paper. Gomes et al. are interested in both generating an initialization and master-algorithm, meaning they also need to focus on the time of each FMU. They also define their graph using methods (Set, Get, doStep) instead of interconnected variables, which is the approach described in this paper. This simplification is valid since this approach only cares about initialization and, therefore, does not need to care about the time of each FMU. This does that we can omit all the $doStep$ nodes and all edges connected to them from the graph by Gomes et al., this approach does, therefore, end up with a subgraph of the graph by Gomes et al. The proof from \cite{gomes_lucio_vangheluwe_2019} can therefore trivial be modified to the graph/approach presented in this paper.

The main contribution of Gomes et al. is an implementation of the FMI specification in Prolog freely available to be used in other projects. The Prolog implementation was used in their research to verify their proposed approach for generation of co-simulation algorithms. The realization encapsulates all the rules of a valid master-algorithm and an initialization algorithm. As a part of this work, integration from the plugin has been created to the Prolog realization. This integration has been realized in order to verify the correctness of the calculated initialization order against an established and recognized method. The integration is based on JIProlog\cite{}, and it is querying the Prolog database with a co-simulation environment and an initialization order. The integration requires substantially mapping of the objects between the Java code of Maestro 2 and the Prolog implementation, and due to the described differences between the two graphs a mapping from the graph of ports to the graph of operations is needed. This mapping is based on the definitions \ref{def:getout} and \ref{def:setin}.

The Prolog code can generate an initialization order, but this functionality haven't been used for several reasons. The main reason for not generating the initialization order using the Prolog code is based on performance considerations, and the approach taken in this paper does also ensure absence of circular dependencies between the interconnected FMU variables.

\section{Related Work}
Gomes et al. \cite{Gomes2019} propose a strategy for the generation of co-simulation algorithms for FMI-based scenarios based on a graph of the operations of a co-simulation step. However, there are some key differences between their work and ours since the method they purpose does not handle algebraic loops. Furthermore, the approach taken in this paper is only concerned with the initialization procedure of a co-simulation.

The requirement of freedom of algebraic loops of FMI-based co-simulation scenarios to obtain a deterministic composition result of a co-simulation master algorithm was required by Broman et al. \cite{BromanCompositionCo-Simulation}. They proposed to use the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of a co-simulation step. This insight

Prior work by Amalio et al. \cite{Amalio2016CheckingCo-simulation} has been investigating how to ensure the absence of algebraic loops in FMU based co-simulation scenarios by statically checking the SysML CPS architectural design. The publication's purpose is partly very similar to ours - to guarantee the absence of algebraic loops in a co-simulation scenario. Nevertheless, their approach is only concerned with ensuring the absence of algebraic-loops since their approach is analyzing an architecture design; the calculation of the initialization order is of no interest.

\input{conclusion.tex}
%
% ---- Bibliography ---

\bibliographystyle{splncs04}
\bibliography{gen_bib}

\end{document}

### 2020-06-28 introduction.tex
Update

@@
 The way a system of multiple FMUs should be initialized and interacted with depends on each FMUs implementation and interconnections to other FMUs \cite{gomes_lucio_vangheluwe_2019}, since these place precedence constraints between the FMU variables.
-The precedence constraints make specific system configurations and initialization orders of a system invalid due to cyclic dependencies and dependencies among the interconnected variables.
-An appropriate order of initialization is vital for the correctness of the co-simulation \cite{Thule2018} because it ensures a variable is never read before it is set like the classical \textit{readers–writers problem}.
-Circular dependencies are important to avoid in a co-simulation scenario since they reduces the ability of a co-simulation to converge \cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}.\\
+The precedence constraints between the variables can introduce algebraic loops, which places particular requirements on the initialization order since the algebraic loops require a particular initialization strategy to be applied to calculate the initial values.
+The order of initialization is vital for the correctness of the co-simulation \cite{Thule2018} because it ensures a variable is never read before it is set like the classical \textit{readers–writers problem} and to make sure that all initial values have stabilized at the start of the simulation.
+Circular dependencies (Algebraic loops) occurs whenever there is an interconnected FMU variable that indirectly depends on itself.
+Algebraic loops introduce specific challenges in the co-simulation, and studies have shown that neglecting a loop can lead to a prohibitively high error in the co-simulation \cite{Kubler2000}.
+Other approaches for the generation of co-simulation have avoided co-simulation scenarios containing algebraic loops since they reduce the ability of co-simulation to converge \cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}.
+However, experience has shown that valid co-simulation scenarios containing algebraic loops exist, and a well-established co-simulation framework should be able to handle them.
+In this work, fixed point iteration techniques have been investigated to initialize scenarios containing algebraic loops properly.
+The technique is to repeat the evaluation of the output functions of the interconnected variables in each algebraic loop until convergence\cite{Gomes2018}.\\
 
-This paper describes an approach for the initialization of an FMI-based co-simulation in linear time of the number of interconnected variables.
-The approach complies with the semantics of FMI and ensures the absence of cycles in the system.
+This paper describes an approach for calculating the initialization order of an FMI-based co-simulation in linear time of the number of interconnected variables.
+The approach complies with the semantics of FMI and support the initialization of algebraic loops between interconnected FMU variables and ensure convergence of these variables.
 The approach does not put any constraints on choosing a master algorithm that should be used to carry out the simulation.
@@
 Gomes et al.
-have created a co-simulation algorithm generator and verifier\cite{gomes_lucio_vangheluwe_2019} in Prolog an integration to this realization has been crated as a part of the plugin.
+have created a co-simulation algorithm generator and verifier\cite{gomes_lucio_vangheluwe_2019} in Prolog, and an integration to this realization has been created as a part of the work.
 This integration is used to verify the calculated initialization order against an already established method for calculating the initialization order.\\

### 2020-06-28 paper.tex
Update

@@
 \author{Simon Thrane Hansen\inst{1} \and
-Casper Thule\inst{1},
+Casper Thule\inst{1} \and
 Claudio Gomes \inst{1}}
@@
 All information about the time of an FMU and master algorithms is of no relevance and will not be discussed in more detail.
+The formalization from Gomes et al. is also extended with some new definitions regarding algrebraic loops, and 
 \begin{definition}[FMU]\label{def:fmu}
@@
 
+\begin{definition}[Algebraic loops]\todo{Create this definition}
+An interconnected variable v of a co-simulation scenario $\tuple{\fmus, \coupling}$ is defined as $v \in \allinputs \cup \alloutputs$, then $\coupling : \allinputs \to \alloutputs$.
+\end{definition}
+
+\begin{definition}[Fixed point iteration]\todo{Create this definition}
+An interconnected variable v of a co-simulation scenario $\tuple{\fmus, \coupling}$ is defined as $v \in \allinputs \cup \alloutputs$, then $\coupling : \allinputs \to \alloutputs$.
+\end{definition}
+
 \subsection{INTO-CPS Maestro 2}\todo{We can have some more in this section - potentially half a page?}
@@
 Afterwards the interconnected variables should be defined, but as stated by the definitions \ref{def:feedthrough}, \ref{def:getout} and \ref{def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order.
+And an algebraic loop in a co-simulation scenario places even more criteria on the initialization order.
 
-The correct initialization order of these interconnected variables has been calculated using the method described in Gomes et al.
-\cite{Gomes2019b}.
-The method is to use a topological ordering as the initialization order.
-The topological ordering is based on a graph of the interconnected FMU variables and internal connections.
-The calculation of an initialization order can be performed in linear based on the number of both external and internal connections.
-The calculation should also identify circular dependencies between the interconnected FMU variables since they would invalidate the co-simulation result.
-This paper's main contribution is to calculate an initialization order of a co-simulation and guarantee absence of cycles in a system being simulated.
+\subsection{Method}
+The approach to calculate the initialization order of the interconnected FMU variables are based on the the method proposed in Gomes et al.
+\cite{Gomes2019b, BromanCompositionCo-Simulation}, but the approach used here has been extended with the ability to handle algebraic loops.
 
-\subsection{Structure of the graph}
-The graph is constructed based on the interconnected variables and internal connections (feed-through).
+\subsubsection{Structure of the graph}
+The initialization algorithm starts by building a directed graph of the dependency among the interconnected variables of the FMUs, The graph is constructed based on the interconnected variables and internal connections (feed-through).
 Each interconnected variable in the system represents a node, and the edges are based on these connections.
@@
 
+\subsubsection{Calculation of a initialization order}
+The topological ordering of a the graph defined in definition \ref{def:initialization_graph} is used a as the initialization order of the interconnected FMU variables.
+The elements of the topological order is the strongly connected components of the graphs.
+The strongly connected components are potentially algebraic loops of the system.
+The algebraic loops is easily identified as the strongly connected components containing more than a single element.
+The single element members of the topological order is normally interconnected FMU variables, whose value should only be calculated once during the initialization.
+\\
+The calculation of an initialization order is performed in linear time based on the number of both external and internal connections using Tarjan's algortihm \cite{tarjan_1972}.
+Tarjan's algorithm is both detecting the strongly connected components of a graph and calculating the topological ordering.
+
+\todo{Come with an example using a graph with loops}
+
+\subsubsection{Handling of algebraic loops}
+As described earlier it is important to handle the algebraic loops by a special strategy since they otherwise would invalidate the result of the co-simulation.
+The strategy for handling of algebraic loops is to identify and initialize them using a fixed point iteration until the initial value of these converges.
+The termination of using fixed-point iteration has been proved \todo{Write more}.
+
+This paper's main contribution is to calculate an initialization order of a co-simulation scenario containing algebraic loops.
+The approach make the circular dependencies between the interconnected converge in the initialization, so the initial values of the interconnected variables in the system being simulated is stable at the time the co-simulation is started.
+
 \noindent As previously stated, a valid initialization order can only be calculated from an Initialization Graph if it does not contain any strongly connected components.
@@
 
-\begin{definition}[Validity criteria for Generation of an Initialization Graph]\label{def:valid_graph}
-  The Initialization Graph is valid if the given a co-simulation scenario $\tuple{\fmus, \coupling}$, and a set of feed-through dependencies $\bigcup_{c \in \fmus} \set{\feedthrough{c}}$.
-  $\forall c \in \fmus \implies \nexists \inputvar{} \in \inputs{c}, \outputvar{} \in \outputs{c}: (\inputvar{},\outputvar{}) \in \feedthrough{c} \land Path(\outputvar{}, \inputvar{})$\\
-  Where Paths is defined as the transitive closure of $Path = L \cup \bigcup_{c \in \fmus} \set{\feedthrough{c}}$
+\begin{definition}[Algebraic loop in an Initialization Graph]\label{def:algebraic_loop}
+  An algebraic loop in the given a co-simulation scenario $\tuple{\fmus, \coupling}$, and a set of feed-through dependencies $\bigcup_{c \in \fmus} \set{\feedthrough{c}}$ can be found if.\\
+  $\exists c \in \fmus : \exists \inputvar{} \in \inputs{c}, \outputvar{} \in \outputs{c}: (\inputvar{},\outputvar{}) \in \feedthrough{c} \land Path(\outputvar{}, \inputvar{})$\\
+  Where Path is defined as the transitive closure of $Path = L \cup \bigcup_{c \in \fmus} \set{\feedthrough{c}}$\\
+  The algebraic-loops is all \todo{Ask Stefan}
 \end{definition}
 
-All co-simulation scenarios satisfying definition \ref{def:valid_graph} is guaranteed to have a valid initialization order.
+All co-simulation scenarios satisfying definition \ref{def:algebraic_loop} contains at least one s guaranteed to have a valid initialization order.
 
+\subsection{Case study}
+Claduio writes this -section 
 \subsection{Three Tank Example}
@@
 \end{definition}
-This optimization uses the fact that the FMI specification allows to \textit{set} or \textit{get} variables of the same FMU to be performed in bulk by grouping interconnected variables of the same FMU with others with similar characteristic.
-Since an Initialization procedure is defined in the same they as other co-simulation steps.
-The optimization process described in definition \ref{def:optimization} is valid for an arbitrary co-simulation step.
-The only difference between an arbitrary co-simulation step and an initialization procedure is the size of the graph on which the topological sorting is performed.
-The correctness of this optimization can be established by the proof of using the Initialization Graph's topological ordering as the initialization order described by Gomes et al.
+This optimization uses the fact that the FMI specification allows to multiple \textit{set} or \textit{get} operations of the same FMU to be performed in bulk by grouping them together to a single operation over multiple variables with similar characteristic.
+Since an Initialization procedure is defined in the same they as other co-simulation steps the optimization criteria described in definition \ref{def:optimization} is valid for an arbitrary co-simulation step.
+The only difference between an arbitrary co-simulation step and an initialization procedure is the size of the dependency graph on which the topological ordering is performed.
+The correctness of this optimization can be established by the proof of using the Initialization Graph's topological ordering as the initialization order described by Gomes et al\cite{Gomes2019}.
 This proof is still valid since this optimization does not change the structure of the Initialization Graph.
-This optimization strategy potentially will not find all valid optimizations of a co-simulation scenario since it works on a co-simulation step (a topological order of a graph), which is not necessarily unique for a given co-simulation scenario/graph.
+A limitation of using this optimization strategy is that it potentially will not find all valid optimizations of a co-simulation scenario since it works on a specific co-simulation step (a topological order of a graph), which is not necessarily unique for a given co-simulation scenario/graph.
 To perform all possible optimizations of a co-simulation step, a more advanced optimization strategy should be used, or the optimization should be performed on the set of all valid co-simulation steps.
@@
 The algorithm is furthermore well-established, and there exist formal proofs of its correctness and properties\cite{stefan_merz}.
+The algorithm is among the best performance graph algorithms to solving the defined task.
 
@@
 The choice of Scala is motivated by the relation to JVM and the connection to Slang and the Logika framework\cite{inbook}.
-The connection to Slang and Logika will be used in the future work of formally verifying the plugin and explore how the contract-based nature of Slang can be used to obtain more trustworthy results of co-simulations.
+The connection to Slang and Logika will be investigated in the future.
+The Logika framework will be used to formally verify the implementation plugin and be used to explore how the contract-based nature of Slang can be used to obtain more reliable results of co-simulations.
+The topological sorting returns a topological order of strongly connected components.
+This order is the order of initialization, where the elements containing more than a single element denotes an algebraic loop that requires a particular initialization strategy.
+The algebraic loops should be initialized using fixed-point iteration in order to obtain a stable initial value.
 
 \subsection{Verification of the approach}
-The plugin and the approach behind it have been verified in several different ways.
+The realized plugin and the developed approach have been verified in several different ways.
 Gomes et al.
-have in \cite{gomes_lucio_vangheluwe_2019} proved the correctness of using the topological order of a similar graph to generate not only the initialization order but also the order for a co-simulation master-algorithm.
+have in \cite{gomes_lucio_vangheluwe_2019} proved the correctness of using the topological order of a dependency graph of the interconnected variables to generate not only the initialization order but also the order for a co-simulation master-algorithm.
 The purpose of the publication by Gomes et al.
@@
 
-The main contribution of Gomes et al.
-is an implementation of the FMI specification in Prolog freely available to be used in other projects.
-The Prolog implementation was used in their research to verify their proposed approach for generation of co-simulation algorithms.
+Gomes et al.
+'s main contribution is an implementation of the FMI specification in Prolog freely available to be used in other projects.
+The Prolog implementation was used in their research to verify their proposed approach for the generation of co-simulation algorithms.
 The realization encapsulates all the rules of a valid master-algorithm and an initialization algorithm.
-As a part of this work, integration from the plugin has been created to the Prolog realization.
+As a part of this work, an integration from this plugin has been realized to interact with the Prolog realization.
 This integration has been realized in order to verify the correctness of the calculated initialization order against an established and recognized method.
 The integration is based on JIProlog\cite{}, and it is querying the Prolog database with a co-simulation environment and an initialization order.
-The integration requires substantially mapping of the objects between the Java code of Maestro 2 and the Prolog implementation, and due to the described differences between the two graphs a mapping from the graph of ports to the graph of operations is needed.
+The integration requires substantial mapping of the objects between the Java code of Maestro 2 and the Prolog implementation.
+Due to the described differences between the two graphs, a mapping from the graph of ports to the graph of operations is needed.
 This mapping is based on the definitions \ref{def:getout} and \ref{def:setin}.
 
-The Prolog code can generate an initialization order, but this functionality haven't been used for several reasons.
-The main reason for not generating the initialization order using the Prolog code is based on performance considerations, and the approach taken in this paper does also ensure absence of circular dependencies between the interconnected FMU variables.
+The Prolog code can generate an initialization order, but this functionality has not been used for several reasons.
+The main reason for not generating the initialization order using the Prolog code is based on performance considerations.
+The approach taken in this paper does also identifies the strongly connected components and performs a particular initialization strategy of these.
 
 \section{Related Work}
+Prior work \cite{Gomes2019, BromanCompositionCo-Simulation} had been looking into the generation of co-simulation algorithms for both master and initialization algorithms for FMI-based scenarios based on a graph of the operations of a co-simulation step.
+Gomes and Broman do both present an approach where they use the topological sorting of a dependency graph to establish a correct order in which the operations of a co-simulation step should be performed.
 Gomes et al.
-\cite{Gomes2019} propose a strategy for the generation of co-simulation algorithms for FMI-based scenarios based on a graph of the operations of a co-simulation step.
-However, there are some key differences between their work and ours since the method they purpose does not handle algebraic loops.
+\cite{Gomes2019} propose a strategy for the generation of co-simulation algorithms and define the criteria for a correct co-simulation step.
+Their work has many similarities with ours.
+However, their work is not implemented and used in a practical context like ours that has been implemented as a plugin to Maestro 2.
 Furthermore, the approach taken in this paper is only concerned with the initialization procedure of a co-simulation.
 
-The requirement of freedom of algebraic loops of FMI-based co-simulation scenarios to obtain a deterministic composition result of a co-simulation master algorithm was required by Broman et al.
-\cite{BromanCompositionCo-Simulation}.
-They proposed to use the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of a co-simulation step.
-This insight
+The work by Broman et al.
+\cite{BromanCompositionCo-Simulation} proposes using the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of port-operations.
+Nevertheless, they specify the requirement for cycle freedom in the dependency graph as a precondition for the generation of a deterministic co-simulation algorithm.
+It means they refuse all co-simulation scenarios containing algebraic loops.
+This is a significant difference in our approach.
+The approach in this paper is more specialized in the sense that it is only considering the initialization of a co-simulation.
+This focus does that our work do need to include the handling of non-interconnected variables that should be addressed during the initialization of a co-simulation.
 
 Prior work by Amalio et al.
-\cite{Amalio2016CheckingCo-simulation} has been investigating how to ensure the absence of algebraic loops in FMU based co-simulation scenarios by statically checking the SysML CPS architectural design.
-The publication's purpose is partly very similar to ours - to guarantee the absence of algebraic loops in a co-simulation scenario.
-Nevertheless, their approach is only concerned with ensuring the absence of algebraic-loops since their approach is analyzing an architecture design; the calculation of the initialization order is of no interest.
+\cite{Amalio2016CheckingCo-simulation} has been investigating how to find and avoid algebraic loops in FMU based co-simulation scenarios by statically checking the SysML CPS architectural design.
+The publication's purpose is a bit different from ours - to guarantee the absence of algebraic loops in a co-simulation scenario.
+But their approach of being implemented
+Nevertheless, their approach is only concerned with ensuring the absence of algebraic-loops since their approach is analyzing an architecture design; the calculation of the initialization order is not in scope of their work.
 

### 2020-06-29 abstract.tex
Updated the article

@@
 The development of cyber-physical systems (CPS) is challenging due to the heterogeneity of the different subsystems.
-To assist in the development process, co-simulation can be used, where models of constituents of a CPS are coupled to jointly simulate the behavior of the full system.
-However, a trustworthy result of the co-simulation is only obtained if all of the simulation units are initialized correctly and in the correct order.
+Co-simulation can be used to assist in the development process, where models of constituents of a CPS are coupled to simulate the behavior of the full system jointly.
+However, an accurate result of the co-simulation is dependent on the correct initialization of all the simulation units.
 In this work, we consider co-simulation where the simulation units are described as Functional Mock-up Units (FMU).
@@
 Such interconnected variables place particular constraints on the initialization order of the FMUs.\\
-The approach taken to calculate a correct initialization order is based on predicates from the specification and the topological ordering of both internal connections and interconnected variables.
-Circular dependencies between FMU variables are dismissed.
+The approach taken to calculate a correct initialization order is based on predicates from the FMI specification and the topological ordering of both internal connections and interconnected variables.
+The approach supports the initialization of algebraic loops using fixed point iteration.%  dependencies between FMU variables are dismissed.
 %This approach has been compared to other already existing approaches for FMI initialization.
 The approach has been realized as a plugin for the open-source INTO-CPS Maestro 2 Co-simulation framework.
-It has been tested for various scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial application.
-The approach has also been directly tested against an established co-simulation algorithm generator implemented in Prolog.
+It has been tested for various scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial application.% The approach has also been directly tested against an established co-simulation algorithm generator implemented in Prolog.
 
-\keywords{Co-simulation \and Initialization \and Topological ordering \and FMI}
+\keywords{Co-simulation \and Initialization \and Algebraic loop \and Topological ordering \and FMI}
 \end{abstract}

### 2020-06-29 conclusion.tex
Updated the article

@@
 \section{Concluding remarks}\label{sc:summary}
-This work used a topological ordering based on the interconnected FMUs variable and internal FMU variable connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario.
-The calculated initialization order is optimized to group similar variables to perform fewest possible operations.
-This approach ensures absence of cycles between interconnected FMU variables by defining the criteria for valid co-simulation scenarios.
+This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU variable connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario.
+The calculated initialization order is optimized to group variables with similar characteristics to perform the fewest possible operations in the initialization procedure.
+This approach supports the initialization of a co-simulation scenario containing algebraic loops by utilization of fixed point iteration.
+The approach does also discard all co-simulation scenarios which are not adhering to the law of convergence \ref{def:convergence}.
 This approach can be combined with an arbitrary master algorithm to run the co-simulation. \\
-The approach was realized as a plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation algorithm generator and verifier implemented in Prolog using an integration.\\
-Future work includes formally verifying the plugin, and its implementation of the algorithm used to calculate the topological ordering using the Logika framework.
-Future work will also look into generation of a verification strategy for the whole Maestro 2 framework to explore how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.
+The approach was realized as a plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\
+Future work includes formal verification of the plugin using the Logika framework\cite{inbook}.
+Future work will also look into the generation of a verification strategy for the whole Maestro 2 framework to explore how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.
 
-\paragraph*{\textbf{Acknowlegements.}}We would like to thank Stefan Hallerstede, Peter Gorm Larsen and Claudio Gomes for providing valuable input to this paper and the developed plugin.
+\paragraph*{\textbf{Acknowlegements.}}We would like to thank Stefan Hallerstede and Peter Gorm Larsen for providing valuable input to this paper and the developed plugin.

### 2020-06-29 introduction.tex
Updated the article

--- 2020-06-26 introduction.tex
@@
 Co-simulation is a technique to combine multiple black-box simulation units to simulate/compute the behavior of the combined models as a discrete trace\cite{Kubler2000}.
-The simulation units, often developed independently from each other, are coupled using a master algorithm, also often developed independently,
-that communicates with each simulation unit via its interface.
-This interface comprises functions for setting/getting inputs/outputs, and computing the associated model behavior over a given interval of time.
+The simulation units, often developed independently from each other, are coupled using a master algorithm, also often developed independently, that communicates with each simulation unit via its interface.
+This interface comprises functions for setting/getting inputs/outputs, and computing the associated model behavior over a given time interval.
 \\
-The Functional Mock-up Interface (FMI) standard \cite{Blochwitz2012, fmi_2019} is such an interface describing how to communicate with each simulation unit.
-This interface can be used to connect different simulation units (called Functional Mock-up Units or FMUs) and exchange values between them and make them progress in time.
+The Functional Mock-up Interface (FMI) standard \cite{Blochwitz2012, fmi_2019} is such an interface prescribing how to communicate with each simulation unit.
+The interface is used to connect different simulation units (called Functional Mock-up Units or FMUs) and exchange values between them and make them progress in time.
 \\
+
 A typical co-simulation consists of three phases: Initialization, simulation, and teardown.
 This work concentrates on the first of these phases - the initialization phase.
-FMI specifies criteria for how an FMU shall be initialized.
+The FMI specification specifies criteria for how a single FMU shall be initialized.
 However, the FMI standard is not concerned with how a connected system of multiple FMUs should be correctly initialized as a whole.
 The way a system of multiple FMUs should be initialized and interacted with depends on each FMUs implementation and interconnections to other FMUs \cite{gomes_lucio_vangheluwe_2019}, since these place precedence constraints between the FMU variables.
-The precedence constraints make specific system configurations and initialization orders of a system invalid due to cyclic dependencies and dependencies among the interconnected variables.
-An appropriate order of initialization is vital for the correctness of the co-simulation \cite{Thule2018} because it ensures a variable is never read before it is set like the classical \textit{readers–writers problem}.
-Circular dependencies are important to avoid in a co-simulation scenario since they reduces the ability of a co-simulation to converge \cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}.\\
+The precedence constraints between the variables can introduce algebraic loops, which places particular requirements on the initialization order since the algebraic loops require a particular initialization strategy to be applied to calculate the initial values of the variables in the algebraic loop\cite{Bastian2011a}.
+The order of initialization is vital for the correctness of the co-simulation \cite{Thule2018} because it ensures a variable is never read before it is set like the classical \textit{readers–writers problem} and to make sure that all initial values have stabilized at the start of the simulation.
 
-This paper describes an approach for the initialization of an FMI-based co-simulation in linear time of the number of interconnected variables.
-The approach complies with the semantics of FMI and ensures the absence of cycles in the system.
+\noindent Algebraic loops occur whenever there is an interconnected FMU variable that indirectly depends on itself.
+Algebraic loops introduce specific challenges in the co-simulation, and studies have shown that neglecting a loop can lead to a prohibitively high error in the co-simulation \cite{Kubler2000}.
+Other approaches for the generation of co-simulation algorithms have avoided co-simulation scenarios containing algebraic loops since their presence reduces the chance of obtaining a valid co-simulation result\cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}.
+This choice is motivated by the fact that not all co-simulation scenarios containing algebraic loops are valid since some algebraic loops have a divergent nature.
+However, experience has shown that valid co-simulation scenarios containing algebraic loops exist, and a well-established co-simulation framework should be able to handle these scenarios.
+
+\textit{Contribution:} This paper describes an approach for calculating the initialization order of an FMI-based co-simulation in linear time of the number of interconnected variables.
+The approach complies with the semantics of FMI and support the initialization of algebraic loops between interconnected FMU variables and identifies divergent co-simulation scenarios.
 The approach does not put any constraints on choosing a master algorithm that should be used to carry out the simulation.
@@
 The approach has been realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2).
+\\
 The realized plugin has been tested for various co-simulation scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial applications. 
-Gomes et al.
-have created a co-simulation algorithm generator and verifier\cite{gomes_lucio_vangheluwe_2019} in Prolog an integration to this realization has been crated as a part of the plugin.
-This integration is used to verify the calculated initialization order against an already established method for calculating the initialization order.\\
+Furthermore, the calculated initialization order is systematically verified by an established co-simulation Algorithm Generator and Verifier by Gomes et al.
+implemented in Prolog \cite{gomes_lucio_vangheluwe_2019}.
+\\
 
-The paper is structured as follows: Section \ref{sc:background} gives a brief background of the formalization of FMUs and Maestro 2.
+\textit{Structure:} The paper is structured as follows: Section \ref{sc:background} gives a brief background of the formalization of FMUs and Maestro 2.
 Section \ref{sc:initilization} describes the approach taken to calculate the initialization order.

### 2020-06-29 paper.tex
Updated the article

@@
 %
-\authorrunning{S. Thrane and C. Thule}
+\authorrunning{S. Thrane et al.}
 % First names are abbreviated in the running head.
@@
 %
-\institute{DIGIT, Department of Engineering, Aarhus University, \email{\{sth, casper.thule\}@eng.au.dk\}}}
+\institute{DIGIT, Department of Engineering, Aarhus University, \email{\{sth, casper.thule, claudio.gomes\}@eng.au.dk\}}}
 %
@@
 The main definitions of relevance to this paper will be presented, but readers are referred to the original publications for more information.
-This paper is only concerned with the initialization-phase of a co-simulation.
-All information about the time of an FMU and master algorithms is of no relevance and will not be discussed in more detail.
-The formalization from Gomes et al. is also extended with some new definitions regarding algrebraic loops, and 
+This paper is only concerned with the initialization-phase of a co-simulation making time of an FMU irrelevant.
+The formalization from Gomes et al.
+is extended with new definitions regarding algebraic loops, and convergence of fixed point iteration.
 \begin{definition}[FMU]\label{def:fmu}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics{images/FMU_legendpdf.pdf}
-    \caption{FMU representation}
-    \label{fig:fmu_legend}
-\end{figure}
-
-An FMU can visually be displayed as in Figure \ref{fig:fmu_legend} where a simple co-simulation scenario is shown.
-
 \begin{definition}[Output Computation]\label{def:getout}
@@
 An interconnected variable v of a co-simulation scenario $\tuple{\fmus, \coupling}$ is defined as $v \in \allinputs \cup \alloutputs$, then $\coupling : \allinputs \to \alloutputs$.
+The set all all interconnected variables is denoted: $V = \allinputs \cup \alloutputs$,
 \end{definition}
 
-\begin{definition}[Algebraic loops]\todo{Create this definition}
-An interconnected variable v of a co-simulation scenario $\tuple{\fmus, \coupling}$ is defined as $v \in \allinputs \cup \alloutputs$, then $\coupling : \allinputs \to \alloutputs$.
+The interconnections of FMU variables can lead to circular dependencies between these.
+The following definitions will formalize the concept of an algebraic loop in a co-simulation scenario, and define the problem these loops are introducing in the system.
+A co-simulation scenario containing an algebraic loop is shown in Figure \ref{fig:fmu_cycle}.
+
+\begin{figure}
+    \centering
+    \includegraphics{images/fmu_cycle.pdf}
+    \caption{Co-simulation scenario with cycle}
+    \label{fig:fmu_cycle}
+\end{figure}
+
+\begin{definition}[Algebraic loops] 
+The set of interconnected variables in an algebraic loop is defined as: $LoopVariables = \{v | v \in V : Path(v,v)\}$ \\
+An algebraic loop is defined as the set $\{p_1, p_2 | p_1, p_2 \in LoopVariables: Path(p_1, p_2) \land Path(p_1, p_2)\}$\todo{Look at this}\\
+Path is defined as the transitive closure of the set of relations: $\bigcup_{c \in \fmus} \set{\feedthrough{c}} \cup \coupling$\\
+The algebraic dependency will lead to the following difference between performing to following :
+\todo{Claudio check this definition and add a formalization of the challenge introduced}
 \end{definition}
 
-\begin{definition}[Fixed point iteration]\todo{Create this definition}
-An interconnected variable v of a co-simulation scenario $\tuple{\fmus, \coupling}$ is defined as $v \in \allinputs \cup \alloutputs$, then $\coupling : \allinputs \to \alloutputs$.
+\begin{definition}[Challenge of Algebraic loops]\label{def:challenge}
+The algebraic dependency will lead to the following difference between performing to following :
+\todo{Claudio check the other definitions and add a formalization of the challenge introduced}
 \end{definition}
 
-\subsection{INTO-CPS Maestro 2}\todo{We can have some more in this section - potentially half a page?}
+As described by definition \ref{def:challenge} the algebraic loops introduce certain challenges in the system.
+This means that algebraic loops needs to be handled using fixed point iterations\cite{Gomes2018}.
+It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step.
+The number of repetitions the operations should be be performed depends on the characteristics of the scenario.
+The operations should be performed until the system converge.
+However a fixed point iteration technique is not guaranteed to convergence if the system is unstable.
+This means that an upper bound of the number of repetitions needs to be established to ensure termination.
+In case of a non-converging algebraic loop this should be treated as an incorrect co-simulation scenario and the simulation should be stopped.
+The criteria of a valid co-simulation scenario is is specified in definition \ref{def:convergence}.
+
+\todo{Christian should I add some pseudo code to explain?}
+\begin{definition}[Convergence of Fixed point iteration]\label{def:convergence}
+A fixed point iteration is converging if a finite number of iterations will make the difference of the output-value of the same operation between two following iterations within a certain threshold.\\
+$Convergence = \exists n \in \setnat: \forall \p \in LoopVariables \implies |f(p, n + 1) - f(p, n)| \leq T$\\
+$f$ is the operation performed on a loop-variable p of a given iteration n.
+\end{definition}
+
+\subsection{INTO-CPS Maestro 2}\todo{We can have some more in this section - potentially half a page - Ask Casper if he can do it?}
 INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}}\cite{thule_maestro2_2019} is an FMI-based co-simulation framework set to supersede Maestro\cite{Maestro}.
@@
 
-\section{Generation of an Initialization Order}\label{sc:initilization}
+\section{Calculation of an Initialization Order}\label{sc:initilization}
 FMI defines certain information about the initialization order described through different states of a co-simulation. The initialization phase covers the two states (in chronological order):
@@
 However, all variables of each FMU are group together to perform the fewest possible operations in the initialization.
-The FMI specification does allow multiple variables of a single FMU to be set in parallel.
 
-In the \textit{Initialization Mode} state, the variables of all FMUs should be defined if no circular dependencies exist. 
+In the \textit{Initialization Mode} state all variables of all FMUs should be defined.
 The variables with \textit{causality = parameter} of each FMU are set first, and the order of which they are set is again insignificant as they are independent.
-Afterwards the interconnected variables should be defined, but as stated by the definitions \ref{def:feedthrough}, \ref{def:getout} and \ref{def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order.
-And an algebraic loop in a co-simulation scenario places even more criteria on the initialization order.
+Afterwards the interconnected variables should be defined, but as stated by the definitions \ref{def:feedthrough}, \ref{def:getout} and \ref{def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops places even more constraints on the initialization order.
+This phase should should also support algebraic loops, this support includes utilization of fixed point iteration and detection of non-convergence of algebraic loops.
 
-\subsection{Method}
-The approach to calculate the initialization order of the interconnected FMU variables are based on the the method proposed in Gomes et al.
+\subsection{Method to calculate the initialization order}
+This section describes the approach to calculate the initialization order of the interconnected FMU variables are based on the the method proposed in Gomes et al.
 \cite{Gomes2019b, BromanCompositionCo-Simulation}, but the approach used here has been extended with the ability to handle algebraic loops.
+The approach is formulated in pseudo-code in algorithm \ref{alg:initialization}.
+\begin{figure}[htb]
+  \centering
+    \begin{algorithm}[H]
+    \caption{Initialization strategy for Interconnected variables}
+    \label{alg:initialization}
+      \begin{algorithmic}[1]
+        \State $InitializationGraph \gets createGraph(connections)$
+        \State $SCCS \gets Tarjan(InitializationGraph)$
+        \State $OptimizeInitializationOrder(SCCS)$
+        \ForEach {$SCC \in SCCS$}
+            \If {$isAlgebraicLoop(SCC)$}
+                \State $applyFixedPointIteration(SCC)$;
+            \Else
+                \State $initializeVariable(SCC)$;
+            \EndIf
+        \EndFor
+        \end{algorithmic}
+    \end{algorithm}
+\end{figure}
 
 \subsubsection{Structure of the graph}
-The initialization algorithm starts by building a directed graph of the dependency among the interconnected variables of the FMUs, The graph is constructed based on the interconnected variables and internal connections (feed-through).
+The initialization algorithm starts by building a directed graph of the dependency between the interconnected variables of the FMUs.
+The graph is constructed based on the interconnected variables and internal connections (feed-through).
 Each interconnected variable in the system represents a node, and the edges are based on these connections.
@@
 
-\subsubsection{Calculation of a initialization order}
-The topological ordering of a the graph defined in definition \ref{def:initialization_graph} is used a as the initialization order of the interconnected FMU variables.
-The elements of the topological order is the strongly connected components of the graphs.
+As described earlier, not all co-simulation scenarios are valid, and these invalid scenarios need to be identified.
+This is done by monitoring convergence of all algebraic loops.
+A valid co-simulation scenario must convergence by definition given in definition \ref{def:convergence}.
+
+\subsubsection{Calculation of an initialization order}
+The topological ordering of the graph defined in definition \ref{def:initialization_graph} is used as the initialization order of the interconnected FMU variables.
+The elements of the topological order are the strongly connected components of the graphs.
 The strongly connected components are potentially algebraic loops of the system.
-The algebraic loops is easily identified as the strongly connected components containing more than a single element.
-The single element members of the topological order is normally interconnected FMU variables, whose value should only be calculated once during the initialization.
+The algebraic loops are easily identified as the strongly connected components containing more than a single element.
+The single element members of the topological order are standard interconnected FMU variables, whose port operation should only be performed once during the initialization procedure.
 \\
-The calculation of an initialization order is performed in linear time based on the number of both external and internal connections using Tarjan's algortihm \cite{tarjan_1972}.
-Tarjan's algorithm is both detecting the strongly connected components of a graph and calculating the topological ordering.
+The calculation of an initialization order is performed in linear time based on the number of both external and internal connections using Tarjan's algorithm \cite{tarjan_1972}.
+This algorithm was selected since it solves two of the central issues of the initialization-phase of the co-simulation.
+\begin{itemize}
+    \item Identifies algebraic loops between interconnected variables (strongly connected components)
+    \item Performs a topological sorting of the Strongly Connected Components
+\end{itemize}
+The algorithm is furthermore well-established, and there exist formal proofs of its correctness and properties\cite{stefan_merz}.
+The algorithm is among the most efficient graph algorithms for achieving the defined goals.
+Tarjan's algorithm is performing a topological sorting of the strongly connected components of a graph. This makes it able to handle both graphs with and without algebraic loops.
 
@@
 \subsubsection{Handling of algebraic loops}
-As described earlier it is important to handle the algebraic loops by a special strategy since they otherwise would invalidate the result of the co-simulation.
-The strategy for handling of algebraic loops is to identify and initialize them using a fixed point iteration until the initial value of these converges.
-The termination of using fixed-point iteration has been proved \todo{Write more}.
+As described earlier, it is essential to handle the algebraic loops by a particular initialization strategy since they otherwise would invalidate the result of the co-simulation.
+The strategy for managing algebraic loops is to identify and initialize them using a fixed point iteration until convergence.
+Because convergence is not guaranteed, it should be monitored, and if convergence can not be established within a finite number of iteration, the co-simulation should be rejected.
 
-This paper's main contribution is to calculate an initialization order of a co-simulation scenario containing algebraic loops.
-The approach make the circular dependencies between the interconnected converge in the initialization, so the initial values of the interconnected variables in the system being simulated is stable at the time the co-simulation is started.
-
-\noindent As previously stated, a valid initialization order can only be calculated from an Initialization Graph if it does not contain any strongly connected components.
-This insight can be used to specify for which co-simulation scenarios a correct initialization order can be generated.
-A valid co-simulation scenario to calculate an initialization order from is defined in definition \ref{def:valid_graph}.
-
-\begin{definition}[Algebraic loop in an Initialization Graph]\label{def:algebraic_loop}
-  An algebraic loop in the given a co-simulation scenario $\tuple{\fmus, \coupling}$, and a set of feed-through dependencies $\bigcup_{c \in \fmus} \set{\feedthrough{c}}$ can be found if.\\
-  $\exists c \in \fmus : \exists \inputvar{} \in \inputs{c}, \outputvar{} \in \outputs{c}: (\inputvar{},\outputvar{}) \in \feedthrough{c} \land Path(\outputvar{}, \inputvar{})$\\
-  Where Path is defined as the transitive closure of $Path = L \cup \bigcup_{c \in \fmus} \set{\feedthrough{c}}$\\
-  The algebraic-loops is all \todo{Ask Stefan}
-\end{definition}
-
-All co-simulation scenarios satisfying definition \ref{def:algebraic_loop} contains at least one s guaranteed to have a valid initialization order.
-
-\subsection{Case study}
-Claduio writes this -section 
-\subsection{Three Tank Example}
-The structure of the Initialization Graph will be described using a small example. 
-The example is based on three water tanks that are filled and emptied.
-The first tank is filled from a source with a valve that may be turned on and off.
-The outflow of the first tank constitutes the inflow of the second, and so forth.
-A discrete-event controller monitors the level of the third tank and controls a valve to a drain.
-When the water level of the tank reaches a particular level (defined in the controller), the controller sends a command to the tank to empty using an exit valve.
-An illustration of the three water tanks can be seen in Figure \ref{fig:watertank}.
-A diagram of the FMUs showing the interconnections of the FMU variables in the system can be in Figure \ref{fig:watertank}.
-It should be noted that all internal connections that do not \textit{feed-through} have been omitted to simplify the diagram since they do not influence the initialization order and are not included in the graph defined in definition \ref{def:initialization_graph}.
-
-\begin{figure}[H]
-    \begin{minipage}{0.40\textwidth}
-    \centering
-        \centering
-    \includegraphics[width=1\textwidth]{images/ttwt_overview.pdf}
-    \end{minipage}
-    \begin{minipage}{0.60\textwidth}
-        \centering
-    \includegraphics[width=1\textwidth]{images/threetank_FMU.pdf}
-    \end{minipage}
-    \caption{Three tank case study}
-    \label{fig:watertank}
-\end{figure}
-
-\noindent A correct initialization order can be calculated since there are no circular dependencies in the system, the Initialization Graph is valid based on definition \ref{def:valid_graph}.
-The corresponding Initialization Graph of the three tank system can be seen in figure \ref{fig:initilizationGraph}.
-As it can be seen from the Initialization Graph, it is a disconnected graph meaning there are no limitations on the order of the initialization between the two sub-graphs.
-Nevertheless, in this case, an optimization of the initialization order can be made, using the fact that the FMI specification allows the set/get variables of the same FMU to be performed in bulk.
-This optimization can be made by setting the two inputs of \textit{T2} simultaneously (by the same operation).
-The definition of the optimization can be found in definition \ref{def:optimization}.
-It is not challenging to calculate the initialization order in this simple example.
-However, knowledge about the internal connections of each FMU is needed in order to calculate the initialization order due to \textit{feed-through} in FMU \textit{T2}.
-The strategy for calculating the initialization order scales to more advanced systems with an arbitrary number of FMUs and interconnected variables.
-Furthermore, an initialization order can be found as long a the Initialization Graph satisfies the criteria of definition \ref{def:valid_graph}.
-
-\begin{figure}
-    \centering
-      \includegraphics[width=0.95\textwidth]{images/threetank_initialization.pdf}
-    \caption{Initialization Graph of three tank}
-  \label{fig:initilizationGraph}
-\end{figure}
-
+\subsection{Optimization of a Initialization Procedure}
+An initialization procedure can be optimized by using the fact that the FMI specification allows multiple \textit{set} or \textit{get} operations of the same FMU to be performed in bulk by grouping them together to a single operation over multiple variables with similar characteristic.
+The criteria of optimization can of an initialization procedure is formalized in definition \ref{def:optimization}
 \begin{definition}[Optimization of a Initialization procedure]\label{def:optimization}
@@
 \end{definition}
-This optimization uses the fact that the FMI specification allows to multiple \textit{set} or \textit{get} operations of the same FMU to be performed in bulk by grouping them together to a single operation over multiple variables with similar characteristic.
-Since an Initialization procedure is defined in the same they as other co-simulation steps the optimization criteria described in definition \ref{def:optimization} is valid for an arbitrary co-simulation step.
-The only difference between an arbitrary co-simulation step and an initialization procedure is the size of the dependency graph on which the topological ordering is performed.
-The correctness of this optimization can be established by the proof of using the Initialization Graph's topological ordering as the initialization order described by Gomes et al\cite{Gomes2019}.
+Since an Initialization procedure is defined in the same way as other co-simulation steps, the optimization criteria described in definition \ref{def:optimization} is valid for an arbitrary co-simulation step.
+\\
+The correctness of this optimization can be established by the proof of using the Initialization Graph's topological ordering as the initialization order described by Gomes et al.
+\cite{Gomes2019}.
 This proof is still valid since this optimization does not change the structure of the Initialization Graph.
-A limitation of using this optimization strategy is that it potentially will not find all valid optimizations of a co-simulation scenario since it works on a specific co-simulation step (a topological order of a graph), which is not necessarily unique for a given co-simulation scenario/graph.
-To perform all possible optimizations of a co-simulation step, a more advanced optimization strategy should be used, or the optimization should be performed on the set of all valid co-simulation steps.
+\\
+A limitation of this optimization strategy is that it is not guaranteed to find all potentially valid optimizations of a co-simulation scenario.
+Considering it works only on a specific co-simulation step (a topological order of a graph), which is not necessarily unique for a given co-simulation scenario/graph.
+To perform all viable optimizations of a co-simulation step, a more advanced optimization strategy should be used, or this optimization strategy should be performed on the set of all valid co-simulation steps - yielding a potential very inefficient initialization algorithm.
+
+%This paper's main contribution is to calculate an initialization order of a co-simulation scenario potentially containing algebraic loops.
+The approach make the circular dependencies between the interconnected converge in the initialization, so the initial values of the interconnected variables in the system being simulated is stable at the time the co-simulation is started.
+
+\subsection{Case study}
+Claudio writes this section
 
@@
 This approach has been realized as a Maestro 2 plugin that generates the \textit{Initialization}-phase of a co-simulation specification expressed in MaBL.
-It calculates the specification based on a list of FMU-components, the simulation scenario as defined in definition \ref{def:cosim_scenario}, and a specific plugin-configuration to let the user supply initial values of FMU variables with $causality=parameter$.
-The plugin optimizes the initialization order of the initialization by grouping operations that can be executed in \textit{parallel} to take advantage of FMI's ability to set or get multiple variables in bulk from the same FMU.
+It calculates the specification based on a list of FMU-components of a co-simulation scenario, and a specific plugin-configuration to let the user supply initial values of FMU variables with $causality=parameter$.
+A correction initialization specification can be calculated by the plugin if the co-simulation scenario is adhering to definition \ref{def:convergence}.
+
+The plugin optimizes the initialization order by grouping operations that can be executed in \textit{parallel} to take advantage of FMI's ability to set or get multiple variables in bulk from the same FMU.
 The criteria for this optimization is defined in definition \ref{def:optimization}.
-The developed plugin has been tested on numerous co-simulation examples from the INTO-CPS universe\todo{should I add a footnote} and compared with the existing \textit{Initializer} of Maestro.
+The developed plugin has been tested on numerous co-simulation examples from the INTO-CPS universe\cite{Maestro} and compared with the existing \textit{Initializer} of Maestro.
 The plugin has been tested in the whole Maestro 2 pipeline to practically verify that it can be used in a co-simulation where the generated initialization procedure is integrated as a part of a complete co-simulation to verify the initialization procedure's integration with a master algorithm.
 
-\subsection{Topological sorting}
-The algorithm for calculating the topological order of the Initialization Graph defined in definition \ref{def:initialization_graph} is Tarjan's algorithm\cite{tarjan_1972}.
-The algorithm was selected since it solves two of the central issues of the initialization-phase of the co-simulation.
-\begin{itemize}
-    \item Identifies circular dependencies between interconnected variables (strongly connected components)
-    \item Performs a topological sorting of the Initialization Graph
-\end{itemize}
-The algorithm is furthermore well-established, and there exist formal proofs of its correctness and properties\cite{stefan_merz}.
-The algorithm is among the best performance graph algorithms to solving the defined task.
-
-The topological sorting algorithm was implemented in Scala.
-The choice of Scala is motivated by the relation to JVM and the connection to Slang and the Logika framework\cite{inbook}.
+\subsection{Realization of the Topological Sorting}
+The topological sorting algorithm (Tarjan's Algorithm) was implemented in Scala.
+The motivation for choosing Scala is its relation to JVM and the connection to Slang and the Logika framework\cite{inbook}.
 The connection to Slang and Logika will be investigated in the future.
@@
 This order is the order of initialization, where the elements containing more than a single element denotes an algebraic loop that requires a particular initialization strategy.
-The algebraic loops should be initialized using fixed-point iteration in order to obtain a stable initial value.
 
@@
 are interested in both generating an initialization and master-algorithm, meaning they also need to focus on the time of each FMU.
-They also define their graph using methods (Set, Get, doStep) instead of interconnected variables, which is the approach described in this paper.
+They also define their graph based on FMU-operations ($Set, Get, doStep$) instead of interconnected variables, which is the approach described in this paper.
 This simplification is valid since this approach only cares about initialization and, therefore, does not need to care about the time of each FMU.
@@
 
-Gomes et al.
-'s main contribution is an implementation of the FMI specification in Prolog freely available to be used in other projects.
+Gomes et al.'s main contribution is an implementation of the FMI specification in Prolog freely available to be used in other projects.
 The Prolog implementation was used in their research to verify their proposed approach for the generation of co-simulation algorithms.
@@
 This integration has been realized in order to verify the correctness of the calculated initialization order against an established and recognized method.
-The integration is based on JIProlog\cite{}, and it is querying the Prolog database with a co-simulation environment and an initialization order.
-The integration requires substantial mapping of the objects between the Java code of Maestro 2 and the Prolog implementation.
-Due to the described differences between the two graphs, a mapping from the graph of ports to the graph of operations is needed.
-This mapping is based on the definitions \ref{def:getout} and \ref{def:setin}.
+The integration is querying the Prolog database with a co-simulation environment and an initialization order.
+The integration requires a transformation of the dependency graph (see definition \ref{def:initialization_graph}) used in the plugin to a graph of FMU operations.
+This transformation is based on the definitions \ref{def:getout} and \ref{def:setin}.
+The described verification integration is not utilized if the graph contains algebraic loops since the Prolog database does not support these scenarios.
 
@@
 \section{Related Work}
-Prior work \cite{Gomes2019, BromanCompositionCo-Simulation} had been looking into the generation of co-simulation algorithms for both master and initialization algorithms for FMI-based scenarios based on a graph of the operations of a co-simulation step.
-Gomes and Broman do both present an approach where they use the topological sorting of a dependency graph to establish a correct order in which the operations of a co-simulation step should be performed.
+Prior work \cite{Gomes2019, BromanCompositionCo-Simulation} has been looking into the generation of co-simulation algorithms for both master and initialization algorithms for FMI-based scenarios based on a dependency graph of the operations of a co-simulation step.
+Gomes and Broman do both present an approach where they use the topological sorting of a dependency graph to establish a correct order of operations in a co-simulation step.
 Gomes et al.
@@
 Their work has many similarities with ours.
-However, their work is not implemented and used in a practical context like ours that has been implemented as a plugin to Maestro 2.
-Furthermore, the approach taken in this paper is only concerned with the initialization procedure of a co-simulation.
+However, their work does not look into the handling of algebraic loops and is not implemented as a real co-simulation framework.
+Furthermore, the approach taken in our work is only concerned with the initialization procedure of a co-simulation.
 
@@
 \cite{BromanCompositionCo-Simulation} proposes using the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of port-operations.
-Nevertheless, they specify the requirement for cycle freedom in the dependency graph as a precondition for the generation of a deterministic co-simulation algorithm.
+Nevertheless, they explicitly specify the requirement for cycle freedom in the dependency graph as a precondition for the generation of a deterministic co-simulation algorithm.
 It means they refuse all co-simulation scenarios containing algebraic loops.
-This is a significant difference in our approach.
-The approach in this paper is more specialized in the sense that it is only considering the initialization of a co-simulation.
-This focus does that our work do need to include the handling of non-interconnected variables that should be addressed during the initialization of a co-simulation.
+This is a significant difference to our approach that applies a fixed point iteration strategy to handle these scenarios.
+Also, the approach in this paper is more specialized in the sense that it is only considering the initialization of a co-simulation.
 
-Prior work by Amalio et al.
-\cite{Amalio2016CheckingCo-simulation} has been investigating how to find and avoid algebraic loops in FMU based co-simulation scenarios by statically checking the SysML CPS architectural design.
-The publication's purpose is a bit different from ours - to guarantee the absence of algebraic loops in a co-simulation scenario.
-But their approach of being implemented
-Nevertheless, their approach is only concerned with ensuring the absence of algebraic-loops since their approach is analyzing an architecture design; the calculation of the initialization order is not in scope of their work.
+Amalio et al.
+\cite{Amalio2016CheckingCo-simulation} has been investigating how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS.
+The publication's purpose is like ours to avoid invalid co-simulation scenarios.
+Nevertheless, they achieve this by excluding scenarios containing algebraic loops.
+Their method is like ours also implemented in the real tool INTO-SysML, and it is based on using different kinds of formal methods (Theorem Proving and Model-checking) and will be an inspiration for the future work of formally verifying the plugin.
 

### 2020-06-29 paper.tex
Updates from Overleaf

@@
 
-\section{Background}\label{sc:background}
-In this section, we provide a formalization of FMI co-simulation and a short background on INTO-CPS Maestro 2.
-
-\subsection{FMU definitions}
-To describe the formalization of FMUs, the vocabulary from Gomes et al\cite{gomes_lucio_vangheluwe_2019, Gomes2018} is adopted.
-The main definitions of relevance to this paper will be presented, but readers are referred to the original publications for more information.
-This paper is only concerned with the initialization-phase of a co-simulation making time of an FMU irrelevant.
-The formalization from Gomes et al.
-is extended with new definitions regarding algebraic loops, and convergence of fixed point iteration.
-\begin{definition}[FMU]\label{def:fmu}
-  An FMU with identifier $c$ is represented by the tuple   
-  $$\tuple{\stateset{c}, \inputs{c}, \outputs{c}, \fset{c}, \fget{c}},$$
-  where:
-  \begin{inparadesc}
-    \item $\stateset{c}$ represents the state space;
-    \item $\inputs{c}$ and $\outputs{c}$ the set of input and output variables, respectively;
-    \item $\fset{c} : \stateset{c} \times \inputs{c} \times \values \to \stateset{c}$ and $\fget{c}: \stateset{c} \times \outputs{c} \to \values$ are functions to set the inputs and get the outputs, respectively (we abstract the set of values that each input/output variable can take as $\values$).
-  \end{inparadesc}
-\end{definition}
-
-\begin{definition}[Scenario]\label{def:cosim_scenario}
-  A scenario is a structure $\tuple{\fmus, \coupling}$ where each identifier $c \in \fmus$ is associated with an FMU, as defined in \ref{def:fmu}, and $\coupling(u)=y$ means that the output $y$ is connected to input $u$.
-  Let $\allinputs = \bigcup_{c \in \fmus} \inputs{c}$ and $\alloutputs = \bigcup_{c \in \fmus} \outputs{c}$, then $\coupling : \allinputs \to \alloutputs$.
-\end{definition}
-
-The following definitions correspond to the operations that are permitted in the initialization phase of a co-simulation.
-
-\begin{definition}[Step]\label{def:cosim_step}
-  Given a scenario $\tuple{\fmus, \coupling}$, a co-simulation step, or just step, is a finite ordered sequence of FMU function calls $\sequence{\functioncall_i}_{i \in \setnat} = \functioncall_0, \functioncall_1, \ldots$ with
-  $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}},$
-  and $i$ denoting the order of the function call.
-\end{definition}
-
-\begin{definition}[Initialization]\label{def:initialization}
-  Given a scenario $\tuple{\fmus, \coupling}$, we define the initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ in the same way as a step, with $\initcall_i \in \allfunctioncalls$.
-\end{definition}
-
-\begin{definition}[Feed-through]\label{def:feedthrough}
-  The input $\inputvar{c} \in \inputs{c}$ feeds through to output $\outputvar{c} \in \outputs{c}$, that is, $(\inputvar{c},\outputvar{c}) \in \feedthrough{c}$, when there exists $v_1, v_2 \in \values$ and $\state{c} \in \stateset{c}$, such that
-  $
-  \fget{c} (\fset{c}(\state{c}, \inputvar{c}, v_1), \outputvar{c}) \neq \fget{c} (\fset{c}(\state{c}, \inputvar{c}, v_2), \outputvar{c}).
-  $
-\end{definition}
-
-\begin{definition}[Output Computation]\label{def:getout}
-The $\fget{c}(\dontcare, \outputvar{c})$ represents the calculation of output $\outputvar{c}$ of $c \in \fmus$.
-Given a co-simulation state, it checks whether all inputs that feed-through to $\outputvar{c}$ are defined.
-\end{definition}
-
-\begin{definition}[Input Computation]\label{def:setin}
-The $\fset{c}(\dontcare, \inputvar{c}, \inputV)$ represents the setting of input $\inputvar{c}$  of $c \in \fmus$.
-Given a co-simulation state, it checks whether all outputs connected to $\inputvar{c}$ are defined.
-\end{definition}
-
-\begin{definition}[Interconnected variable]
-An interconnected variable v of a co-simulation scenario $\tuple{\fmus, \coupling}$ is defined as $v \in \allinputs \cup \alloutputs$, then $\coupling : \allinputs \to \alloutputs$.
-The set all all interconnected variables is denoted: $V = \allinputs \cup \alloutputs$,
-\end{definition}
-
-The interconnections of FMU variables can lead to circular dependencies between these.
-The following definitions will formalize the concept of an algebraic loop in a co-simulation scenario, and define the problem these loops are introducing in the system.
-A co-simulation scenario containing an algebraic loop is shown in Figure \ref{fig:fmu_cycle}.
-
-\begin{figure}
-    \centering
-    \includegraphics{images/fmu_cycle.pdf}
-    \caption{Co-simulation scenario with cycle}
-    \label{fig:fmu_cycle}
-\end{figure}
-
-\begin{definition}[Algebraic loops] 
-The set of interconnected variables in an algebraic loop is defined as: $LoopVariables = \{v | v \in V : Path(v,v)\}$ \\
-An algebraic loop is defined as the set $\{p_1, p_2 | p_1, p_2 \in LoopVariables: Path(p_1, p_2) \land Path(p_1, p_2)\}$\todo{Look at this}\\
-Path is defined as the transitive closure of the set of relations: $\bigcup_{c \in \fmus} \set{\feedthrough{c}} \cup \coupling$\\
-The algebraic dependency will lead to the following difference between performing to following :
-\todo{Claudio check this definition and add a formalization of the challenge introduced}
-\end{definition}
-
-\begin{definition}[Challenge of Algebraic loops]\label{def:challenge}
-The algebraic dependency will lead to the following difference between performing to following :
-\todo{Claudio check the other definitions and add a formalization of the challenge introduced}
-\end{definition}
-
-As described by definition \ref{def:challenge} the algebraic loops introduce certain challenges in the system.
-This means that algebraic loops needs to be handled using fixed point iterations\cite{Gomes2018}.
-It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step.
-The number of repetitions the operations should be be performed depends on the characteristics of the scenario.
-The operations should be performed until the system converge.
-However a fixed point iteration technique is not guaranteed to convergence if the system is unstable.
-This means that an upper bound of the number of repetitions needs to be established to ensure termination.
-In case of a non-converging algebraic loop this should be treated as an incorrect co-simulation scenario and the simulation should be stopped.
-The criteria of a valid co-simulation scenario is is specified in definition \ref{def:convergence}.
-
-\todo{Christian should I add some pseudo code to explain?}
-\begin{definition}[Convergence of Fixed point iteration]\label{def:convergence}
-A fixed point iteration is converging if a finite number of iterations will make the difference of the output-value of the same operation between two following iterations within a certain threshold.\\
-$Convergence = \exists n \in \setnat: \forall \p \in LoopVariables \implies |f(p, n + 1) - f(p, n)| \leq T$\\
-$f$ is the operation performed on a loop-variable p of a given iteration n.
-\end{definition}
-
-\subsection{INTO-CPS Maestro 2}\todo{We can have some more in this section - potentially half a page - Ask Casper if he can do it?}
-INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}}\cite{thule_maestro2_2019} is an FMI-based co-simulation framework set to supersede Maestro\cite{Maestro}.
-The philosophy of the framework is to apply plugins to generate co-simulation specifications expressed in the domain specific language called Maestro Base Language (MaBL).
-Such specifications are then interpreted and executed resolving in the execution of a co-simulation.
-
+\input{background.tex}
 \section{Calculation of an Initialization Order}\label{sc:initilization}
@@
 
-\section{Realization of a Maestro 2 Plugin}\label{sc:implementation}
-This approach has been realized as a Maestro 2 plugin that generates the \textit{Initialization}-phase of a co-simulation specification expressed in MaBL.
-It calculates the specification based on a list of FMU-components of a co-simulation scenario, and a specific plugin-configuration to let the user supply initial values of FMU variables with $causality=parameter$.
-A correction initialization specification can be calculated by the plugin if the co-simulation scenario is adhering to definition \ref{def:convergence}.
+\input{realization.tex}
 
-The plugin optimizes the initialization order by grouping operations that can be executed in \textit{parallel} to take advantage of FMI's ability to set or get multiple variables in bulk from the same FMU.
-The criteria for this optimization is defined in definition \ref{def:optimization}.
-The developed plugin has been tested on numerous co-simulation examples from the INTO-CPS universe\cite{Maestro} and compared with the existing \textit{Initializer} of Maestro.
-The plugin has been tested in the whole Maestro 2 pipeline to practically verify that it can be used in a co-simulation where the generated initialization procedure is integrated as a part of a complete co-simulation to verify the initialization procedure's integration with a master algorithm.
-
-\subsection{Realization of the Topological Sorting}
-The topological sorting algorithm (Tarjan's Algorithm) was implemented in Scala.
-The motivation for choosing Scala is its relation to JVM and the connection to Slang and the Logika framework\cite{inbook}.
-The connection to Slang and Logika will be investigated in the future.
-The Logika framework will be used to formally verify the implementation plugin and be used to explore how the contract-based nature of Slang can be used to obtain more reliable results of co-simulations.
-The topological sorting returns a topological order of strongly connected components.
-This order is the order of initialization, where the elements containing more than a single element denotes an algebraic loop that requires a particular initialization strategy.
-
-\subsection{Verification of the approach}
-The realized plugin and the developed approach have been verified in several different ways.
-Gomes et al.
-have in \cite{gomes_lucio_vangheluwe_2019} proved the correctness of using the topological order of a dependency graph of the interconnected variables to generate not only the initialization order but also the order for a co-simulation master-algorithm.
-The purpose of the publication by Gomes et al.
-is a little different from the one of this paper.
-Gomes et al.
-are interested in both generating an initialization and master-algorithm, meaning they also need to focus on the time of each FMU.
-They also define their graph based on FMU-operations ($Set, Get, doStep$) instead of interconnected variables, which is the approach described in this paper.
-This simplification is valid since this approach only cares about initialization and, therefore, does not need to care about the time of each FMU.
-This does that we can omit all the $doStep$ nodes and all edges connected to them from the graph by Gomes et al., this approach does, therefore, end up with a subgraph of the graph by Gomes et al.
-The proof from \cite{gomes_lucio_vangheluwe_2019} can therefore trivial be modified to the graph/approach presented in this paper.
-
-Gomes et al.'s main contribution is an implementation of the FMI specification in Prolog freely available to be used in other projects.
-The Prolog implementation was used in their research to verify their proposed approach for the generation of co-simulation algorithms.
-The realization encapsulates all the rules of a valid master-algorithm and an initialization algorithm.
-As a part of this work, an integration from this plugin has been realized to interact with the Prolog realization.
-This integration has been realized in order to verify the correctness of the calculated initialization order against an established and recognized method.
-The integration is querying the Prolog database with a co-simulation environment and an initialization order.
-The integration requires a transformation of the dependency graph (see definition \ref{def:initialization_graph}) used in the plugin to a graph of FMU operations.
-This transformation is based on the definitions \ref{def:getout} and \ref{def:setin}.
-The described verification integration is not utilized if the graph contains algebraic loops since the Prolog database does not support these scenarios.
-
-The Prolog code can generate an initialization order, but this functionality has not been used for several reasons.
-The main reason for not generating the initialization order using the Prolog code is based on performance considerations.
-The approach taken in this paper does also identifies the strongly connected components and performs a particular initialization strategy of these.
-
-\section{Related Work}
-Prior work \cite{Gomes2019, BromanCompositionCo-Simulation} has been looking into the generation of co-simulation algorithms for both master and initialization algorithms for FMI-based scenarios based on a dependency graph of the operations of a co-simulation step.
-Gomes and Broman do both present an approach where they use the topological sorting of a dependency graph to establish a correct order of operations in a co-simulation step.
-Gomes et al.
-\cite{Gomes2019} propose a strategy for the generation of co-simulation algorithms and define the criteria for a correct co-simulation step.
-Their work has many similarities with ours.
-However, their work does not look into the handling of algebraic loops and is not implemented as a real co-simulation framework.
-Furthermore, the approach taken in our work is only concerned with the initialization procedure of a co-simulation.
-
-The work by Broman et al.
-\cite{BromanCompositionCo-Simulation} proposes using the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of port-operations.
-Nevertheless, they explicitly specify the requirement for cycle freedom in the dependency graph as a precondition for the generation of a deterministic co-simulation algorithm.
-It means they refuse all co-simulation scenarios containing algebraic loops.
-This is a significant difference to our approach that applies a fixed point iteration strategy to handle these scenarios.
-Also, the approach in this paper is more specialized in the sense that it is only considering the initialization of a co-simulation.
-
-Amalio et al.
-\cite{Amalio2016CheckingCo-simulation} has been investigating how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS.
-The publication's purpose is like ours to avoid invalid co-simulation scenarios.
-Nevertheless, they achieve this by excluding scenarios containing algebraic loops.
-Their method is like ours also implemented in the real tool INTO-SysML, and it is based on using different kinds of formal methods (Theorem Proving and Model-checking) and will be an inspiration for the future work of formally verifying the plugin.
+\input{relatedwork.tex}
 

### 2020-06-29 background.tex

\section{Background}\label{sc:background}
In this section, we provide a formalization of FMI co-simulation and a short background on INTO-CPS Maestro 2.

\subsection{FMU definitions}
To describe the formalization of FMUs, the vocabulary from Gomes et al\cite{gomes_lucio_vangheluwe_2019, Gomes2018} is adopted. The main definitions of relevance to this paper will be presented, but readers are referred to the original publications for more information. This paper is only concerned with the initialization-phase of a co-simulation making time of an FMU irrelevant. The formalization from Gomes et al. is extended with new definitions regarding algebraic loops, and convergence of fixed point iteration.
\begin{definition}[FMU]\label{def:fmu}
  An FMU with identifier $c$ is represented by the tuple   
  $$\tuple{\stateset{c}, \inputs{c}, \outputs{c}, \fset{c}, \fget{c}},$$
  where:
  \begin{inparadesc}
    \item $\stateset{c}$ represents the state space;
    \item $\inputs{c}$ and $\outputs{c}$ the set of input and output variables, respectively;
    \item $\fset{c} : \stateset{c} \times \inputs{c} \times \values \to \stateset{c}$ and $\fget{c}: \stateset{c} \times \outputs{c} \to \values$ are functions to set the inputs and get the outputs, respectively (we abstract the set of values that each input/output variable can take as $\values$).
  \end{inparadesc}
\end{definition}

\begin{definition}[Scenario]\label{def:cosim_scenario}
  A scenario is a structure $\tuple{\fmus, \coupling}$ where each identifier $c \in \fmus$ is associated with an FMU, as defined in \ref{def:fmu}, and $\coupling(u)=y$ means that the output $y$ is connected to input $u$.
  Let $\allinputs = \bigcup_{c \in \fmus} \inputs{c}$ and $\alloutputs = \bigcup_{c \in \fmus} \outputs{c}$, then $\coupling : \allinputs \to \alloutputs$.
\end{definition}

The following definitions correspond to the operations that are permitted in the initialization phase of a co-simulation.

\begin{definition}[Step]\label{def:cosim_step}
  Given a scenario $\tuple{\fmus, \coupling}$, a co-simulation step, or just step, is a finite ordered sequence of FMU function calls $\sequence{\functioncall_i}_{i \in \setnat} = \functioncall_0, \functioncall_1, \ldots$ with
  $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}},$
  and $i$ denoting the order of the function call.
\end{definition}

\begin{definition}[Initialization]\label{def:initialization}
  Given a scenario $\tuple{\fmus, \coupling}$, we define the initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ in the same way as a step, with $\initcall_i \in \allfunctioncalls$.
\end{definition}

\begin{definition}[Feed-through]\label{def:feedthrough}
  The input $\inputvar{c} \in \inputs{c}$ feeds through to output $\outputvar{c} \in \outputs{c}$, that is, $(\inputvar{c},\outputvar{c}) \in \feedthrough{c}$, when there exists $v_1, v_2 \in \values$ and $\state{c} \in \stateset{c}$, such that
  $
  \fget{c} (\fset{c}(\state{c}, \inputvar{c}, v_1), \outputvar{c}) \neq \fget{c} (\fset{c}(\state{c}, \inputvar{c}, v_2), \outputvar{c}).
  $
\end{definition}

\begin{definition}[Output Computation]\label{def:getout}
The $\fget{c}(\dontcare, \outputvar{c})$ represents the calculation of output $\outputvar{c}$ of $c \in \fmus$. Given a co-simulation state, it checks whether all inputs that feed-through to $\outputvar{c}$ are defined.
\end{definition}

\begin{definition}[Input Computation]\label{def:setin}
The $\fset{c}(\dontcare, \inputvar{c}, \inputV)$ represents the setting of input $\inputvar{c}$  of $c \in \fmus$. Given a co-simulation state, it checks whether all outputs connected to $\inputvar{c}$ are defined.
\end{definition}

\begin{definition}[Interconnected variable]
An interconnected variable v of a co-simulation scenario $\tuple{\fmus, \coupling}$ is defined as $v \in \allinputs \cup \alloutputs$, then $\coupling : \allinputs \to \alloutputs$.
The set all all interconnected variables is denoted: $V = \allinputs \cup \alloutputs$,
\end{definition}

The interconnections of FMU variables can lead to circular dependencies between these. The following definitions will formalize the concept of an algebraic loop in a co-simulation scenario, and define the problem these loops are introducing in the system. A co-simulation scenario containing an algebraic loop is shown in Figure \ref{fig:fmu_cycle}.

\begin{figure}
    \centering
    \includegraphics{images/fmu_cycle.pdf}
    \caption{Co-simulation scenario with cycle}
    \label{fig:fmu_cycle}
\end{figure}

\begin{definition}[Algebraic loops] 
The set of interconnected variables in an algebraic loop is defined as: $LoopVariables = \{v | v \in V : Path(v,v)\}$ \\
An algebraic loop is defined as the set $\{p_1, p_2 | p_1, p_2 \in LoopVariables: Path(p_1, p_2) \land Path(p_1, p_2)\}$\todo{Look at this}\\
Path is defined as the transitive closure of the set of relations: $\bigcup_{c \in \fmus} \set{\feedthrough{c}} \cup \coupling$\\
The algebraic dependency will lead to the following difference between performing to following :
\todo{Claudio check this definition and add a formalization of the challenge introduced}
\end{definition}

\begin{definition}[Challenge of Algebraic loops]\label{def:challenge}
The algebraic dependency will lead to the following difference between performing to following :
\todo{Claudio check the other definitions and add a formalization of the challenge introduced}
\end{definition}

As described by definition \ref{def:challenge} the algebraic loops introduce certain challenges in the system. This means that algebraic loops needs to be handled using fixed point iterations\cite{Gomes2018}. It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step. The number of repetitions the operations should be be performed depends on the characteristics of the scenario. The operations should be performed until the system converge.
However a fixed point iteration technique is not guaranteed to convergence if the system is unstable. This means that an upper bound of the number of repetitions needs to be established to ensure termination. In case of a non-converging algebraic loop this should be treated as an incorrect co-simulation scenario and the simulation should be stopped. The criteria of a valid co-simulation scenario is is specified in definition \ref{def:convergence}.

\todo{Christian should I add some pseudo code to explain?}
\begin{definition}[Convergence of Fixed point iteration]\label{def:convergence}
A fixed point iteration is converging if a finite number of iterations will make the difference of the output-value of the same operation between two following iterations within a certain threshold.\\
$Convergence = \exists n \in \setnat: \forall \p \in LoopVariables \implies |f(p, n + 1) - f(p, n)| \leq T$\\
$f$ is the operation performed on a loop-variable p of a given iteration n.
\end{definition}

\subsection{INTO-CPS Maestro 2}\todo{We can have some more in this section - potentially half a page - Ask Casper if he can do it?}
INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}}\cite{thule_maestro2_2019} is an FMI-based co-simulation framework set to supersede Maestro\cite{Maestro}. The philosophy of the framework is to apply plugins to generate co-simulation specifications expressed in the domain specific language called Maestro Base Language (MaBL). Such specifications are then interpreted and executed resolving in the execution of a co-simulation.

### 2020-06-29 realization.tex

\section{Realization of a Maestro 2 Plugin}\label{sc:implementation}
This approach has been realized as a Maestro 2 plugin that generates the \textit{Initialization}-phase of a co-simulation specification expressed in MaBL. It calculates the specification based on a list of FMU-components of a co-simulation scenario, and a specific plugin-configuration to let the user supply initial values of FMU variables with $causality=parameter$. A correction initialization specification can be calculated by the plugin if the co-simulation scenario is adhering to definition \ref{def:convergence}.

The plugin optimizes the initialization order by grouping operations that can be executed in \textit{parallel} to take advantage of FMI's ability to set or get multiple variables in bulk from the same FMU. The criteria for this optimization is defined in definition \ref{def:optimization}. 
The developed plugin has been tested on numerous co-simulation examples from the INTO-CPS universe\cite{Maestro} and compared with the existing \textit{Initializer} of Maestro. The plugin has been tested in the whole Maestro 2 pipeline to practically verify that it can be used in a co-simulation where the generated initialization procedure is integrated as a part of a complete co-simulation to verify the initialization procedure's integration with a master algorithm.

\subsection{Realization of the Topological Sorting}
The topological sorting algorithm (Tarjan's Algorithm) was implemented in Scala. The motivation for choosing Scala is its relation to JVM and the connection to Slang and the Logika framework\cite{inbook}. The connection to Slang and Logika will be investigated in the future. The Logika framework will be used to formally verify the implementation plugin and be used to explore how the contract-based nature of Slang can be used to obtain more reliable results of co-simulations. The topological sorting returns a topological order of strongly connected components. This order is the order of initialization, where the elements containing more than a single element denotes an algebraic loop that requires a particular initialization strategy.

\subsection{Verification of the approach}
The realized plugin and the developed approach have been verified in several different ways. Gomes et al. have in \cite{gomes_lucio_vangheluwe_2019} proved the correctness of using the topological order of a dependency graph of the interconnected variables to generate not only the initialization order but also the order for a co-simulation master-algorithm. The purpose of the publication by Gomes et al. is a little different from the one of this paper. Gomes et al. are interested in both generating an initialization and master-algorithm, meaning they also need to focus on the time of each FMU. They also define their graph based on FMU-operations ($Set, Get, doStep$) instead of interconnected variables, which is the approach described in this paper. This simplification is valid since this approach only cares about initialization and, therefore, does not need to care about the time of each FMU. This does that we can omit all the $doStep$ nodes and all edges connected to them from the graph by Gomes et al., this approach does, therefore, end up with a subgraph of the graph by Gomes et al. The proof from \cite{gomes_lucio_vangheluwe_2019} can therefore trivial be modified to the graph/approach presented in this paper.

Gomes et al.'s main contribution is an implementation of the FMI specification in Prolog freely available to be used in other projects. The Prolog implementation was used in their research to verify their proposed approach for the generation of co-simulation algorithms. The realization encapsulates all the rules of a valid master-algorithm and an initialization algorithm. As a part of this work, an integration from this plugin has been realized to interact with the Prolog realization. This integration has been realized in order to verify the correctness of the calculated initialization order against an established and recognized method. The integration is querying the Prolog database with a co-simulation environment and an initialization order. The integration requires a transformation of the dependency graph (see definition \ref{def:initialization_graph}) used in the plugin to a graph of FMU operations. This transformation is based on the definitions \ref{def:getout} and \ref{def:setin}. The described verification integration is not utilized if the graph contains algebraic loops since the Prolog database does not support these scenarios.

The Prolog code can generate an initialization order, but this functionality has not been used for several reasons. The main reason for not generating the initialization order using the Prolog code is based on performance considerations. The approach taken in this paper does also identifies the strongly connected components and performs a particular initialization strategy of these.

### 2020-06-29 relatedwork.tex

\section{Related Work}
Prior work \cite{Gomes2019, BromanCompositionCo-Simulation} has been looking into the generation of co-simulation algorithms for both master and initialization algorithms for FMI-based scenarios based on a dependency graph of the operations of a co-simulation step. Gomes and Broman do both present an approach where they use the topological sorting of a dependency graph to establish a correct order of operations in a co-simulation step.
Gomes et al. \cite{Gomes2019} propose a strategy for the generation of co-simulation algorithms and define the criteria for a correct co-simulation step. Their work has many similarities with ours. However, their work does not look into the handling of algebraic loops and is not implemented as a real co-simulation framework. Furthermore, the approach taken in our work is only concerned with the initialization procedure of a co-simulation.

The work by Broman et al. \cite{BromanCompositionCo-Simulation} proposes using the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of port-operations. Nevertheless, they explicitly specify the requirement for cycle freedom in the dependency graph as a precondition for the generation of a deterministic co-simulation algorithm. It means they refuse all co-simulation scenarios containing algebraic loops. This is a significant difference to our approach that applies a fixed point iteration strategy to handle these scenarios. Also, the approach in this paper is more specialized in the sense that it is only considering the initialization of a co-simulation.

Amalio et al. \cite{Amalio2016CheckingCo-simulation} has been investigating how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS. The publication's purpose is like ours to avoid invalid co-simulation scenarios. Nevertheless, they achieve this by excluding scenarios containing algebraic loops. Their method is like ours also implemented in the real tool INTO-SysML, and it is based on using different kinds of formal methods (Theorem Proving and Model-checking) and will be an inspiration for the future work of formally verifying the plugin.

### 2020-06-29 background.tex
Updated some broken references

@@
 A fixed point iteration is converging if a finite number of iterations will make the difference of the output-value of the same operation between two following iterations within a certain threshold.\\
-$Convergence = \exists n \in \setnat: \forall \p \in LoopVariables \implies |f(p, n + 1) - f(p, n)| \leq T$\\
+$Convergence = \exists n \in \setnat: \forall p \in LoopVariables \implies |f(p, n + 1) - f(p, n)| \leq T$\\
 $f$ is the operation performed on a loop-variable p of a given iteration n.

### 2020-06-29 realization.tex
Updated some broken references

@@
 It calculates the specification based on a list of FMU-components of a co-simulation scenario, and a specific plugin-configuration to let the user supply initial values of FMU variables with $causality=parameter$.
-A correction initialization specification can be calculated by the plugin if the co-simulation scenario is adhering to definition \ref{def:convergence}.
+A correction initialization specification can be calculated by the plugin if the co-simulation scenario is adhering to the behavior dictated by definition given in \ref{def:convergence}.
 
-The plugin optimizes the initialization order by grouping operations that can be executed in \textit{parallel} to take advantage of FMI's ability to set or get multiple variables in bulk from the same FMU.
+The plugin optimizes the initialization order by grouping operations that can be executed in \textit{parallel} to take advantage of FMI's ability to \textit{set} or \textit{get} multiple variables in bulk from the same FMU.
 The criteria for this optimization is defined in definition \ref{def:optimization}.
@@
 The connection to Slang and Logika will be investigated in the future.
-The Logika framework will be used to formally verify the implementation plugin and be used to explore how the contract-based nature of Slang can be used to obtain more reliable results of co-simulations.
+The Logika framework will be used to formally verify the implemented plugin and be used to explore how the contract-based nature of Slang can be used to obtain more reliable results of co-simulations.
 The topological sorting returns a topological order of strongly connected components.
@@
 
-\subsection{Verification of the approach}
-The realized plugin and the developed approach have been verified in several different ways.
+\subsection{Verification of the calculated Initialization Order}
+The realized plugin has been verified in several different ways.
 Gomes et al.
-have in \cite{gomes_lucio_vangheluwe_2019} proved the correctness of using the topological order of a dependency graph of the interconnected variables to generate not only the initialization order but also the order for a co-simulation master-algorithm.
+have in \cite{gomes_lucio_vangheluwe_2019} proved the correctness of using the topological order of a dependency graph of the interconnected variables to generate not only the initialization order but also the order of operations for a co-simulation step in master-algorithm.
 The purpose of the publication by Gomes et al.
@@
 are interested in both generating an initialization and master-algorithm, meaning they also need to focus on the time of each FMU.
-They also define their graph based on FMU-operations ($Set, Get, doStep$) instead of interconnected variables, which is the approach described in this paper.
+They also define their graph based on FMU-operations (\textit{Set, Get, doStep}) instead of interconnected variables, which is the approach described in this paper.
 This simplification is valid since this approach only cares about initialization and, therefore, does not need to care about the time of each FMU.
-This does that we can omit all the $doStep$ nodes and all edges connected to them from the graph by Gomes et al., this approach does, therefore, end up with a subgraph of the graph by Gomes et al.
+This does that we can omit all the \textit{doStep} nodes and all edges connected to them from the graph by Gomes et al., this approach does, therefore, end up with a subgraph of the graph by Gomes et al.
 The proof from \cite{gomes_lucio_vangheluwe_2019} can therefore trivial be modified to the graph/approach presented in this paper.

### 2020-06-29 relatedwork.tex
Updated some broken references

@@
 Nevertheless, they achieve this by excluding scenarios containing algebraic loops.
-Their method is like ours also implemented in the real tool INTO-SysML, and it is based on using different kinds of formal methods (Theorem Proving and Model-checking) and will be an inspiration for the future work of formally verifying the plugin.
+Their method is like ours also implemented in the real tool INTO-SysML\cite{Miyazawa2016INtegratedModelling}, and it is based on using different kinds of formal methods (Theorem Proving and Model-checking) and will be an inspiration for the future work of formally verifying the plugin.

### 2020-06-29 initializationorder.tex
Added Initialization order file

--- 2020-06-29 paper.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
-\documentclass[runningheads]{llncs}
-
-\usepackage{graphicx}
-\usepackage{ae,aecompl}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage{verbatim}
-\usepackage{graphicx}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{stmaryrd}
-\usepackage{amstext}
-\usepackage{bm} 
-\let\proof\relax
-\let\endproof\relax
-\usepackage{amsthm}
-\usepackage{siunitx}
-\usepackage{mathrsfs}
-\usepackage{wrapfig}
-\usepackage{minted}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-\usepackage{semantic}
-\usepackage[dvipsnames]{xcolor}
-\usepackage{paralist}
-\usepackage{cite}
-\usepackage{url}
-\usepackage{todonotes}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
-\input{commands}
-
-\begin{document}
-%
-\title{An FMI-Based Initialization Plugin for INTO-CPS Maestro 2}
-%
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\author{Simon Thrane Hansen\inst{1} \and
-Casper Thule\inst{1} \and
-Claudio Gomes \inst{1}}
-%
-\authorrunning{S. Thrane et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{DIGIT, Department of Engineering, Aarhus University, \email{\{sth, casper.thule, claudio.gomes\}@eng.au.dk\}}}
-%
-\maketitle              % typeset the header of the contribution
-%
-
-\input{abstract.tex}
-
-\input{introduction.tex}
-
-\input{background.tex}
 \section{Calculation of an Initialization Order}\label{sc:initilization}
@@
 \end{itemize}
-The algorithm is furthermore well-established, and there exist formal proofs of its correctness and properties\cite{stefan_merz}.
+The algorithm is furthermore well-established, and there exist formal proofs of its correctness and properties\cite{stefanMerz}.
 The algorithm is among the most efficient graph algorithms for achieving the defined goals.
@@
 To perform all viable optimizations of a co-simulation step, a more advanced optimization strategy should be used, or this optimization strategy should be performed on the set of all valid co-simulation steps - yielding a potential very inefficient initialization algorithm.
-
-%This paper's main contribution is to calculate an initialization order of a co-simulation scenario potentially containing algebraic loops.
-The approach make the circular dependencies between the interconnected converge in the initialization, so the initial values of the interconnected variables in the system being simulated is stable at the time the co-simulation is started.
-
-\subsection{Case study}
-Claudio writes this section
-
-\input{realization.tex}
-
-\input{relatedwork.tex}
-
-\input{conclusion.tex}
-%
-% ---- Bibliography ---
-
-\bibliographystyle{splncs04}
-\bibliography{gen_bib}
-
-\end{document}

### 2020-06-29 paper.tex
Updated some broken references
Added Initialization order file

@@
 \usepackage{wrapfig}
-\usepackage{minted}
+%\usepackage{minted}
 \usepackage{algorithm}
@@
 \input{background.tex}
-\section{Calculation of an Initialization Order}\label{sc:initilization}
-FMI defines certain information about the initialization order described through different states of a co-simulation. The initialization phase covers the two states (in chronological order):
-\begin{itemize}
-    \item \textit{Instantiated}
-    \item \textit{Initialization Mode}
-\end{itemize}
-In each of the two states, different groups of FMU variables can be assigned a value.
-The groups are defined by FMI based on predicates on the characteristics of the variables (\textit{causality}, \textit{initial} and \textit{variability}).
-These predicates have been extracted and used in the implementation.
-An example of a group is the \textit{INI}-group that consists of FMU variables with $initial = exact\, \lor initial = \,approx $  and $variability \neq constant$.
-All variables of this group should be set in the \textit{Instantiated}-phase of a co-simulation, and since they have no dependencies/connections to other FMU variables, the order is insignificant.
-However, all variables of each FMU are group together to perform the fewest possible operations in the initialization.
 
-In the \textit{Initialization Mode} state all variables of all FMUs should be defined.
-The variables with \textit{causality = parameter} of each FMU are set first, and the order of which they are set is again insignificant as they are independent.
-Afterwards the interconnected variables should be defined, but as stated by the definitions \ref{def:feedthrough}, \ref{def:getout} and \ref{def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops places even more constraints on the initialization order.
-This phase should should also support algebraic loops, this support includes utilization of fixed point iteration and detection of non-convergence of algebraic loops.
-
-\subsection{Method to calculate the initialization order}
-This section describes the approach to calculate the initialization order of the interconnected FMU variables are based on the the method proposed in Gomes et al.
-\cite{Gomes2019b, BromanCompositionCo-Simulation}, but the approach used here has been extended with the ability to handle algebraic loops.
-The approach is formulated in pseudo-code in algorithm \ref{alg:initialization}.
-\begin{figure}[htb]
-  \centering
-    \begin{algorithm}[H]
-    \caption{Initialization strategy for Interconnected variables}
-    \label{alg:initialization}
-      \begin{algorithmic}[1]
-        \State $InitializationGraph \gets createGraph(connections)$
-        \State $SCCS \gets Tarjan(InitializationGraph)$
-        \State $OptimizeInitializationOrder(SCCS)$
-        \ForEach {$SCC \in SCCS$}
-            \If {$isAlgebraicLoop(SCC)$}
-                \State $applyFixedPointIteration(SCC)$;
-            \Else
-                \State $initializeVariable(SCC)$;
-            \EndIf
-        \EndFor
-        \end{algorithmic}
-    \end{algorithm}
-\end{figure}
-
-\subsubsection{Structure of the graph}
-The initialization algorithm starts by building a directed graph of the dependency between the interconnected variables of the FMUs.
-The graph is constructed based on the interconnected variables and internal connections (feed-through).
-Each interconnected variable in the system represents a node, and the edges are based on these connections.
-The edges of this graph represent precedence constraints based on the algebraic dependencies of the interconnected variables.
-Please see definition \ref{def:initialization_graph} for a formal definition of the graph.
-
-\begin{definition}[Initialization Graph]\label{def:initialization_graph}
-  Given a co-simulation scenario $\tuple{\fmus, \coupling}$, and a set of feed-through dependencies $\bigcup_{c \in \fmus} \set{\feedthrough{c}}$, we define the Initialization Graph where each node represents a port $\outputvar{c} \in \outputs{c}$ or $\inputvar{c} \in \inputs{c}$ of some fmu $c \in \fmus$.
-The edges are created according to the following rules:
-  \begin{compactenum}
-    \item For each $c \in \fmus$ and $\inputvar{c} \in \inputs{c}$, if $\coupling(\inputvar{c}) = \outputvar{d}$, add an edge $\outputvar{d} -> \inputvar{c}$.
-    \item For each $c \in \fmus$ and $(\inputvar{c},\outputvar{c}) \in \feedthrough{c}$, add an edge $\inputvar{c} -> \outputvar{c}$.
-  \end{compactenum}
-\end{definition}
-
-As described earlier, not all co-simulation scenarios are valid, and these invalid scenarios need to be identified.
-This is done by monitoring convergence of all algebraic loops.
-A valid co-simulation scenario must convergence by definition given in definition \ref{def:convergence}.
-
-\subsubsection{Calculation of an initialization order}
-The topological ordering of the graph defined in definition \ref{def:initialization_graph} is used as the initialization order of the interconnected FMU variables.
-The elements of the topological order are the strongly connected components of the graphs.
-The strongly connected components are potentially algebraic loops of the system.
-The algebraic loops are easily identified as the strongly connected components containing more than a single element.
-The single element members of the topological order are standard interconnected FMU variables, whose port operation should only be performed once during the initialization procedure.
-\\
-The calculation of an initialization order is performed in linear time based on the number of both external and internal connections using Tarjan's algorithm \cite{tarjan_1972}.
-This algorithm was selected since it solves two of the central issues of the initialization-phase of the co-simulation.
-\begin{itemize}
-    \item Identifies algebraic loops between interconnected variables (strongly connected components)
-    \item Performs a topological sorting of the Strongly Connected Components
-\end{itemize}
-The algorithm is furthermore well-established, and there exist formal proofs of its correctness and properties\cite{stefan_merz}.
-The algorithm is among the most efficient graph algorithms for achieving the defined goals.
-Tarjan's algorithm is performing a topological sorting of the strongly connected components of a graph. This makes it able to handle both graphs with and without algebraic loops.
-
-\todo{Come with an example using a graph with loops}
-
-\subsubsection{Handling of algebraic loops}
-As described earlier, it is essential to handle the algebraic loops by a particular initialization strategy since they otherwise would invalidate the result of the co-simulation.
-The strategy for managing algebraic loops is to identify and initialize them using a fixed point iteration until convergence.
-Because convergence is not guaranteed, it should be monitored, and if convergence can not be established within a finite number of iteration, the co-simulation should be rejected.
-
-\subsection{Optimization of a Initialization Procedure}
-An initialization procedure can be optimized by using the fact that the FMI specification allows multiple \textit{set} or \textit{get} operations of the same FMU to be performed in bulk by grouping them together to a single operation over multiple variables with similar characteristic.
-The criteria of optimization can of an initialization procedure is formalized in definition \ref{def:optimization}
-\begin{definition}[Optimization of a Initialization procedure]\label{def:optimization}
-  Given an initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ with a finite ordered sequence of FMU function calls $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}},$ and $i$ denoting the order of the function call.
-It can be optimized if $\exists \functioncall_i, \functioncall_{i +1} \in \allfunctioncalls : \exists c \in \fmus :(\functioncall_i \in {\fset{c}} \land \functioncall_{i+1} \in {\fset{c}}) \lor (\functioncall_i \in {\fget{c}} \land \functioncall_{i+1} \in {\fget{c}})$
-\end{definition}
-Since an Initialization procedure is defined in the same way as other co-simulation steps, the optimization criteria described in definition \ref{def:optimization} is valid for an arbitrary co-simulation step.
-\\
-The correctness of this optimization can be established by the proof of using the Initialization Graph's topological ordering as the initialization order described by Gomes et al.
-\cite{Gomes2019}.
-This proof is still valid since this optimization does not change the structure of the Initialization Graph.
-\\
-A limitation of this optimization strategy is that it is not guaranteed to find all potentially valid optimizations of a co-simulation scenario.
-Considering it works only on a specific co-simulation step (a topological order of a graph), which is not necessarily unique for a given co-simulation scenario/graph.
-To perform all viable optimizations of a co-simulation step, a more advanced optimization strategy should be used, or this optimization strategy should be performed on the set of all valid co-simulation steps - yielding a potential very inefficient initialization algorithm.
+\input{initializationorder.tex}
 

### 2020-06-29 background.tex
Added some based on the feedback from Christian

@@
 The set of interconnected variables in an algebraic loop is defined as: $LoopVariables = \{v | v \in V : Path(v,v)\}$ \\
-An algebraic loop is defined as the set $\{p_1, p_2 | p_1, p_2 \in LoopVariables: Path(p_1, p_2) \land Path(p_1, p_2)\}$\todo{Look at this}\\
+An algebraic loop is defined as the set $\{p_1, p_2 | p_1, p_2 \in LoopVariables: Path(p_1, p_2) \land Path(p_2, p_1)\}$\todo{Look at this - can it be specified better?}\\
 Path is defined as the transitive closure of the set of relations: $\bigcup_{c \in \fmus} \set{\feedthrough{c}} \cup \coupling$\\
@@
 The operations should be performed until the system converge.
+An example of applying a fixed point iteration can be seen in Figure \ref{} where a bigger system contains an algebraic loop.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics{images/fmu_cycle.pdf}
+    \caption{Co-simulation scenario with cycle}
+    \label{fig:fmu_cycle}
+\end{figure}
+
+The initialization of the system requires application of fixed point iteration as defined by definition \ref{def:fixedpoint}.
+
+\begin{definition}[Fixed point iteration of an Initialization procedure]\label{def:fixedpoint}
+Given an Initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ of a co-simulation $\tuple{\fmus, \coupling}$ where $LoopVariables \neq \emptyset$.\\
+Fixed point iteration should be used by 
+$\forall v \in LoopVariables $
+
+\end{definition}
+
 However a fixed point iteration technique is not guaranteed to convergence if the system is unstable.
 This means that an upper bound of the number of repetitions needs to be established to ensure termination.
-In case of a non-converging algebraic loop this should be treated as an incorrect co-simulation scenario and the simulation should be stopped.
+In case of a non-converging algebraic loop the simulation should be stopped since the result of the co-simulation scenario wouldn't be trustworthy.
 The criteria of a valid co-simulation scenario is is specified in definition \ref{def:convergence}.
 
-\todo{Christian should I add some pseudo code to explain?}
 \begin{definition}[Convergence of Fixed point iteration]\label{def:convergence}

### 2020-06-29 initializationorder.tex
Added some based on the feedback from Christian

@@
 \section{Calculation of an Initialization Order}\label{sc:initilization}
-FMI defines certain information about the initialization order described through different states of a co-simulation. The initialization phase covers the two states (in chronological order):
+The FMI specification defines certain information about the initialization order described through different states of a co-simulation.
+The initialization phase covers the two states (in chronological order):
 \begin{itemize}
@@
 In each of the two states, different groups of FMU variables can be assigned a value.
-The groups are defined by FMI based on predicates on the characteristics of the variables (\textit{causality}, \textit{initial} and \textit{variability}).
-These predicates have been extracted and used in the implementation.
-An example of a group is the \textit{INI}-group that consists of FMU variables with $initial = exact\, \lor initial = \,approx $  and $variability \neq constant$.
+The groups are defined by FMI based on rules on the characteristics of the variables (\textit{causality}, \textit{initial} and \textit{variability}).
+These rules have been extracted as predicates and used in the implementation.
+An example of a group from the FMI specification is the \textit{INI}-group that consists of FMU variables with $initial = exact\, \lor initial = \,approx $  and $variability \neq constant$.
 All variables of this group should be set in the \textit{Instantiated}-phase of a co-simulation, and since they have no dependencies/connections to other FMU variables, the order is insignificant.
-However, all variables of each FMU are group together to perform the fewest possible operations in the initialization.
+However, all variables of each FMU are grouped together to perform the fewest possible operations in the initialization.
 
@@
 \cite{Gomes2019b, BromanCompositionCo-Simulation}, but the approach used here has been extended with the ability to handle algebraic loops.
-The approach is formulated in pseudo-code in algorithm \ref{alg:initialization}.
-\begin{figure}[htb]
-  \centering
-    \begin{algorithm}[H]
-    \caption{Initialization strategy for Interconnected variables}
-    \label{alg:initialization}
-      \begin{algorithmic}[1]
-        \State $InitializationGraph \gets createGraph(connections)$
-        \State $SCCS \gets Tarjan(InitializationGraph)$
-        \State $OptimizeInitializationOrder(SCCS)$
-        \ForEach {$SCC \in SCCS$}
-            \If {$isAlgebraicLoop(SCC)$}
-                \State $applyFixedPointIteration(SCC)$;
-            \Else
-                \State $initializeVariable(SCC)$;
-            \EndIf
-        \EndFor
-        \end{algorithmic}
-    \end{algorithm}
-\end{figure}
 
@@
 
+The entire approach of the initialization of interconnected variables is formulated in pseudo-code in algorithm \ref{alg:initialization}.
+\begin{figure}[htb]
+  \centering
+    \begin{algorithm}[H]
+    \caption{Initialization strategy for Interconnected variables}
+    \label{alg:initialization}
+      \begin{algorithmic}[1]
+        \State $InitializationGraph \gets createGraph(connections)$
+        \State $SCCS \gets Tarjan(InitializationGraph)$
+        \State $OptimizeInitializationOrder(SCCS)$
+        \ForEach {$SCC \in SCCS$}
+            \If {$isAlgebraicLoop(SCC)$}
+                \State $applyFixedPointIteration(SCC)$;
+            \Else
+                \State $initializeVariable(SCC)$;
+            \EndIf
+        \EndFor
+        \end{algorithmic}
+    \end{algorithm}
+\end{figure}
+
 \subsection{Optimization of a Initialization Procedure}

### 2020-06-29 introduction.tex
Added some based on the feedback from Christian

@@
 The precedence constraints between the variables can introduce algebraic loops, which places particular requirements on the initialization order since the algebraic loops require a particular initialization strategy to be applied to calculate the initial values of the variables in the algebraic loop\cite{Bastian2011a}.
-The order of initialization is vital for the correctness of the co-simulation \cite{Thule2018} because it ensures a variable is never read before it is set like the classical \textit{readers–writers problem} and to make sure that all initial values have stabilized at the start of the simulation.
+An algebraic loops occur whenever there is an interconnected FMU variable that indirectly depends on itself.
+Algebraic loops introduce specific challenges in the co-simulation, and studies have shown that neglecting a loop can lead to a prohibitively high error in the co-simulation \cite{Kubler2000}.
+The order of initialization is vital for ensuring the correctness of the co-simulation \cite{Thule2018} because it ensures a variable is never read before it is set like the classical \textit{readers–writers problem} and to make sure that all initial values have stabilized at the start of the simulation.
 
-\noindent Algebraic loops occur whenever there is an interconnected FMU variable that indirectly depends on itself.
-Algebraic loops introduce specific challenges in the co-simulation, and studies have shown that neglecting a loop can lead to a prohibitively high error in the co-simulation \cite{Kubler2000}.
-Other approaches for the generation of co-simulation algorithms have avoided co-simulation scenarios containing algebraic loops since their presence reduces the chance of obtaining a valid co-simulation result\cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}.
+\noindent Other approaches for the generation of co-simulation algorithms have avoided co-simulation scenarios containing algebraic loops since their presence reduces the chance of obtaining a valid co-simulation result\cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}.
 This choice is motivated by the fact that not all co-simulation scenarios containing algebraic loops are valid since some algebraic loops have a divergent nature.
-However, experience has shown that valid co-simulation scenarios containing algebraic loops exist, and a well-established co-simulation framework should be able to handle these scenarios.
+However, experience has shown that valid co-simulation scenarios containing algebraic loops exist like \todo{Claudio can you help me come up with an example?
+Maybe some kind of feedback control}, and a well-established co-simulation framework should be able to handle these scenarios.
 

### 2020-06-30 casestudy.tex
add seprarte case study file

--- 2020-06-29 paper.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
-\documentclass[runningheads]{llncs}
-
-\usepackage{graphicx}
-\usepackage{ae,aecompl}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage{verbatim}
-\usepackage{graphicx}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{stmaryrd}
-\usepackage{amstext}
-\usepackage{bm} 
-\let\proof\relax
-\let\endproof\relax
-\usepackage{amsthm}
-\usepackage{siunitx}
-\usepackage{mathrsfs}
-\usepackage{wrapfig}
-%\usepackage{minted}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-\usepackage{semantic}
-\usepackage[dvipsnames]{xcolor}
-\usepackage{paralist}
-\usepackage{cite}
-\usepackage{url}
-\usepackage{todonotes}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
-\input{commands}
-
-\begin{document}
-%
-\title{An FMI-Based Initialization Plugin for INTO-CPS Maestro 2}
-%
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\author{Simon Thrane Hansen\inst{1} \and
-Casper Thule\inst{1} \and
-Claudio Gomes \inst{1}}
-%
-\authorrunning{S. Thrane et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{DIGIT, Department of Engineering, Aarhus University, \email{\{sth, casper.thule, claudio.gomes\}@eng.au.dk\}}}
-%
-\maketitle              % typeset the header of the contribution
-%
-
-\input{abstract.tex}
-
-\input{introduction.tex}
-
-\input{background.tex}
-
-\input{initializationorder.tex}
+\section{Case study}
 
@@
 
-\subsection{Case study}
 Claudio writes this section
-
-\input{realization.tex}
-
-\input{relatedwork.tex}
-
-\input{conclusion.tex}
-%
-% ---- Bibliography ---
-
-\bibliographystyle{splncs04}
-\bibliography{gen_bib}
-
-\end{document}

### 2020-06-30 background.tex
Updates from Overleaf

@@
 \begin{definition}[Algebraic loops] 
-The set of interconnected variables in an algebraic loop is defined as: $LoopVariables = \{v | v \in V : Path(v,v)\}$ \\
-An algebraic loop is defined as the set $\{p_1, p_2 | p_1, p_2 \in LoopVariables: Path(p_1, p_2) \land Path(p_2, p_1)\}$\todo{Look at this - can it be specified better?}\\
+The set of interconnected variables in an algebraic loop is defined as: $\LoopVariables = \{v | v \in V : Path(v,v)\}$ \\
+An algebraic loop is defined as the set $\{p_1, p_2 | p_1, p_2 \in \LoopVariables: Path(p_1, p_2) \land Path(p_2, p_1)\}$\todo{Look at this - can it be specified better?}\\
 Path is defined as the transitive closure of the set of relations: $\bigcup_{c \in \fmus} \set{\feedthrough{c}} \cup \coupling$\\
@@
 The operations should be performed until the system converge.
-An example of applying a fixed point iteration can be seen in Figure \ref{} where a bigger system contains an algebraic loop.
+An example of applying a fixed point iteration can be seen in Figure \ref{def:fixedpoint} where a system containing an algebraic loop has to be initialized using fixed point iteration.
 
@@
     \centering
-    \includegraphics{images/fmu_cycle.pdf}
-    \caption{Co-simulation scenario with cycle}
-    \label{fig:fmu_cycle}
+    \includegraphics[width=0.8\textwidth]{images/fixedpoint.pdf}
+    \caption{Fixed point iteration in a co-simulation scenario}
+    \label{fig:fixedpont}
 \end{figure}
@@
 The initialization of the system requires application of fixed point iteration as defined by definition \ref{def:fixedpoint}.
-
 \begin{definition}[Fixed point iteration of an Initialization procedure]\label{def:fixedpoint}
-Given an Initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ of a co-simulation $\tuple{\fmus, \coupling}$ where $LoopVariables \neq \emptyset$.\\
+Given an Initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ of a co-simulation $\tuple{\fmus, \coupling}$ where $\LoopVariables \neq \emptyset$.\\
 Fixed point iteration should be used by 
-$\forall v \in LoopVariables $
+$\forall v \in \LoopVariables $
 
@@
 A fixed point iteration is converging if a finite number of iterations will make the difference of the output-value of the same operation between two following iterations within a certain threshold.\\
-$Convergence = \exists n \in \setnat: \forall p \in LoopVariables \implies |f(p, n + 1) - f(p, n)| \leq T$\\
+$Convergence = \exists n \in \setnat: \forall p \in \LoopVariables \implies |f(p, n + 1) - f(p, n)| \leq T$\\
 $f$ is the operation performed on a loop-variable p of a given iteration n.

### 2020-06-30 realization.tex
Updates from Overleaf

@@
 
-\subsection{Verification of the calculated Initialization Order}
-The realized plugin has been verified in several different ways.
+\subsection{Verification of the Initialization Order}
+The realized plugin has been verified in several ways using traditional proof methods and practical verification against an established co-simulation Verifier.
+The approach behind the plugin has been verified by Gomes et al.
+that in \cite{gomes_lucio_vangheluwe_2019} proved the correctness of using the topological order of a dependency graph of the interconnected variables to generate for the order of the operations that need to be performed in a co-simulation step (both the initialization procedure and an arbitrary step).
 Gomes et al.
-have in \cite{gomes_lucio_vangheluwe_2019} proved the correctness of using the topological order of a dependency graph of the interconnected variables to generate not only the initialization order but also the order of operations for a co-simulation step in master-algorithm.
-The purpose of the publication by Gomes et al.
-is a little different from the one of this paper.
-Gomes et al.
-are interested in both generating an initialization and master-algorithm, meaning they also need to focus on the time of each FMU.
-They also define their graph based on FMU-operations (\textit{Set, Get, doStep}) instead of interconnected variables, which is the approach described in this paper.
-This simplification is valid since this approach only cares about initialization and, therefore, does not need to care about the time of each FMU.
-This does that we can omit all the \textit{doStep} nodes and all edges connected to them from the graph by Gomes et al., this approach does, therefore, end up with a subgraph of the graph by Gomes et al.
-The proof from \cite{gomes_lucio_vangheluwe_2019} can therefore trivial be modified to the graph/approach presented in this paper.
+used a graph based on FMU-operations (\textit{Set, Get, doStep}) instead of interconnected variables, which is the approach described in this paper.
+The simplification of using the interconnected variables is valid since this approach only cares about initialization and, therefore, does not need to care about the time of each FMU.
+This does that we can omit all the \textit{doStep} nodes, it means that each interconnected variable can only perform one of the two operations \textit{get} or \textit{set} as described by the definitions \ref{def:getout} and \ref{def:setin}.
+This approach does, therefore, end up with a subgraph of the graph by Gomes et al.
+The proof from \cite{gomes_lucio_vangheluwe_2019} can trivially be modified to the graph/approach presented in this paper.
 
-Gomes et al.'s main contribution is an implementation of the FMI specification in Prolog freely available to be used in other projects.
-The Prolog implementation was used in their research to verify their proposed approach for the generation of co-simulation algorithms.
+\subsubsection{Practical verification against a Verifier} 
+Gomes et al.'s main contribution is an implementation of the criteria for a valid FMI based co-simulation in Prolog freely available to be used in other projects\footnote{\url{}}.
+The Prolog implementation was used in their research to formally verify their proposed approach for the generation of co-simulation algorithms.
 The realization encapsulates all the rules of a valid master-algorithm and an initialization algorithm.
-As a part of this work, an integration from this plugin has been realized to interact with the Prolog realization.
-This integration has been realized in order to verify the correctness of the calculated initialization order against an established and recognized method.
-The integration is querying the Prolog database with a co-simulation environment and an initialization order.
+As a part of this work, an integration from the developed plugin has been realized to interact with the Prolog Verifier.
+This integration has been realized to verify the correctness of the calculated initialization order against an established and recognized co-simulation Algorithm Generator and Verifier.
+The integration works by querying the Prolog database with a co-simulation environment and a calculated initialization to verify the order's correctness.
 The integration requires a transformation of the dependency graph (see definition \ref{def:initialization_graph}) used in the plugin to a graph of FMU operations.
@@
 The Prolog code can generate an initialization order, but this functionality has not been used for several reasons.
-The main reason for not generating the initialization order using the Prolog code is based on performance considerations.
+The main reason for not creating the initialization order using the Prolog code is based on performance considerations.
 The approach taken in this paper does also identifies the strongly connected components and performs a particular initialization strategy of these.

### 2020-06-30 abstract.tex
minor improvements

@@
 \begin{abstract}
-The development of cyber-physical systems (CPS) is challenging due to the heterogeneity of the different subsystems.
-Co-simulation can be used to assist in the development process, where models of constituents of a CPS are coupled to simulate the behavior of the full system jointly.
-However, an accurate result of the co-simulation is dependent on the correct initialization of all the simulation units.
+The accuracy of the result in a co-simulation is dependent on the correct initialization of all the simulation units.
 In this work, we consider co-simulation where the simulation units are described as Functional Mock-up Units (FMU).
@@
 The approach taken to calculate a correct initialization order is based on predicates from the FMI specification and the topological ordering of both internal connections and interconnected variables.
-The approach supports the initialization of algebraic loops using fixed point iteration.%  dependencies between FMU variables are dismissed.
+The approach supports the initialization of algebraic loops using fixed point iteration.
+%  dependencies between FMU variables are dismissed.
 %This approach has been compared to other already existing approaches for FMI initialization.

### 2020-06-30 introduction.tex
minor improvements

@@
 One of the tools used to manage the increasing complexity of such systems is co-simulation since it addresses their various parts of heterogeneous nature.
-Co-simulation is a technique to combine multiple black-box simulation units to simulate/compute the behavior of the combined models as a discrete trace\cite{Kubler2000}.
+Co-simulation is a technique to combine multiple black-box simulation units to simulate/compute the behavior of the combined models as a discrete trace (see, e.g., \cite{Kubler2000,Gomes2018}).
 The simulation units, often developed independently from each other, are coupled using a master algorithm, also often developed independently, that communicates with each simulation unit via its interface.
@@
 An algebraic loops occur whenever there is an interconnected FMU variable that indirectly depends on itself.
-Algebraic loops introduce specific challenges in the co-simulation, and studies have shown that neglecting a loop can lead to a prohibitively high error in the co-simulation \cite{Kubler2000}.
-The order of initialization is vital for ensuring the correctness of the co-simulation \cite{Thule2018} because it ensures a variable is never read before it is set like the classical \textit{readers–writers problem} and to make sure that all initial values have stabilized at the start of the simulation.
+Algebraic loops introduce specific challenges in the co-simulation, and studies have shown that neglecting a loop can lead to a prohibitively high error in the co-simulation \cite{Arnold2014}.
+The order of initialization is vital for ensuring the correctness of the co-simulation \cite{Thule2018} because it ensures a variable is never read before it is set like the classical \textit{readers–writers problem} and to make sure that all initial values have converged at the start of the simulation.
 
@@
 The realized plugin has been tested for various co-simulation scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial applications. 
-Furthermore, the calculated initialization order is systematically verified by an established co-simulation Algorithm Generator and Verifier by Gomes et al.
-implemented in Prolog \cite{gomes_lucio_vangheluwe_2019}.
-\\
+Furthermore, the calculated initialization order is systematically verified by co-simulation algorithm verifier introduced in \cite{gomes_lucio_vangheluwe_2019}. \\
 

### 2020-06-30 background.tex
minor improvements
fixed problem with doi
Changed the order of the initialization algorithm

@@
 \subsection{FMU definitions}
-To describe the formalization of FMUs, the vocabulary from Gomes et al\cite{gomes_lucio_vangheluwe_2019, Gomes2018} is adopted.
+To describe the formalization of FMUs, we adopt the vocabulary from \cite{gomes_lucio_vangheluwe_2019,Gomes2018}.
 The main definitions of relevance to this paper will be presented, but readers are referred to the original publications for more information.
@@
 \begin{definition}[Scenario]\label{def:cosim_scenario}
-  A scenario is a structure $\tuple{\fmus, \coupling}$ where each identifier $c \in \fmus$ is associated with an FMU, as defined in \ref{def:fmu}, and $\coupling(u)=y$ means that the output $y$ is connected to input $u$.
+  A scenario is a structure $\tuple{\fmus, \coupling}$ where each identifier $c \in \fmus$ is associated with an FMU, as defined in \cref{def:fmu}, and $\coupling(u)=y$ means that the output $y$ is connected to input $u$.
   Let $\allinputs = \bigcup_{c \in \fmus} \inputs{c}$ and $\alloutputs = \bigcup_{c \in \fmus} \outputs{c}$, then $\coupling : \allinputs \to \alloutputs$.
@@
 
+A graph of the dependencies of a co-simulation scenario is established from the interconnected variables by \cref{def:initialization_graph}.
+The graph is the foundation for the calculation of the initialization procedure and is therefore referred to as the Initialization Graph.
+
+\begin{definition}[Initialization Graph]\label{def:initialization_graph}
+  Given a co-simulation scenario $\tuple{\fmus, \coupling}$, and a set of feed-through dependencies $\bigcup_{c \in \fmus} \set{\feedthrough{c}}$, we define the Initialization Graph where each node represents a port $\outputvar{c} \in \outputs{c}$ or $\inputvar{c} \in \inputs{c}$ of some fmu $c \in \fmus$.
+The edges are created according to the following rules:
+  \begin{compactenum}
+    \item For each $c \in \fmus$ and $\inputvar{c} \in \inputs{c}$, if $\coupling(\inputvar{c}) = \outputvar{d}$, add an edge $\outputvar{d} -> \inputvar{c}$.
+    \item For each $c \in \fmus$ and $(\inputvar{c},\outputvar{c}) \in \feedthrough{c}$, add an edge $\inputvar{c} -> \outputvar{c}$.
+  \end{compactenum}
+\end{definition}
+
 The interconnections of FMU variables can lead to circular dependencies between these.
 The following definitions will formalize the concept of an algebraic loop in a co-simulation scenario, and define the problem these loops are introducing in the system.
-A co-simulation scenario containing an algebraic loop is shown in Figure \ref{fig:fmu_cycle}.
+A co-simulation scenario containing an algebraic loop is shown in \cref{fig:fmu_cycle}.
 
@@
 \begin{definition}[Algebraic loops] 
-The set of interconnected variables in an algebraic loop is defined as: $\LoopVariables = \{v | v \in V : Path(v,v)\}$ \\
+The set of interconnected variables in an algebraic loop is defined as a strongly connected component of the graph in \cref{def:initialization_graph}. \\
+A strongly connected component: $SCC = v \in V: Path(v,v)$\\
+$\LoopVariables = \{v | v \in V : Path(v,v)\}$ \\
 An algebraic loop is defined as the set $\{p_1, p_2 | p_1, p_2 \in \LoopVariables: Path(p_1, p_2) \land Path(p_2, p_1)\}$\todo{Look at this - can it be specified better?}\\
-Path is defined as the transitive closure of the set of relations: $\bigcup_{c \in \fmus} \set{\feedthrough{c}} \cup \coupling$\\
-The algebraic dependency will lead to the following difference between performing to following :
+Path is defined as the transitive closure of the edges of the graph denoted by \cref{def:initialization_graph}.\\
 \todo{Claudio check this definition and add a formalization of the challenge introduced}
@@
 
-As described by definition \ref{def:challenge} the algebraic loops introduce certain challenges in the system.
+As described by \cref{def:challenge} the algebraic loops introduce certain challenges in the system.
 This means that algebraic loops needs to be handled using fixed point iterations\cite{Gomes2018}.
@@
 The operations should be performed until the system converge.
-An example of applying a fixed point iteration can be seen in Figure \ref{def:fixedpoint} where a system containing an algebraic loop has to be initialized using fixed point iteration.
+An example of applying a fixed point iteration can be seen in \cref{def:fixedpoint} where a system containing an algebraic loop has to be initialized using fixed point iteration.
 
@@
 
-The initialization of the system requires application of fixed point iteration as defined by definition \ref{def:fixedpoint}.
+The initialization of the system requires application of fixed point iteration as defined by \cref{def:fixedpoint}.
 \begin{definition}[Fixed point iteration of an Initialization procedure]\label{def:fixedpoint}
@@
 In case of a non-converging algebraic loop the simulation should be stopped since the result of the co-simulation scenario wouldn't be trustworthy.
-The criteria of a valid co-simulation scenario is is specified in definition \ref{def:convergence}.
+The criteria of a valid co-simulation scenario is is specified in \cref{def:convergence}.
 

### 2020-06-30 conclusion.tex
Changed the order of the initialization algorithm

@@
 
-\paragraph*{\textbf{Acknowlegements.}}We would like to thank Stefan Hallerstede and Peter Gorm Larsen for providing valuable input to this paper and the developed plugin.
+\paragraph*{\textbf{Acknowlegements.}}We would like to thank Stefan Hallerstede, Christian Møldrup Legaard and Peter Gorm Larsen for providing valuable input to this paper and the developed plugin.

### 2020-06-30 initializationorder.tex
Changed the order of the initialization algorithm

@@
 
-\begin{definition}[Initialization Graph]\label{def:initialization_graph}
-  Given a co-simulation scenario $\tuple{\fmus, \coupling}$, and a set of feed-through dependencies $\bigcup_{c \in \fmus} \set{\feedthrough{c}}$, we define the Initialization Graph where each node represents a port $\outputvar{c} \in \outputs{c}$ or $\inputvar{c} \in \inputs{c}$ of some fmu $c \in \fmus$.
-The edges are created according to the following rules:
-  \begin{compactenum}
-    \item For each $c \in \fmus$ and $\inputvar{c} \in \inputs{c}$, if $\coupling(\inputvar{c}) = \outputvar{d}$, add an edge $\outputvar{d} -> \inputvar{c}$.
-    \item For each $c \in \fmus$ and $(\inputvar{c},\outputvar{c}) \in \feedthrough{c}$, add an edge $\inputvar{c} -> \outputvar{c}$.
-  \end{compactenum}
-\end{definition}
-
 As described earlier, not all co-simulation scenarios are valid, and these invalid scenarios need to be identified.
@@
 
-The entire approach of the initialization of interconnected variables is formulated in pseudo-code in algorithm \ref{alg:initialization}.
+\subsection{Optimization of a Initialization Procedure}
+An initialization procedure can be optimized by using the fact that the FMI specification allows multiple \textit{set} or \textit{get} operations of the same FMU to be performed in bulk by grouping them together to a single operation over multiple variables with similar characteristic.
+The criteria of optimization can of an initialization procedure is formalized in definition \ref{def:optimization}
+\begin{definition}[Optimization of a Initialization procedure]\label{def:optimization}
+  Given an initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ with a finite ordered sequence of FMU function calls $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}},$ and $i$ denoting the order of the function call.
+It can be optimized if $\exists \functioncall_i, \functioncall_{i +1} \in \allfunctioncalls : \exists c \in \fmus :(\functioncall_i \in {\fset{c}} \land \functioncall_{i+1} \in {\fset{c}}) \lor (\functioncall_i \in {\fget{c}} \land \functioncall_{i+1} \in {\fget{c}})$
+\end{definition}
+Since an Initialization procedure is defined in the same way as other co-simulation steps, the optimization criteria described in definition \ref{def:optimization} is valid for an arbitrary co-simulation step.
+\\
+The correctness of this optimization can be established by the proof of using the Initialization Graph's topological ordering as the initialization order described by Gomes et al.
+\cite{Gomes2019}.
+This proof is still valid since this optimization does not change the structure of the Initialization Graph.
+\\
+A limitation of this optimization strategy is that it is not guaranteed to find all potentially valid optimizations of a co-simulation scenario.
+Considering it works only on a specific co-simulation step (a topological order of a graph), which is not necessarily unique for a given co-simulation scenario/graph.
+To perform all viable optimizations of a co-simulation step, a more advanced optimization strategy should be used, or this optimization strategy should be performed on the set of all valid co-simulation steps - yielding a potential very inefficient initialization algorithm.
+
+\subsection{The entire Initialization Strategy}
+The pseudo-code in \cref{alg:initialization} formulates the entire initialization strategy of the interconnected variables of a co-simulation scenario.
 \begin{figure}[htb]
@@
 \end{figure}
-
-\subsection{Optimization of a Initialization Procedure}
-An initialization procedure can be optimized by using the fact that the FMI specification allows multiple \textit{set} or \textit{get} operations of the same FMU to be performed in bulk by grouping them together to a single operation over multiple variables with similar characteristic.
-The criteria of optimization can of an initialization procedure is formalized in definition \ref{def:optimization}
-\begin{definition}[Optimization of a Initialization procedure]\label{def:optimization}
-  Given an initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ with a finite ordered sequence of FMU function calls $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}},$ and $i$ denoting the order of the function call.
-It can be optimized if $\exists \functioncall_i, \functioncall_{i +1} \in \allfunctioncalls : \exists c \in \fmus :(\functioncall_i \in {\fset{c}} \land \functioncall_{i+1} \in {\fset{c}}) \lor (\functioncall_i \in {\fget{c}} \land \functioncall_{i+1} \in {\fget{c}})$
-\end{definition}
-Since an Initialization procedure is defined in the same way as other co-simulation steps, the optimization criteria described in definition \ref{def:optimization} is valid for an arbitrary co-simulation step.
-\\
-The correctness of this optimization can be established by the proof of using the Initialization Graph's topological ordering as the initialization order described by Gomes et al.
-\cite{Gomes2019}.
-This proof is still valid since this optimization does not change the structure of the Initialization Graph.
-\\
-A limitation of this optimization strategy is that it is not guaranteed to find all potentially valid optimizations of a co-simulation scenario.
-Considering it works only on a specific co-simulation step (a topological order of a graph), which is not necessarily unique for a given co-simulation scenario/graph.
-To perform all viable optimizations of a co-simulation step, a more advanced optimization strategy should be used, or this optimization strategy should be performed on the set of all valid co-simulation steps - yielding a potential very inefficient initialization algorithm.

### 2020-06-30 realization.tex
Changed the order of the initialization algorithm

@@
 \subsection{Realization of the Topological Sorting}
-The topological sorting algorithm (Tarjan's Algorithm) was implemented in Scala.
+The topological sorting algorithm (Tarjan's Algorithm) is implemented in Scala.
 The motivation for choosing Scala is its relation to JVM and the connection to Slang and the Logika framework\cite{inbook}.
@@
 \subsection{Verification of the Initialization Order}
-The realized plugin has been verified in several ways using traditional proof methods and practical verification against an established co-simulation Verifier.
+The realized plugin is verified in several ways using traditional proof methods and practical verification against an established co-simulation Verifier.
 The approach behind the plugin has been verified by Gomes et al.
@@
 \subsubsection{Practical verification against a Verifier} 
-Gomes et al.'s main contribution is an implementation of the criteria for a valid FMI based co-simulation in Prolog freely available to be used in other projects\footnote{\url{}}.
+Gomes et al.'s main contribution is an implementation of the criteria for a valid FMI based co-simulation in Prolog freely available to be used in other projects\footnote{\url{http://msdl.cs.mcgill.ca/people/claudio/projs/PrologCosimGeneration.zip}}.
 The Prolog implementation was used in their research to formally verify their proposed approach for the generation of co-simulation algorithms.

### 2020-06-30 background.tex
Updated images in background section

@@
 
-The interconnections of FMU variables can lead to circular dependencies between these.
-The following definitions will formalize the concept of an algebraic loop in a co-simulation scenario, and define the problem these loops are introducing in the system.
-A co-simulation scenario containing an algebraic loop is shown in \cref{fig:fmu_cycle}.
+The interconnections of FMU variables can lead to circular dependencies between these as seen in \cref{fig:fmu_cycle} showing a co-simulation scenario containing an algebraic loop and its Initialization Graph.
 
-\begin{figure}
+\begin{figure}[H]
     \centering
-    \includegraphics{images/fmu_cycle.pdf}
-    \caption{Co-simulation scenario with cycle}
+    \begin{minipage}{0.55\textwidth}
+        \centering
+    \includegraphics[width=1\textwidth]{images/fmu_cycle.pdf}
+    \end{minipage}\hfill
+    \begin{minipage}{0.35\textwidth}
+        \centering
+    \includegraphics[width=1\textwidth]{images/SCC.pdf}
+    \end{minipage}
+    \caption{An FMU co-simulation scenario and its Initialization Graph}
     \label{fig:fmu_cycle}
@@
 
+The following definitions will formalize the concept of an algebraic loop in a co-simulation scenario, and define the problem these algebraic loops are introducing in the system.
+
 \begin{definition}[Algebraic loops] 
-The set of interconnected variables in an algebraic loop is defined as a strongly connected component of the graph in \cref{def:initialization_graph}. \\
+An algebraic loop is defined as a strongly connected component of the graph in \cref{def:initialization_graph}. \\
 A strongly connected component: $SCC = v \in V: Path(v,v)$\\

### 2020-06-30 initializationorder.tex
Updated images in background section

@@
 The variables with \textit{causality = parameter} of each FMU are set first, and the order of which they are set is again insignificant as they are independent.
-Afterwards the interconnected variables should be defined, but as stated by the definitions \ref{def:feedthrough}, \ref{def:getout} and \ref{def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops places even more constraints on the initialization order.
+Afterwards the interconnected variables should be defined, but as stated by the \cref{def:feedthrough,def:getout,def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops places even more constraints on the initialization order.
 This phase should should also support algebraic loops, this support includes utilization of fixed point iteration and detection of non-convergence of algebraic loops.
@@
 The edges of this graph represent precedence constraints based on the algebraic dependencies of the interconnected variables.
-Please see definition \ref{def:initialization_graph} for a formal definition of the graph.
+Please see \cref{def:initialization_graph} for a formal definition of the graph.
 
@@
 This is done by monitoring convergence of all algebraic loops.
-A valid co-simulation scenario must convergence by definition given in definition \ref{def:convergence}.
+A valid co-simulation scenario must convergence by \cref{def:convergence}.
 
 \subsubsection{Calculation of an initialization order}
-The topological ordering of the graph defined in definition \ref{def:initialization_graph} is used as the initialization order of the interconnected FMU variables.
+The topological ordering of the graph defined in \cref{def:initialization_graph} is the initialization order of the interconnected FMU variables.
 The elements of the topological order are the strongly connected components of the graphs.
@@
 The algorithm is among the most efficient graph algorithms for achieving the defined goals.
-Tarjan's algorithm is performing a topological sorting of the strongly connected components of a graph. This makes it able to handle both graphs with and without algebraic loops.
-
-\todo{Come with an example using a graph with loops}
+Tarjan's algorithm is performing a topological sorting of the strongly connected components of a graph. It is able to handle both graphs with and without algebraic loops.
 
@@
 \subsection{Optimization of a Initialization Procedure}
-An initialization procedure can be optimized by using the fact that the FMI specification allows multiple \textit{set} or \textit{get} operations of the same FMU to be performed in bulk by grouping them together to a single operation over multiple variables with similar characteristic.
-The criteria of optimization can of an initialization procedure is formalized in definition \ref{def:optimization}
+An initialization procedure can be optimized since the FMI specification allows multiple \textit{set} or \textit{get} operations of the same FMU to be performed in bulk by grouping them together to a single operation over multiple variables with similar characteristic.
+The criteria of optimization can of an initialization procedure is formalized in \cref{def:optimization}
 \begin{definition}[Optimization of a Initialization procedure]\label{def:optimization}

### 2020-06-30 background.tex
case study equations (needs to be done by hand)

--- 2020-06-30 background.tex
@@
 This means that algebraic loops needs to be handled using fixed point iterations\cite{Gomes2018}.
-It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step.
-The number of repetitions the operations should be be performed depends on the characteristics of the scenario.
-The operations should be performed until the system converge.
+It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step \claudio{Co-simulation step?
+Aren't only considering initialization here?}.
+The number of repetitions the operations should be performed depends on the characteristics of the scenario.
+The operations should be performed until the values assigned to each variable no longer change.
 An example of applying a fixed point iteration can be seen in Figure \ref{def:fixedpoint} where a system containing an algebraic loop has to be initialized using fixed point iteration.
+\claudio{Perhaps later you can ditch \cref{fig:fixedpont} and refer to the case study section, to shorten the text.}
 
@@
 In case of a non-converging algebraic loop the simulation should be stopped since the result of the co-simulation scenario wouldn't be trustworthy.
-The criteria of a valid co-simulation scenario is is specified in definition \ref{def:convergence}.
+The criteria of a valid co-simulation scenario is specified in definition \ref{def:convergence}.
 

### 2020-06-30 initializationorder.tex
case study equations (needs to be done by hand)

--- 2020-06-29 initializationorder.tex
@@
 Afterwards the interconnected variables should be defined, but as stated by the definitions \ref{def:feedthrough}, \ref{def:getout} and \ref{def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops places even more constraints on the initialization order.
-This phase should should also support algebraic loops, this support includes utilization of fixed point iteration and detection of non-convergence of algebraic loops.
+This phase should also support algebraic loops, this support includes utilization of fixed point iteration and detection of non-convergence of algebraic loops.
 
@@
 As described earlier, not all co-simulation scenarios are valid, and these invalid scenarios need to be identified.
-This is done by monitoring convergence of all algebraic loops.
-A valid co-simulation scenario must convergence by definition given in definition \ref{def:convergence}.
+This is done by monitoring convergence of the fixed point iteration when solving the algebraic loops.
+A valid co-simulation scenario must convergence by definition \ref{def:convergence}.
 

### 2020-06-30 introduction.tex

@@
 Cyber-physical systems (CPS) are becoming ever more sophisticated, while market pressure shortens the available development time.
-One of the tools used to manage the increasing complexity of such systems is co-simulation since it addresses their various parts of heterogeneous nature.
-Co-simulation is a technique to combine multiple black-box simulation units to simulate/compute the behavior of the combined models as a discrete trace (see, e.g., \cite{Kubler2000,Gomes2018}).
+One of the tools to manage the increasing complexity of such systems is co-simulation since it addresses their various parts of heterogeneous nature.
+Co-simulation is a technique to combine multiple black-box simulation units to simulate/compute the behavior of the combined models as a discrete trace (see, e.g., \cite{Kubler2000, Gomes2018}).
 The simulation units, often developed independently from each other, are coupled using a master algorithm, also often developed independently, that communicates with each simulation unit via its interface.
@@
 The FMI specification specifies criteria for how a single FMU shall be initialized.
-However, the FMI standard is not concerned with how a connected system of multiple FMUs should be correctly initialized as a whole.
+However, the FMI standard is not concerned with how a connected system of multiple FMUs is initialized correctly as a whole.
 The way a system of multiple FMUs should be initialized and interacted with depends on each FMUs implementation and interconnections to other FMUs \cite{gomes_lucio_vangheluwe_2019}, since these place precedence constraints between the FMU variables.
 The precedence constraints between the variables can introduce algebraic loops, which places particular requirements on the initialization order since the algebraic loops require a particular initialization strategy to be applied to calculate the initial values of the variables in the algebraic loop\cite{Bastian2011a}.
-An algebraic loops occur whenever there is an interconnected FMU variable that indirectly depends on itself.
-Algebraic loops introduce specific challenges in the co-simulation, and studies have shown that neglecting a loop can lead to a prohibitively high error in the co-simulation \cite{Arnold2014}.
-The order of initialization is vital for ensuring the correctness of the co-simulation \cite{Thule2018} because it ensures a variable is never read before it is set like the classical \textit{readers–writers problem} and to make sure that all initial values have converged at the start of the simulation.
+Algebraic loops occur whenever an interconnected FMU variable indirectly depends on itself.
+Algebraic loops introduce specific challenges in the co-simulation, and studies have shown that neglecting a loop can lead to a prohibitively high error in the co-simulation result \cite{Arnold2014}.
+Therefore, the order of initialization and strategy is vital for ensuring the correctness of the co-simulation \cite{Thule2018}.
+The initialization ensures a variable is never read before it is set like the classical \textit{readers–writers problem} and to make sure that all initial values have converged at the start of the simulation.
 
-\noindent Other approaches for the generation of co-simulation algorithms have avoided co-simulation scenarios containing algebraic loops since their presence reduces the chance of obtaining a valid co-simulation result\cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}.
-This choice is motivated by the fact that not all co-simulation scenarios containing algebraic loops are valid since some algebraic loops have a divergent nature.
+\noindent Other approaches for the generation of co-simulation algorithms have avoided co-simulation scenarios containing algebraic loops since their presence reduces the chance of obtaining a sound co-simulation result\cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}.
+This choice is driven by the fact that not all co-simulation scenarios containing algebraic loops are stable since some algebraic loops have a divergent nature.
 However, experience has shown that valid co-simulation scenarios containing algebraic loops exist like \todo{Claudio can you help me come up with an example?
@@
 \textit{Contribution:} This paper describes an approach for calculating the initialization order of an FMI-based co-simulation in linear time of the number of interconnected variables.
-The approach complies with the semantics of FMI and support the initialization of algebraic loops between interconnected FMU variables and identifies divergent co-simulation scenarios.
+The approach complies with the semantics of FMI and support the initialization of algebraic loops between interconnected FMU variables and identifies divergence in a co-simulation scenario.
 The approach does not put any constraints on choosing a master algorithm that should be used to carry out the simulation.
 This means that the approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobian \cite{Palensky2017}.
-The approach has been realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2).
+The approach is realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2).
 \\
 The realized plugin has been tested for various co-simulation scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial applications. 
-Furthermore, the calculated initialization order is systematically verified by co-simulation algorithm verifier introduced in \cite{gomes_lucio_vangheluwe_2019}. \\
+Furthermore, the calculated initialization order is systematically verified by the co-simulation algorithm verifier introduced in \cite{gomes_lucio_vangheluwe_2019}. \\
 
@@
 Section \ref{sc:initilization} describes the approach taken to calculate the initialization order.
-This is followed by section \ref{sc:implementation}, where the realization of the approach is presented.
+It is followed by section \ref{sc:implementation}, where the realization of the approach is presented.
 Finally, section \ref{sc:summary} provides concluding remarks and describes future work.

### 2020-06-30 background.tex
Updates from Overleaf

--- 2020-06-30 background.tex
@@
 \section{Background}\label{sc:background}
-In this section, we provide a formalization of FMI co-simulation and a short background on INTO-CPS Maestro 2.
+In this section, we provide a formalization of FMI co-simulation and a brief background on INTO-CPS Maestro 2.
 
 \subsection{FMU definitions}
-To describe the formalization of FMUs, we adopt the vocabulary from \cite{gomes_lucio_vangheluwe_2019,Gomes2018}.
+To describe the formalization of FMUs, we adopt the vocabulary from \cite{gomes_lucio_vangheluwe_2019, Gomes2018}.
 The main definitions of relevance to this paper will be presented, but readers are referred to the original publications for more information.
-This paper is only concerned with the initialization-phase of a co-simulation making time of an FMU irrelevant.
+This paper is only concerned with the initialization-phase of a co-simulation, making time of an FMU irrelevant.
 The formalization from Gomes et al.
@@
 
-The interconnections of FMU variables can lead to circular dependencies between these as seen in \cref{fig:fmu_cycle} showing a co-simulation scenario containing an algebraic loop and its Initialization Graph.
+The interconnections of FMU variables can lead to circular dependencies between them, as seen in \cref{fig:fmu_cycle} showing a co-simulation scenario containing an algebraic loop and its Initialization Graph.
 
@@
 
-The following definitions will formalize the concept of an algebraic loop in a co-simulation scenario, and define the problem these algebraic loops are introducing in the system.
+The following definitions will formalize the concept of an algebraic loop in a co-simulation scenario, and define the problem these algebraic loops are introducing.
 
@@
 
-As described by \cref{def:challenge} the algebraic loops introduce certain challenges in the system.
-This means that algebraic loops needs to be handled using fixed point iterations\cite{Gomes2018}.
+As described by \cref{def:challenge}, the algebraic loops introduce specific challenges in the system.
+This means that algebraic loops need to be handled using fixed point iterations\cite{Gomes2018}.
 It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step.
-The number of repetitions the operations should be be performed depends on the characteristics of the scenario.
+The number of repetitions the operations should be performed depends on the characteristics of the scenario.
 The operations should be performed until the system converge.
-An example of applying a fixed point iteration can be seen in \cref{def:fixedpoint} where a system containing an algebraic loop has to be initialized using fixed point iteration.
+An example of applying a fixed point iteration can be seen in \cref{def:fixedpoint}, where a system containing an algebraic loop has to be initialized using fixed point iteration.
 
@@
 
-The initialization of the system requires application of fixed point iteration as defined by \cref{def:fixedpoint}.
+The initialization of the system requires the application of fixed point iteration, as defined by \cref{def:fixedpoint}.
 \begin{definition}[Fixed point iteration of an Initialization procedure]\label{def:fixedpoint}
@@
 
-However a fixed point iteration technique is not guaranteed to convergence if the system is unstable.
+However, a fixed point iteration technique is not guaranteed to convergence if the system is unstable.
 This means that an upper bound of the number of repetitions needs to be established to ensure termination.
-In case of a non-converging algebraic loop the simulation should be stopped since the result of the co-simulation scenario wouldn't be trustworthy.
-The criteria of a valid co-simulation scenario is is specified in \cref{def:convergence}.
+In the case of a non-converging algebraic loop, the simulation should be stopped since the result of the co-simulation scenario would not be trustworthy.
+The criteria of a valid co-simulation scenario is specified in \cref{def:convergence}.
 
 \begin{definition}[Convergence of Fixed point iteration]\label{def:convergence}
-A fixed point iteration is converging if a finite number of iterations will make the difference of the output-value of the same operation between two following iterations within a certain threshold.\\
+A fixed point iteration converges if a finite number of iterations will make the difference of the output value of the same operation between two following iterations within a certain threshold.\\
 $Convergence = \exists n \in \setnat: \forall p \in \LoopVariables \implies |f(p, n + 1) - f(p, n)| \leq T$\\
@@
 The philosophy of the framework is to apply plugins to generate co-simulation specifications expressed in the domain specific language called Maestro Base Language (MaBL).
-Such specifications are then interpreted and executed resolving in the execution of a co-simulation.
+Such specifications are then interpreted and executed, resolving in the execution of a co-simulation.

### 2020-06-30 background.tex

@@
 
-As described by \cref{def:challenge}, the algebraic loops introduce specific challenges in the system.
-This means that algebraic loops need to be handled using fixed point iterations\cite{Gomes2018}.
+As described by \cref{def:challenge} the algebraic loops introduce certain challenges in the system.
+This means that algebraic loops needs to be handled using fixed point iterations\cite{Gomes2018}.
 It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step.
-The number of repetitions the operations should be performed depends on the characteristics of the scenario.
+The number of repetitions the operations should be be performed depends on the characteristics of the scenario.
 The operations should be performed until the system converge.
-An example of applying a fixed point iteration can be seen in \cref{def:fixedpoint}, where a system containing an algebraic loop has to be initialized using fixed point iteration.
+An example of applying a fixed point iteration can be seen in \cref{def:fixedpoint} where a system containing an algebraic loop has to be initialized using fixed point iteration.
+\claudio{Perhaps later you can ditch \cref{fig:fixedpont} and refer to the case study section, to shorten the text.}
 
@@
 
-However, a fixed point iteration technique is not guaranteed to convergence if the system is unstable.
+However a fixed point iteration technique is not guaranteed to convergence if the system is unstable.
 This means that an upper bound of the number of repetitions needs to be established to ensure termination.
-In the case of a non-converging algebraic loop, the simulation should be stopped since the result of the co-simulation scenario would not be trustworthy.
+In case of a non-converging algebraic loop the simulation should be stopped since the result of the co-simulation scenario would not be trustworthy.
 The criteria of a valid co-simulation scenario is specified in \cref{def:convergence}.

### 2020-06-30 conclusion.tex

--- 2020-06-29 conclusion.tex
@@
 This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU variable connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario.
-The calculated initialization order is optimized to group variables with similar characteristics to perform the fewest possible operations in the initialization procedure.
+The plugin optimizes the calculated initialization order by grouping variables with similar characteristics to perform the fewest possible operations in the initialization procedure.
 This approach supports the initialization of a co-simulation scenario containing algebraic loops by utilization of fixed point iteration.
-The approach does also discard all co-simulation scenarios which are not adhering to the law of convergence \ref{def:convergence}.
-This approach can be combined with an arbitrary master algorithm to run the co-simulation. \\
-The approach was realized as a plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\
+The approach discards all co-simulation scenarios, not adhering to the law of convergence \ref{def:convergence}.
+It is possible to combine the approach with an arbitrary master algorithm to run a co-simulation. \\
+The approach is realized as a plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\
 Future work includes formal verification of the plugin using the Logika framework\cite{inbook}.
-Future work will also look into the generation of a verification strategy for the whole Maestro 2 framework to explore how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.
+Future work will look into the generation of a verification strategy for the whole Maestro 2 framework to examine how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.
 
-\paragraph*{\textbf{Acknowlegements.}}We would like to thank Stefan Hallerstede and Peter Gorm Larsen for providing valuable input to this paper and the developed plugin.
+\paragraph*{\textbf{Acknowlegements.}}We would like to thank Stefan Hallerstede, Christian Møldrup Legaard, and Peter Gorm Larsen for providing valuable input to this paper and the developed plugin.

### 2020-06-30 initializationorder.tex
Updated related work

--- 2020-06-30 initializationorder.tex
@@
 The FMI specification defines certain information about the initialization order described through different states of a co-simulation.
-The initialization phase covers the two states (in chronological order):
+The initialization phase covers the two states (in chronological order) defined in the specification:
 \begin{itemize}
@@
 \end{itemize}
-In each of the two states, different groups of FMU variables can be assigned a value.
-The groups are defined by FMI based on rules on the characteristics of the variables (\textit{causality}, \textit{initial} and \textit{variability}).
+In each of the two states, different groups of FMU variables is potientially assigned a value.
+The groups are defined by FMI based on rules of the characteristics of the variables (\textit{causality}, \textit{initial} and \textit{variability}).
 These rules have been extracted as predicates and used in the implementation.
 An example of a group from the FMI specification is the \textit{INI}-group that consists of FMU variables with $initial = exact\, \lor initial = \,approx $  and $variability \neq constant$.
-All variables of this group should be set in the \textit{Instantiated}-phase of a co-simulation, and since they have no dependencies/connections to other FMU variables, the order is insignificant.
-However, all variables of each FMU are grouped together to perform the fewest possible operations in the initialization.
+All variables of this group are set in the \textit{Instantiated}-phase of a co-simulation.
+Since these variables have no connections to other FMU variables - meaning they are not represented in the graph of \cref{def:initialization_graph}, the order is insignificant.
+However, all variables of each FMU are grouped to perform the fewest possible operations in the initialization.
 
-In the \textit{Initialization Mode} state all variables of all FMUs should be defined.
-The variables with \textit{causality = parameter} of each FMU are set first, and the order of which they are set is again insignificant as they are independent.
+In the \textit{Initialization Mode} state, all variables of all FMUs should be defined.
+The variables with \textit{causality = parameter} of each FMU are set first, and the order they are set is again insignificant as they are independent.
 Afterwards the interconnected variables should be defined, but as stated by the \cref{def:feedthrough,def:getout,def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops places even more constraints on the initialization order.
-This phase should should also support algebraic loops, this support includes utilization of fixed point iteration and detection of non-convergence of algebraic loops.
+All these constraints must be satisfied by the initialization procedure of the interconnected variables.
 
 \subsection{Method to calculate the initialization order}
-This section describes the approach to calculate the initialization order of the interconnected FMU variables are based on the the method proposed in Gomes et al.
-\cite{Gomes2019b, BromanCompositionCo-Simulation}, but the approach used here has been extended with the ability to handle algebraic loops.
+This section describes the approach taken to calculate the initialization order of the interconnected FMU variables.
+The approach is based on the strategy proposed in Gomes et al.
+\cite{Gomes2019b, BromanCompositionCo-Simulation}, but the approach in this work is extended with the ability to handle the initialization of algebraic loops.
 
@@
 
-As described earlier, not all co-simulation scenarios are valid, and these invalid scenarios need to be identified.
-This is done by monitoring convergence of all algebraic loops.
+As described earlier, not all co-simulation scenarios are suitable, and these invalid scenarios need to be identified in this phase to avoid wasting valuable development.
+This is accomplished by monitoring convergence of all algebraic loops.
 A valid co-simulation scenario must convergence by \cref{def:convergence}.
@@
 The strongly connected components are potentially algebraic loops of the system.
-The algebraic loops are easily identified as the strongly connected components containing more than a single element.
-The single element members of the topological order are standard interconnected FMU variables, whose port operation should only be performed once during the initialization procedure.
+The loops are easily identified as the strongly connected components of more than a single element.
+The single element members of the topological order are standard interconnected FMU variables, whose port operation should only be performed only once during the initialization procedure.
 \\
 The calculation of an initialization order is performed in linear time based on the number of both external and internal connections using Tarjan's algorithm \cite{tarjan_1972}.
-This algorithm was selected since it solves two of the central issues of the initialization-phase of the co-simulation.
+This algorithm is selected due to its properties.
+It solves two of the central issues of the initialization-phase of the co-simulation.
 \begin{itemize}
@@
 The algorithm is furthermore well-established, and there exist formal proofs of its correctness and properties\cite{stefanMerz}.
-The algorithm is among the most efficient graph algorithms for achieving the defined goals.
-Tarjan's algorithm is performing a topological sorting of the strongly connected components of a graph. It is able to handle both graphs with and without algebraic loops.
+The algorithm is among the most efficient graph algorithms for accomplishing the defined goals.
+Tarjan's algorithm is performing a topological sorting of the strongly connected components of a graph. Moreover, it can handle both graphs with and without algebraic loops.
 
 \subsubsection{Handling of algebraic loops}
-As described earlier, it is essential to handle the algebraic loops by a particular initialization strategy since they otherwise would invalidate the result of the co-simulation.
+As described earlier sections, it is essential to handle the algebraic loops by a particular initialization strategy since they otherwise would invalidate the result of the co-simulation.
 The strategy for managing algebraic loops is to identify and initialize them using a fixed point iteration until convergence.
-Because convergence is not guaranteed, it should be monitored, and if convergence can not be established within a finite number of iteration, the co-simulation should be rejected.
+Since convergence is not guaranteed, this property is monitored.
+If convergence is not established within a finite number of iteration, the co-simulation is rejected to avoid running an invalid simulation.
 
@@
 An initialization procedure can be optimized since the FMI specification allows multiple \textit{set} or \textit{get} operations of the same FMU to be performed in bulk by grouping them together to a single operation over multiple variables with similar characteristic.
-The criteria of optimization can of an initialization procedure is formalized in \cref{def:optimization}
+This criteria of optimization is formalized in \cref{def:optimization}
 \begin{definition}[Optimization of a Initialization procedure]\label{def:optimization}
@@
 \end{definition}
-Since an Initialization procedure is defined in the same way as other co-simulation steps, the optimization criteria described in definition \ref{def:optimization} is valid for an arbitrary co-simulation step.
+Since an Initialization procedure is defined in the same way as other co-simulation steps (see \cref{def:initialization}), the optimization criteria described in \cref{def:optimization} is valid for an arbitrary co-simulation step.
 \\
-The correctness of this optimization can be established by the proof of using the Initialization Graph's topological ordering as the initialization order described by Gomes et al.
+The correctness of this optimization is established by the proof of using the Initialization Graph's topological ordering as the initialization order by Gomes et al.
 \cite{Gomes2019}.
-This proof is still valid since this optimization does not change the structure of the Initialization Graph.
+This proof is valid for this approach since the optimization does not change the structure of the Initialization Graph.
 \\
 A limitation of this optimization strategy is that it is not guaranteed to find all potentially valid optimizations of a co-simulation scenario.
-Considering it works only on a specific co-simulation step (a topological order of a graph), which is not necessarily unique for a given co-simulation scenario/graph.
-To perform all viable optimizations of a co-simulation step, a more advanced optimization strategy should be used, or this optimization strategy should be performed on the set of all valid co-simulation steps - yielding a potential very inefficient initialization algorithm.
+Considering it works only on a specific co-simulation step (a topological order of a graph), which is not necessarily unique for a given co-simulation scenario.
+A more advanced optimization strategy needs to be developed to perform all viable optimizations of a co-simulation step.
+Another solution is to apply this optimization strategy on the set of all valid co-simulation steps - yielding a potential very inefficient initialization algorithm.
 

### 2020-06-30 introduction.tex
Updated related work

@@
 The realized plugin has been tested for various co-simulation scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial applications. 
-Furthermore, the calculated initialization order is systematically verified by the co-simulation algorithm verifier introduced in \cite{gomes_lucio_vangheluwe_2019}. \\
+Furthermore, the calculated initialization order is systematically verified by the co-simulation Algorithm Verifier introduced in \cite{gomes_lucio_vangheluwe_2019}. \\
 

### 2020-06-30 realization.tex
Updated verification section

@@
 \subsubsection{Practical verification against a Verifier} 
-Gomes et al.'s main contribution is an implementation of the criteria for a valid FMI based co-simulation in Prolog freely available to be used in other projects\footnote{\url{http://msdl.cs.mcgill.ca/people/claudio/projs/PrologCosimGeneration.zip}}.
-The Prolog implementation was used in their research to formally verify their proposed approach for the generation of co-simulation algorithms.
-The realization encapsulates all the rules of a valid master-algorithm and an initialization algorithm.
-As a part of this work, an integration from the developed plugin has been realized to interact with the Prolog Verifier.
-This integration has been realized to verify the correctness of the calculated initialization order against an established and recognized co-simulation Algorithm Generator and Verifier.
-The integration works by querying the Prolog database with a co-simulation environment and a calculated initialization to verify the order's correctness.
-The integration requires a transformation of the dependency graph (see definition \ref{def:initialization_graph}) used in the plugin to a graph of FMU operations.
-This transformation is based on the definitions \ref{def:getout} and \ref{def:setin}.
-The described verification integration is not utilized if the graph contains algebraic loops since the Prolog database does not support these scenarios.
+Gomes et al.'s main contribution is an implementation of the criteria for a valid FMI based co-simulation formulated in Prolog freely available to be used in other projects\footnote{\url{http://msdl.cs.mcgill.ca/people/claudio/projs/PrologCosimGeneration.zip}}.
+The Prolog implementation was used in their research to verify their approach for generating co-simulation algorithms formally.
+The Prolog realization encapsulates all the rules of a valid co-simulation step (both master-algorithm and an initialization algorithm).
+This work includes an integration from the developed plugin to the Prolog Verifier.
+The integration has been realized to systematically verify the correctness of the calculated initialization order against an established and recognized co-simulation Algorithm Verifier.
+The integration queries the Prolog database with a co-simulation environment and a calculated initialization order to verify the order's correctness.
+The integration performs all the necessary transformations of the dependency graph (see definition \ref{def:initialization_graph}) used in the Maestro plugin to a graph of FMU operations used in the Prolog database.
+The transformation is based on the definitions \ref{def:getout} and \ref{def:setin}.
+The Prolog integration is not applied if the graph contains algebraic loops since the Prolog database does not support these scenarios.
 
-The Prolog code can generate an initialization order, but this functionality has not been used for several reasons.
-The main reason for not creating the initialization order using the Prolog code is based on performance considerations.
-The approach taken in this paper does also identifies the strongly connected components and performs a particular initialization strategy of these.
+The Prolog code is capable of generating a valid initialization order, but this functionality is not used for several reasons.
+The main reasons are based on performance considerations and the desire to handle the initialization of co-simulation scenarios containing strongly connected components.

### 2020-06-30 conclusion.tex

@@
 Future work includes formal verification of the plugin using the Logika framework\cite{inbook}.
-Future work will look into the generation of a verification strategy for the whole Maestro 2 framework to examine how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.
+We will also look into the generation of a verification strategy for the whole Maestro 2 framework to examine how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.
 

### 2020-06-30 relatedwork.tex

--- 2020-06-29 relatedwork.tex
@@
 \section{Related Work}
-Prior work \cite{Gomes2019, BromanCompositionCo-Simulation} has been looking into the generation of co-simulation algorithms for both master and initialization algorithms for FMI-based scenarios based on a dependency graph of the operations of a co-simulation step.
-Gomes and Broman do both present an approach where they use the topological sorting of a dependency graph to establish a correct order of operations in a co-simulation step.
+Prior work \cite{Gomes2019, BromanCompositionCo-Simulation} is looking into the generation of co-simulation algorithms (both master and initialization algorithms) for FMI-based scenarios.
+Their generation technique is like ours based on a dependency graph of the operations of a co-simulation step.
+Both Gomes and Broman present an approach for using the topological order of a dependency graph to establish a correct order of operations in a co-simulation step of a given co-simulation scenario.
+The work by Gomes et al.
+\cite{Gomes2019} does also define the criteria for a correct co-simulation step.
+Their work has many similarities with ours.
+However, their work is mostly concerned with the theoretical aspect of co-simulation algorithm generation and verification, while our work has a more practical nature.
 Gomes et al.
-\cite{Gomes2019} propose a strategy for the generation of co-simulation algorithms and define the criteria for a correct co-simulation step.
-Their work has many similarities with ours.
-However, their work does not look into the handling of algebraic loops and is not implemented as a real co-simulation framework.
+do also not consider the handling of algebraic loops, which is a key feature of our approach.
 Furthermore, the approach taken in our work is only concerned with the initialization procedure of a co-simulation.
 
-The work by Broman et al.
-\cite{BromanCompositionCo-Simulation} proposes using the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of port-operations.
-Nevertheless, they explicitly specify the requirement for cycle freedom in the dependency graph as a precondition for the generation of a deterministic co-simulation algorithm.
+Broman et al.
+\cite{BromanCompositionCo-Simulation} also suggest to use the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of port-operations.
+Nevertheless, they explicitly specify the requirement for cycle freedom in the dependency graph as a precondition for the generation of a valid co-simulation.
 It means they refuse all co-simulation scenarios containing algebraic loops.
-This is a significant difference to our approach that applies a fixed point iteration strategy to handle these scenarios.
-Also, the approach in this paper is more specialized in the sense that it is only considering the initialization of a co-simulation.
+It is a significant difference to our approach that applies a fixed point iteration strategy to handle these scenarios.
+Also, the approach in this paper is more specialized because it only considers the initialization of a co-simulation, which means it deals with non-interconnected variables.
 
@@
 Nevertheless, they achieve this by excluding scenarios containing algebraic loops.
-Their method is like ours also implemented in the real tool INTO-SysML, and it is based on using different kinds of formal methods (Theorem Proving and Model-checking) and will be an inspiration for the future work of formally verifying the plugin.
+Their method is like ours realized in a real co-simulation tool, INTO-SysML\cite{Miyazawa2016INtegratedModelling}.
+Formal methods form the basis of their work, where they have used different kinds of formal methods (Theorem Proving and Model-checking).
+It will be an inspiration for the future work of formally verifying the plugin and other parts of Maestro 2.

### 2020-06-30 casestudy.tex
case study equations (needs to be done by hand)
Updated related work
produced even more obvious formulation
Added gist of the argument for case study

@@
 
-Claudio writes this section
+In this section, we give a simple example of a co-simulation whose correct initialization demands the solution to an algebraic loop.
+
+In the example case study, the acceleration can be set to 0, at time 0.
+We show that \verb|tire_x| depends on itself as a consequence:
+\begin{verbatim}
+0 = a = (1/tire_mass) * F_total
+0 = F_total = F_rubber + F_suspension - f_gravity
+f_gravity - F_suspension = F_rubber
+F_rubber = - rubber_stiffness*tire_x - rubber_damping * tire_v
+tire_v = 0
+F_rubber = - rubber_stiffness*tire_x
+
+F_suspension = suspension_stiffness*(car_x - tire_x) + suspension_damping*(car_v - tire_v);
+
+tire_x = F(F_rubber) = G(F_suspension)= H(tire_x)
+\end{verbatim}

### 2020-07-01 background.tex
Updates from Overleaf

@@
   Given a scenario $\tuple{\fmus, \coupling}$, a co-simulation step, or just step, is a finite ordered sequence of FMU function calls $\sequence{\functioncall_i}_{i \in \setnat} = \functioncall_0, \functioncall_1, \ldots$ with
-  $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}},$
-  and $i$ denoting the order of the function call.
+  $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}} \cup \bigcup_{l \in \loops} \fixedpoint_{l},$
+  and $i$ denoting the order of the function call. Fixed point is defined in \cref{def:fixedpoint} and loops in \cref{def:loops}
 \end{definition}
@@
 
-\begin{definition}[Algebraic loops] 
+\begin{definition}[Algebraic loops]\label{def:loops}
 An algebraic loop is defined as a strongly connected component of the graph in \cref{def:initialization_graph}. \\
@@
 
+\begin{definition}[Fixed Point Iteration]\label{def:fixedpoint}
+The fixed point iteration $\fixedpoint_{Loop}$ of a given algebraic loop is the ordered sequence of all FMU functions call $\functioncall$ performed on the variables in the algebraic loop.
+$\fixedpoint_{l} = $ 
+\end{definition}
+
 \begin{definition}[Challenge of Algebraic loops]\label{def:challenge}
-The algebraic dependency will lead to the following difference between performing to following :
-\todo{Claudio check the other definitions and add a formalization of the challenge introduced}
+The algebraic dependency can lead to 
 \end{definition}
@@
 
-The initialization of the system requires the application of fixed point iteration, as defined by \cref{def:fixedpoint}.
-\begin{definition}[Fixed point iteration of an Initialization procedure]\label{def:fixedpoint}
-Given an Initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ of a co-simulation $\tuple{\fmus, \coupling}$ where $\LoopVariables \neq \emptyset$.\\
-Fixed point iteration should be used by 
-$\forall v \in \LoopVariables $
-
-\end{definition}
-
 However a fixed point iteration technique is not guaranteed to convergence if the system is unstable.

### 2020-07-01 casestudy.tex
Updates from Overleaf
case study section

--- 2020-06-30 casestudy.tex
@@
 
-Claudio writes this section
+In this section, we give a simple example of a co-simulation whose correct initialization demands the solution to an algebraic loop.
+
+We consider a co-simulation of a quarter car model \cite[Section 6.4]{Schramm2014}, illustrated in \cref{fig:quarter_car}.
+We omit the equations that each FMU is solving but note that gravity acts on both wheel and chassis masses, and that the origin of each mass is when the springs are not displaced.
+The equations and simulation model for this example are available online.
+\claudio{Simon, could you please make the QuarterCarCosimScenario.mo, QuarterCarMass.mo, and Suspension.mo, files available online?
+They're the right under the case study folder.
+Then place a link to those here.
+You might want to also add a readme file describing how to open them (using Open Modelica).}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.8\textwidth]{images/quarter_car.pdf}
+    \caption{Quarter car model co-simulation. Adapted from \cite[Section 6.4]{Schramm2014}. \claudio{Simon, please improve the figure with maybe some color coding for the different components.}}
+    \label{fig:quarter_car}
+\end{figure}
+
+The FMUs need initial conditions that are specified by equations that restrict the possible initial values for the position and velocity of the wheel and chassis masses.
+\Cref{fig:init_state_0_sim} illustrates what happens when we simply set those positions and velocities to zero.
+Note that, because of gravity, the car chassis bounces on the suspension wheel, with a maximum compression of about 17cm.
+This is most likely an invalid scenario, as the suspension of the car might not be rated to be displaced that much.
+In any case, the purpose of simulation studies involving quarter car models is to understand how well a suspension systems absords shock when the car goes over a bump, not when the car is \emph{falls on the road}, which is what the simulation results in \cref{fig:init_state_0_sim} resemble.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.8\textwidth]{images/init_state_0_sim.png}
+    \caption{Simulation results when position and velocity of the chassis mass is zero. \claudio{Simon, please improve plot (I have exported an svg and also the csv with the simulation data).}}
+    \label{fig:init_state_0_sim}
+\end{figure}
+
+The correct way to initialize this co-simulation scenario is to force the master algorithm to calculate the valid initial velocities and position from equations that force the accelerations and velocities on the masses to be zero.
+This will force the co-simulation to initialize to a steady state.
+
+To make the above explanation concrete, we now show the equations that are active at the initial time for each FMU, for a correct initialization, and we show that there is an algebraic loop.
+
+For the road FMU, the initial equation is simply the initial height of the road surface, which is this case is zero, i.e., $Z_s(0)=0$.
+For the suspension FMU, the following equations are active:
+\begin{align}
+& a_R = 0.0 & \text{Acceleration of tire} \\
+& v_R = 0.0 & \text{Velocity of tire} \\
+& F_{gR} = 9.81 * m_R  & \text{Gravity on the tire} \\
+& F_R = - c_R * z_R  & \text{Rubber force acting on tire} \\
+& F_A = c_A * (z_a - z_R) + d_A * (v_a - v_r)  & \text{Suspension force acting on tire} \\
+& F_{\mathit{total}} = F_R + F_A - F_{gR} & \text{Total forces acting on tire} \\
+& a_R = (1/m_R) * F_{\mathit{total}}  & \text{Acceleration of tire}
+\end{align}
+Finally, for the Chassis FMU, the following equations are active at the initial time:
+\begin{align}
+& a_A = 0.0 & \text{Acceleration of chassis} \\
+& v_A = 0.0 & \text{Velocity of chassis} \\
+& F_{gA} = 9.81 * m_A  & \text{Gravity on the chassis} \\
+& a_A = (1/m_A) * (- F_A - F_{gA})  & \text{Acceleration of chassis}
+\end{align}
+
+To see that there's an algebraic loop, note that the output $z_A$ of the chassis FMU is not restricted directly, but instead has to be computed from the acceleration equations $a_A = 0 = (1/m_A) * (- F_A - F_{gA})$.
+The later contain the output $F_A$ of the Suspension FMU.
+This output, in turn, depends on $z_A$, thus yielding an algebraic loop.
+\Cref{fig:init_state_correct_sim} shows the simulation results when the algebraic loops is properly solved during initialization.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=0.8\textwidth]{images/init_state_correct_sim.png}
+    \caption{Simulation results starting from a correct initial state (a steady state).
+\claudio{Simon, please improve plot (I have exported an svg and also the csv with the simulation data).
+Perhaps even merging the two plots might make sense.}}
+    \label{fig:init_state_correct_sim}
+\end{figure}

### 2020-07-01 casestudy.tex
Updates from Overleaf
Fixed inconsistencies

@@
 
-For the road FMU, the initial equation is simply the initial height of the road surface, which is this case is zero, i.e., $Z_s(0)=0$.
+For the road FMU, the initial equation is simply the initial height of the road surface, which is this case is zero, i.e., $z_s=0$.
 For the suspension FMU, the following equations are active:
@@
 & F_R = - c_R * z_R  & \text{Rubber force acting on tire} \\
-& F_A = c_A * (z_a - z_R) + d_A * (v_a - v_r)  & \text{Suspension force acting on tire} \\
+& F_A = c_A * (z_A - z_R) + d_A * (v_A - v_r)  & \text{Suspension force acting on tire} \\
 & F_{\mathit{total}} = F_R + F_A - F_{gR} & \text{Total forces acting on tire} \\

### 2020-07-01 introduction.tex
example gen bib and comments

@@
 Cyber-physical systems (CPS) are becoming ever more sophisticated, while market pressure shortens the available development time.
-One of the tools to manage the increasing complexity of such systems is co-simulation since it addresses their various parts of heterogeneous nature.
-Co-simulation is a technique to combine multiple black-box simulation units to simulate/compute the behavior of the combined models as a discrete trace (see, e.g., \cite{Kubler2000, Gomes2018}).
+One of the tools to manage the increasing complexity of such systems is co-simulation since it tackles their heterogeneous nature.
+Co-simulation is a technique to combine multiple black-box simulation units to compute the behavior of the combined models as a discrete trace (see, e.g., \cite{Kubler2000, Gomes2018}).
 The simulation units, often developed independently from each other, are coupled using a master algorithm, also often developed independently, that communicates with each simulation unit via its interface.
 This interface comprises functions for setting/getting inputs/outputs, and computing the associated model behavior over a given time interval.
-\\
 The Functional Mock-up Interface (FMI) standard \cite{Blochwitz2012, fmi_2019} is such an interface prescribing how to communicate with each simulation unit.
-The interface is used to connect different simulation units (called Functional Mock-up Units or FMUs) and exchange values between them and make them progress in time.
-\\
+The interface is used to connect different simulation units, called Functional Mock-up Units (FMUs), exchange values between them, and make them progress in time.
 
-A typical co-simulation consists of three phases: Initialization, simulation, and teardown.
+A typical co-simulation consists of three phases: Initialization, simulation, and teardown \cite{Thule2019b}.
 This work concentrates on the first of these phases - the initialization phase.
@@
 
-\noindent Other approaches for the generation of co-simulation algorithms have avoided co-simulation scenarios containing algebraic loops since their presence reduces the chance of obtaining a sound co-simulation result\cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}.
+Other approaches for the generation of co-simulation algorithms have avoided co-simulation scenarios containing algebraic loops since their presence reduces the chance of obtaining a sound co-simulation result\cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}.
 This choice is driven by the fact that not all co-simulation scenarios containing algebraic loops are stable since some algebraic loops have a divergent nature.
@@
 The approach does not put any constraints on choosing a master algorithm that should be used to carry out the simulation.
+\claudio{Maybe move the following sentence to the conclusion as it's kind of redundant with the previous sentence, and seems to a conclusion of this approach.}
 This means that the approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobian \cite{Palensky2017}. 
-The approach is realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2).
-\\
-The realized plugin has been tested for various co-simulation scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial applications. 
-Furthermore, the calculated initialization order is systematically verified by the co-simulation Algorithm Verifier introduced in \cite{gomes_lucio_vangheluwe_2019}. \\
+The approach is realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2), introduced in \cite{Thule2019b}.
+The realized plugin has been tested for various co-simulation scenarios and compared to an existing approach that has been validated through academic and industrial applications. 
+Furthermore, the calculated initialization order is systematically verified by the semantics of co-simulation introduced in \cite{gomes_lucio_vangheluwe_2019,Gomes2019c}. \\
+\claudio{Simon, can you please remove the double slashes (like the one right before this comment) from the end of sentences and paragraphs?
+It's bad practice to force Latex to make new lines.
+Also, you don't want to worry about that...
+latex usually does a good job at laying out the text for you.}
 
@@
 Finally, section \ref{sc:summary} provides concluding remarks and describes future work.
+\claudio{Simon, please make sure that the references are according to what the template suggests.
+Some templates ask references like \emph{Section~\ref{sc:summary}} and others ask for \emph{Sect.~\ref{sc:summary}}, or \emph{section~\ref{sc:summary}}, or \emph{sect.~\ref{sc:summary}}.
+The package cleveref allows you to configure how you want references to be displayed (see the package documentation) and make this uniform throughout all document.
+The same comment applies to figures, tables, definitions, etc.
+If in doubt on how to make the references, copy the style in the template text.}

### 2020-07-01 introduction.tex
intro revised

@@
 
-A typical co-simulation consists of three phases: Initialization, simulation, and teardown \cite{Thule2019b}.
-This work concentrates on the first of these phases - the initialization phase.
-The FMI specification specifies criteria for how a single FMU shall be initialized.
-However, the FMI standard is not concerned with how a connected system of multiple FMUs is initialized correctly as a whole.
+A typical co-simulation consists of three phases: initialization, simulation, and teardown \cite{Thule2019b}.
+This work concentrates on the first.
+The FMI specifies criteria for how a single FMU shall be initialized.
+However, the FMI is not concerned with how a connected system of multiple FMUs is initialized correctly as a whole.
+
 The way a system of multiple FMUs should be initialized and interacted with depends on each FMUs implementation and interconnections to other FMUs \cite{gomes_lucio_vangheluwe_2019}, since these place precedence constraints between the FMU variables.
-The precedence constraints between the variables can introduce algebraic loops, which places particular requirements on the initialization order since the algebraic loops require a particular initialization strategy to be applied to calculate the initial values of the variables in the algebraic loop\cite{Bastian2011a}.
+These constraints can introduce algebraic loops, which places particular requirements on the initialization order to calculate the initial values of the variables in the algebraic loop\cite{Bastian2011a}.
 Algebraic loops occur whenever an interconnected FMU variable indirectly depends on itself.
-Algebraic loops introduce specific challenges in the co-simulation, and studies have shown that neglecting a loop can lead to a prohibitively high error in the co-simulation result \cite{Arnold2014}.
-Therefore, the order of initialization and strategy is vital for ensuring the correctness of the co-simulation \cite{Thule2018}.
-The initialization ensures a variable is never read before it is set like the classical \textit{readers–writers problem} and to make sure that all initial values have converged at the start of the simulation.
+Not solving an algebraic loop can lead to a prohibitively high error in the co-simulation result \cite{Arnold2014}, and invalid results, as shown in \cref{sec:case_study}.
+For variables that do not belong in an algebraic loop, the initialization has to ensure that a variable is never read before it is set like the classical \textit{readers–writers problem}.
+For variable within an algebraic loop, the initialization has to make sure that all initial values have converged to a fixed point.
 
-Other approaches for the generation of co-simulation algorithms have avoided co-simulation scenarios containing algebraic loops since their presence reduces the chance of obtaining a sound co-simulation result\cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}.
-This choice is driven by the fact that not all co-simulation scenarios containing algebraic loops are stable since some algebraic loops have a divergent nature.
-However, experience has shown that valid co-simulation scenarios containing algebraic loops exist like \todo{Claudio can you help me come up with an example?
-Maybe some kind of feedback control}, and a well-established co-simulation framework should be able to handle these scenarios.
+Other approaches for the generation of co-simulation algorithms have avoided co-simulation scenarios containing algebraic loops since their presence reduces the chance of obtaining a deterministic co-simulation result\cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation, Gomes2019c}.
+This choice is driven by the fact that not all co-simulation scenarios containing algebraic loops are valid since those algebraic loops never converge, or might converge to unexpected solutions.
+However, as shown in \cref{sec:case_study}, algebraic loops can be essential to obtaining valid simulation results, and a well-established co-simulation framework should be able to handle these scenarios.
 
-\textit{Contribution:} This paper describes an approach for calculating the initialization order of an FMI-based co-simulation in linear time of the number of interconnected variables.
-The approach complies with the semantics of FMI and support the initialization of algebraic loops between interconnected FMU variables and identifies divergence in a co-simulation scenario.
+\textit{Contribution:} This paper describes an approach for calculating the initialization order of an FMI-based co-simulation in linear time of the number of interconnected variables, even when algebraic loops are present.
+% The approach complies with the semantics of FMI and support the initialization of algebraic loops between interconnected FMU variables and identifies divergence in a co-simulation scenario. 
 The approach does not put any constraints on choosing a master algorithm that should be used to carry out the simulation. 
-\claudio{Maybe move the following sentence to the conclusion as it's kind of redundant with the previous sentence, and seems to a conclusion of this approach.}
 This means that the approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobian \cite{Palensky2017}. 
+\claudio{Maybe move the above sentence to the conclusion as it's kind of redundant with the previous sentence, and seems to a conclusion of this approach.}
 The approach is realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2), introduced in \cite{Thule2019b}.

### 2020-07-01 introduction.tex
Updates from Overleaf

--- 2020-07-01 introduction.tex
@@
 The approach does not put any constraints on choosing a master algorithm that should be used to carry out the simulation.
-\claudio{Maybe move the following sentence to the conclusion as it's kind of redundant with the previous sentence, and seems to a conclusion of this approach.}
-This means that the approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobian \cite{Palensky2017}. 
 The approach is realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2), introduced in \cite{Thule2019b}.
 The realized plugin has been tested for various co-simulation scenarios and compared to an existing approach that has been validated through academic and industrial applications. 
-Furthermore, the calculated initialization order is systematically verified by the semantics of co-simulation introduced in \cite{gomes_lucio_vangheluwe_2019,Gomes2019c}. \\
+Furthermore, the calculated initialization order is systematically verified by the semantics of co-simulation introduced in \cite{gomes_lucio_vangheluwe_2019,Gomes2019c}. 
 \claudio{Simon, can you please remove the double slashes (like the one right before this comment) from the end of sentences and paragraphs?

### 2020-07-01 background.tex
case study section
Updated background section

--- 2020-06-30 background.tex
@@
 \begin{definition}[Algebraic loops] 
-An algebraic loop is defined as a strongly connected component of the graph in \cref{def:initialization_graph}. \\
+An algebraic loop is defined as a strongly connected component of the graph in \cref{def:initialization_graph}. 
 A strongly connected component: $SCC = v \in V: Path(v,v)$\\
@@
 Path is defined as the transitive closure of the edges of the graph denoted by \cref{def:initialization_graph}.\\
-\todo{Claudio check this definition and add a formalization of the challenge introduced}
 \end{definition}
 
-\begin{definition}[Challenge of Algebraic loops]\label{def:challenge}
-The algebraic dependency will lead to the following difference between performing to following :
-\todo{Claudio check the other definitions and add a formalization of the challenge introduced}
-\end{definition}
+The algebraic loops introduce certain challenges in the simulation in order to handle a on-linear system that can lead to unstable simulation behavior.
+This means that algebraic loops needs to be handled using fixed point iterations\cite{Gomes2018} to reach a valid initial state as described in \cref{sec:case_study}.
+Fixed point iteration is a technique to repeatedly perform the functions of an order sub-sequence of the co-simulation step.
+The number of repetitions the operations should be be performed depends on the scenario.
+However the repetitions of the operations is performed until the convergence of the system.
+Fixed point iteration
 
-As described by \cref{def:challenge} the algebraic loops introduce certain challenges in the system.
-This means that algebraic loops needs to be handled using fixed point iterations\cite{Gomes2018}.
-It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step.
-The number of repetitions the operations should be be performed depends on the characteristics of the scenario.
-The operations should be performed until the system converge.
-An example of applying a fixed point iteration can be seen in \cref{def:fixedpoint} where a system containing an algebraic loop has to be initialized using fixed point iteration.
-\claudio{Perhaps later you can ditch \cref{fig:fixedpont} and refer to the case study section, to shorten the text.}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{images/fixedpoint.pdf}
-    \caption{Fixed point iteration in a co-simulation scenario}
-    \label{fig:fixedpont}
-\end{figure}
-
-The initialization of the system requires the application of fixed point iteration, as defined by \cref{def:fixedpoint}.
 \begin{definition}[Fixed point iteration of an Initialization procedure]\label{def:fixedpoint}
-Given an Initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ of a co-simulation $\tuple{\fmus, \coupling}$ where $\LoopVariables \neq \emptyset$.\\
-Fixed point iteration should be used by 
-$\forall v \in \LoopVariables $
-
+A fixed point iteration of given loop $l$ consist of the order sequence of functions calls:
+$\forall v \in l: \exists op \in \fixedpoint{l} : op = \fget{}(\dontcare, v) \lor op = \fset{}(\dontcare, v, \dontcare)$.
+Performing a iteration on a co-simulation state leads to a new state to $\fixedpoint{l}(\state{n}) = \state{n + 1}$
+The fixed point iteration is performed in order to find a convergent initialization state as defined in \cref{def:convergence}.
 \end{definition}
@@
 
-\subsection{INTO-CPS Maestro 2}\todo{We can have some more in this section - potentially half a page - Ask Casper if he can do it?}
+\subsection{INTO-CPS Maestro 2}\todo{We can have some more in this section - Ask Casper if he can do it?}
 INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}}\cite{thule_maestro2_2019} is an FMI-based co-simulation framework set to supersede Maestro\cite{Maestro}.

### 2020-07-01 introduction.tex
Updated background section

--- 2020-07-01 introduction.tex
@@
 The approach does not put any constraints on choosing a master algorithm that should be used to carry out the simulation. 
-This means that the approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobian \cite{Palensky2017}. 
-\claudio{Maybe move the above sentence to the conclusion as it's kind of redundant with the previous sentence, and seems to a conclusion of this approach.}
 The approach is realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2), introduced in \cite{Thule2019b}.
 The realized plugin has been tested for various co-simulation scenarios and compared to an existing approach that has been validated through academic and industrial applications. 
-Furthermore, the calculated initialization order is systematically verified by the semantics of co-simulation introduced in \cite{gomes_lucio_vangheluwe_2019,Gomes2019c}. \\
+Furthermore, the calculated initialization order is systematically verified by the semantics of co-simulation introduced in \cite{gomes_lucio_vangheluwe_2019,Gomes2019c}. 
 \claudio{Simon, can you please remove the double slashes (like the one right before this comment) from the end of sentences and paragraphs?

### 2020-07-01 introduction.tex
Updated reference by cleverref

@@
 
-\textit{Structure:} The paper is structured as follows: Section \ref{sc:background} gives a brief background of the formalization of FMUs and Maestro 2.
-Section \ref{sc:initilization} describes the approach taken to calculate the initialization order.
-It is followed by section \ref{sc:implementation}, where the realization of the approach is presented.
-Finally, section \ref{sc:summary} provides concluding remarks and describes future work.
-\claudio{Simon, please make sure that the references are according to what the template suggests.
-Some templates ask references like \emph{Section~\ref{sc:summary}} and others ask for \emph{Sect.~\ref{sc:summary}}, or \emph{section~\ref{sc:summary}}, or \emph{sect.~\ref{sc:summary}}.
-The package cleveref allows you to configure how you want references to be displayed (see the package documentation) and make this uniform throughout all document.
-The same comment applies to figures, tables, definitions, etc.
-If in doubt on how to make the references, copy the style in the template text.}
+\textit{Structure:} The paper is structured as follows: \crref{sc:background} gives a brief background of the formalization of FMUs and Maestro 2.
+\cref{sc:initilization} describes the approach taken to calculate the initialization order.
+It is followed by \cref{sc:implementation}, where the realization of the approach is presented.
+Finally, \cref{sc:summary} provides concluding remarks and describes future work.

### 2020-07-01 background.tex
Comments on background section

--- 2020-06-30 background.tex
@@
 \subsection{FMU definitions}
-To describe the formalization of FMUs, we adopt the vocabulary from \cite{gomes_lucio_vangheluwe_2019, Gomes2018}.
+To describe the formalization of FMUs, we adopt the vocabulary from \cite{gomes_lucio_vangheluwe_2019}.
 The main definitions of relevance to this paper will be presented, but readers are referred to the original publications for more information.
@@
 \end{definition}
+\claudio{The above definition should not be called Step, because it can be confused with co-simulation step.
+Maybe call it Operations?
+Note that in the sentence before the definition, you say that these defs only refer to the initialization.}
 
@@
 \end{definition}
+
+\claudio{I'm now confused by the above definition, as it's trying to use the step definition. But the step definition is the same as the INitialization definition....}
 
@@
 
+\claudio{I think the above two definitions should come before the initialization definition, as the later uses the former (I prefer a bottom up approach.).
+You can also, at the beginning of sectioin 2.1, explain that you're going to ultimately define what the initialization procedure and algebraic loops are, but to do that, you have to define a couple of small things first.
+This allows the reader to understand why you define these small operations before getting to the bigger definitions.}
+
 \begin{definition}[Interconnected variable]
@@
 The graph is the foundation for the calculation of the initialization procedure and is therefore referred to as the Initialization Graph.
+\claudio{The graph construction is similar to the one in \cite{Gomes2019c} except that the later focuses on the co-simulation step, while we here focus on the initialization phase.}
 
@@
 The interconnections of FMU variables can lead to circular dependencies between them, as seen in \cref{fig:fmu_cycle} showing a co-simulation scenario containing an algebraic loop and its Initialization Graph.
+\claudio{Simon, can you update the above paragraph to use the co-simulation scenario presernted in the case study section?
+You can then reuse the space and the reader will already get some familiarity with the case study.
+Maybe you can even ditch the \cref{fig:fmu_cycle}.}
 
@@
 
-The following definitions will formalize the concept of an algebraic loop in a co-simulation scenario, and define the problem these algebraic loops are introducing.
+The following definitions will formalize \claudio{Simon, please avoid the future tense in the text.
+This is because the present tense is used to describe an action that is eternal...
+and the text in the paper is eternal.} the concept of an algebraic loop in a co-simulation scenario, and define the problem these algebraic loops are introducing.
+The definition of strongly connected components is adapted from the semantics of Causal Block Diagrams (see \cite{Gomes2020} for an overview).
 
 \begin{definition}[Algebraic loops] 
-An algebraic loop is defined as a strongly connected component of the graph in \cref{def:initialization_graph}. \\
-A strongly connected component: $SCC = v \in V: Path(v,v)$\\
-$\LoopVariables = \{v | v \in V : Path(v,v)\}$ \\
-An algebraic loop is defined as the set $\{p_1, p_2 | p_1, p_2 \in \LoopVariables: Path(p_1, p_2) \land Path(p_2, p_1)\}$\todo{Look at this - can it be specified better?}\\
-Path is defined as the transitive closure of the edges of the graph denoted by \cref{def:initialization_graph}.\\
-\todo{Claudio check this definition and add a formalization of the challenge introduced}
+An algebraic loop is defined as a non-trivial strongly connected component of the graph in \cref{def:initialization_graph}.
+\claudio{Using mathit tells latex that the text is a single block and avoids formatting problems.
+See \url{https://tex.stackexchange.com/questions/482743/typesetting-multi-letter-variable-names-in-math-mode}.}
+Formally, a strong connected component satisfies $\set{a,b \in SCC: \mathit{Path}(a,b)}$, where $\mathit{Path}(a,b)$ is true when there's a path (including an empty path) between nodes $a$ and $b$ ($\mathit{Path}(a,a)$ is always true).
+An $SCC$ is non trivial when it has more than one node.
+%$\LoopVariables = \{v | v \in V : Path(v,v)\}$ \\
+%An algebraic loop is defined as the set $\{p_1, p_2 | p_1, p_2 \in \LoopVariables: Path(p_1, p_2) \land Path(p_2, p_1)\}$/
+%Path is defined as the transitive closure of the edges of the graph denoted by \cref{def:initialization_graph}.
 \end{definition}
 
-\begin{definition}[Challenge of Algebraic loops]\label{def:challenge}
-The algebraic dependency will lead to the following difference between performing to following :
-\todo{Claudio check the other definitions and add a formalization of the challenge introduced}
-\end{definition}
+%\begin{definition}[Challenge of Algebraic loops]\label{def:challenge}
+%The algebraic dependency will lead to the following difference between performing to following :
+%\todo{Claudio check the other definitions and add a formalization of the challenge introduced}
+%\end{definition}
 
-As described by \cref{def:challenge} the algebraic loops introduce certain challenges in the system.
-This means that algebraic loops needs to be handled using fixed point iterations\cite{Gomes2018}.
-It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step.
-The number of repetitions the operations should be be performed depends on the characteristics of the scenario.
+Since the edges of the graph represent dependencies between variables, the value of every variable in a non trivial strong component depends on itself.
+Let $X$ denote a vector of one or more variables whose value depends on itself.
+Then the non trivial strong component forms an equation with the form $F(X, U) = X$, where $F$ denotes the relations between the variables in the loop, and $U$ denotes the variables whose values are calculated elsewhere.
+This means that algebraic loops need to be handled using fixed point iterations\cite{Gomes2018}. 
+% It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step.
+The number of repetitions the operations should be performed depends on the characteristics of the scenario.
 The operations should be performed until the system converge.
@@
 \claudio{Perhaps later you can ditch \cref{fig:fixedpont} and refer to the case study section, to shorten the text.}
+\claudio{You should avoid forcing Latex to position pictures in a particular place.
+It's bad practice because it causes too much blank space.
+Also it's a lot of work for you to care about the specific placement of figures.}
 
@@
 
-The initialization of the system requires the application of fixed point iteration, as defined by \cref{def:fixedpoint}.
+% The initialization of the system requires the application of fixed point iteration, as defined \cref{def:fixedpoint}.
 \begin{definition}[Fixed point iteration of an Initialization procedure]\label{def:fixedpoint}
@@
 
-However a fixed point iteration technique is not guaranteed to convergence if the system is unstable.
+\claudio{The above defintions is strange.
+If there's an algebraic loop, you cannot have an initialization procedure.
+At least not the way it is currently defined.
+Also I feel that you don't really need to define the fixed point iteration.
+We just need to reformulate the initialization procedure so that it matches what your plugin should output.}
+
+A fixed point iteration technique is not guaranteed to convergence if the system is unstable.
 This means that an upper bound of the number of repetitions needs to be established to ensure termination.
@@
 \begin{definition}[Convergence of Fixed point iteration]\label{def:convergence}
-A fixed point iteration converges if a finite number of iterations will make the difference of the output value of the same operation between two following iterations within a certain threshold.\\
-$Convergence = \exists n \in \setnat: \forall p \in \LoopVariables \implies |f(p, n + 1) - f(p, n)| \leq T$\\
-$f$ is the operation performed on a loop-variable p of a given iteration n.
+A fixed point iteration converges if a finite number of iterations will make the difference of the output value of the same operation between two following iterations within a certain threshold $\epsilon$.\\
+Formally, 
+$\exists n \in \setnat: |F(X^{n+1}, U) - F(X^{n}, U)| \leq \epsilon$.
 \end{definition}
@@
 \subsection{INTO-CPS Maestro 2}\todo{We can have some more in this section - potentially half a page - Ask Casper if he can do it?}
-INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}}\cite{thule_maestro2_2019} is an FMI-based co-simulation framework set to supersede Maestro\cite{Maestro}.
+INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}}\cite{Thule2019b} is an FMI-based co-simulation framework set to supersede Maestro\cite{Maestro}.
 The philosophy of the framework is to apply plugins to generate co-simulation specifications expressed in the domain specific language called Maestro Base Language (MaBL).

### 2020-07-01 background.tex

@@
 \begin{definition}[Fixed point iteration of an Initialization procedure]\label{def:fixedpoint}
-Given an Initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ of a co-simulation $\tuple{\fmus, \coupling}$ where $\LoopVariables \neq \emptyset$.\\
-Fixed point iteration should be used by 
-$\forall v \in \LoopVariables $
-
+A fixed point iteration of given loop $l$ consist of the order sequence of functions calls:
+$\forall v \in l: \exists op \in \fixedpoint{l} : op = \fget{}(\dontcare, v) \lor op = \fset{}(\dontcare, v, \dontcare)$.
+Performing a iteration on a co-simulation state leads to a new state to $\fixedpoint{l}(\state{n}) = \state{n + 1}$
+The fixed point iteration is performed in order to find a convergent initialization state as defined in \cref{def:convergence}.
 \end{definition}
@@
 
-\subsection{INTO-CPS Maestro 2}\todo{We can have some more in this section - potentially half a page - Ask Casper if he can do it?}
+\subsection{INTO-CPS Maestro 2}\todo{We can have some more in this section - Ask Casper if he can do it?}
 INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}}\cite{Thule2019b} is an FMI-based co-simulation framework set to supersede Maestro\cite{Maestro}.

### 2020-07-01 casestudy.tex
intro revised
Updates from Overleaf

@@
 \section{Case study}
-
-%This paper's main contribution is to calculate an initialization order of a co-simulation scenario potentially containing algebraic loops.
-The approach make the circular dependencies between the interconnected converge in the initialization, so the initial values of the interconnected variables in the system being simulated is stable at the time the co-simulation is started.
-
+\label{sec:case_study}
 In this section, we give a simple example of a co-simulation whose correct initialization demands the solution to an algebraic loop.
@@
 This is most likely an invalid scenario, as the suspension of the car might not be rated to be displaced that much.
-In any case, the purpose of simulation studies involving quarter car models is to understand how well a suspension systems absords shock when the car goes over a bump, not when the car is \emph{falls on the road}, which is what the simulation results in \cref{fig:init_state_0_sim} resemble.
+In any case, the purpose of simulation studies involving quarter car models is to understand how well a suspension systems absorbs shock when the car goes over a bump, not when the car is \emph{falls on the road}, which is what the simulation results in \cref{fig:init_state_0_sim} resemble.
 

### 2020-07-01 conclusion.tex
Updates from Overleaf

@@
 This approach supports the initialization of a co-simulation scenario containing algebraic loops by utilization of fixed point iteration.
-The approach discards all co-simulation scenarios, not adhering to the law of convergence \ref{def:convergence}.
-It is possible to combine the approach with an arbitrary master algorithm to run a co-simulation. \\
+The approach discards all co-simulation scenarios, not adhering to the law of convergence defined in \cref{def:convergence}.
+It is possible to combine the approach with an arbitrary master algorithm meaning the approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobian \cite{Palensky2017}.
 The approach is realized as a plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\

### 2020-07-01 realization.tex

@@
 It calculates the specification based on a list of FMU-components of a co-simulation scenario, and a specific plugin-configuration to let the user supply initial values of FMU variables with $causality=parameter$.
-A correction initialization specification can be calculated by the plugin if the co-simulation scenario is adhering to the behavior dictated by definition given in \ref{def:convergence}.
+A correction initialization specification can be calculated by the plugin if the co-simulation scenario is adhering to the behavior dictated by definition given in \cref{def:convergence}.
 
 The plugin optimizes the initialization order by grouping operations that can be executed in \textit{parallel} to take advantage of FMI's ability to \textit{set} or \textit{get} multiple variables in bulk from the same FMU.
-The criteria for this optimization is defined in definition \ref{def:optimization}.
+The criteria for this optimization is defined in \cref{def:optimization}.
 The developed plugin has been tested on numerous co-simulation examples from the INTO-CPS universe\cite{Maestro} and compared with the existing \textit{Initializer} of Maestro.
@@
 The simplification of using the interconnected variables is valid since this approach only cares about initialization and, therefore, does not need to care about the time of each FMU.
-This does that we can omit all the \textit{doStep} nodes, it means that each interconnected variable can only perform one of the two operations \textit{get} or \textit{set} as described by the definitions \ref{def:getout} and \ref{def:setin}.
+This does that we can omit all the \textit{doStep} nodes, it means that each interconnected variable can only perform one of the two operations \textit{get} or \textit{set} as described by the \cref{def:getout,def:setin}.
 This approach does, therefore, end up with a subgraph of the graph by Gomes et al.

### 2020-07-01 background.tex
Updates from Overleaf

--- 2020-07-01 background.tex
@@
   Given a scenario $\tuple{\fmus, \coupling}$, a co-simulation step, or just step, is a finite ordered sequence of FMU function calls $\sequence{\functioncall_i}_{i \in \setnat} = \functioncall_0, \functioncall_1, \ldots$ with
-  $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}},$
+  $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}} \cup (\bigcup_{l \in loops} \fixedpoint{l}),$
   and $i$ denoting the order of the function call.
+  Fixed point is defined in \cref{def:fixedpoint} and loop in \cref{def:}.
 \end{definition}
@@
 
-\begin{figure}[H]
+\begin{figure}
     \centering
@@
 
-\begin{definition}[Algebraic loops] 
-An algebraic loop is defined as a strongly connected component of the graph in \cref{def:initialization_graph}. 
-A strongly connected component: $SCC = v \in V: Path(v,v)$\\
-$\LoopVariables = \{v | v \in V : Path(v,v)\}$ \\
-An algebraic loop is defined as the set $\{p_1, p_2 | p_1, p_2 \in \LoopVariables: Path(p_1, p_2) \land Path(p_2, p_1)\}$\todo{Look at this - can it be specified better?}\\
+\begin{definition}[Algebraic loops] \label{def:loop}
+An algebraic loop is defined as a strongly connected component(SCC( of the graph in \cref{def:initialization_graph}. 
+A strongly connected component: $SCC = v \in V: Path(v,v)$ and satisfying: $\forall p_1, p_2 \in SCC: Path(p_1, p_2) \land Path(p_2, p_1),$\\
+$\loops$ denote the set of all distinct SCCs and $\abs$
 Path is defined as the transitive closure of the edges of the graph denoted by \cref{def:initialization_graph}.\\
@@
 
-The algebraic loops introduce certain challenges in the simulation in order to handle a on-linear system that can lead to unstable simulation behavior.
-This means that algebraic loops needs to be handled using fixed point iterations\cite{Gomes2018} to reach a valid initial state as described in \cref{sec:case_study}.
+The algebraic loops introduce specific challenges in the simulation to handle a non-linear system that can lead to unstable simulation behavior.
+Algebraic loops are handled using fixed point iterations\cite{Gomes2018} to reach a valid initial state as described in \cref{sec:case_study}.
 Fixed point iteration is a technique to repeatedly perform the functions of an order sub-sequence of the co-simulation step.
-The number of repetitions the operations should be be performed depends on the scenario.
-However the repetitions of the operations is performed until the convergence of the system.
-Fixed point iteration
+The number of repetitions the operations should be performed depends on the scenario.
+However, the repetitions of the operations are performed until the convergence of the system.
 
@@
 
-However a fixed point iteration technique is not guaranteed to convergence if the system is unstable.
-This means that an upper bound of the number of repetitions needs to be established to ensure termination.
-In case of a non-converging algebraic loop the simulation should be stopped since the result of the co-simulation scenario would not be trustworthy.
-The criteria of a valid co-simulation scenario is specified in \cref{def:convergence}.
+However, a fixed point iteration technique is not guaranteed to convergence if the system is unstable.
+It means that an upper bound of the number of repetitions needs to be established to ensure termination.
+In the case of a non-converging algebraic loop, the simulation should be stopped since the co-simulation result would not be trustworthy.
+The criteria of a valid co-simulation scenario are specified in \cref{def:convergence}.
 
@@
 A fixed point iteration converges if a finite number of iterations will make the difference of the output value of the same operation between two following iterations within a certain threshold.\\
-$Convergence = \exists n \in \setnat: \forall p \in \LoopVariables \implies |f(p, n + 1) - f(p, n)| \leq T$\\
+$Convergence = \exists n \in \setnat: \forall l \in \loops \implies |f(p, n + 1) - f(p, n)| \leq T$\\
 $f$ is the operation performed on a loop-variable p of a given iteration n.

### 2020-07-01 introduction.tex
Updated definitions in background section

@@
 Furthermore, the calculated initialization order is systematically verified by the semantics of co-simulation introduced in \cite{gomes_lucio_vangheluwe_2019,Gomes2019c}.
-\claudio{Simon, can you please remove the double slashes (like the one right before this comment) from the end of sentences and paragraphs?
-It's bad practice to force Latex to make new lines.
-Also, you don't want to worry about that...
-latex usually does a good job at laying out the text for you.}
 
-\textit{Structure:} The paper is structured as follows: \crref{sc:background} gives a brief background of the formalization of FMUs and Maestro 2.
+\textit{Structure:} The paper is structured as follows: \cref{sc:background} gives a brief background of the formalization of FMUs and Maestro 2.
 \cref{sc:initilization} describes the approach taken to calculate the initialization order.

### 2020-07-01 conclusion.tex
comments done

@@
 This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU variable connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario.
+\claudio{You forgot to mention algebraic loops.}
 The plugin optimizes the calculated initialization order by grouping variables with similar characteristics to perform the fewest possible operations in the initialization procedure.
-This approach supports the initialization of a co-simulation scenario containing algebraic loops by utilization of fixed point iteration.
-The approach discards all co-simulation scenarios, not adhering to the law of convergence defined in \cref{def:convergence}.
-It is possible to combine the approach with an arbitrary master algorithm meaning the approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobian \cite{Palensky2017}.
+This approach supports the initialization of a co-simulation scenario containing algebraic loops by using fixed point iteration. 
+%The approach discards all co-simulation scenarios, not adhering to the law of convergence defined in \cref{def:convergence}.
+Our approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobi \cite{Palensky2017}. 
 The approach is realized as a plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\

### 2020-07-01 relatedwork.tex
comments done

@@
 
-Amalio et al.
-\cite{Amalio2016CheckingCo-simulation} has been investigating how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS.
+Amalio et al. \cite{Amalio2016CheckingCo-simulation} has been investigating 
+\claudio{Also use present tense here, since it's the paper that we're talking about, and the paper is eternal.}
+how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS.
 The publication's purpose is like ours to avoid invalid co-simulation scenarios.
@@
 It will be an inspiration for the future work of formally verifying the plugin and other parts of Maestro 2.
+
+\claudio{Also related: \cite{EvoraGomez2019a}. Copy paste from paper content  below (please have a look and rephrase).
+A suggestion to distinguish your work from theirs: the resulting algorithm is verified against the simulation semantics (hence the more formal approach.). But this is a weak argument. 
+In practice, we will probably need to do more work to really move ahead of the state of the art.
+}
+{\scriptsize
+\begin{verbatim}
+The key idea is that a topological sorting of the directed
+acyclic graph (DAG) naturally gives the order in which the
+variables must be initialised. Therefore, this led to study
+how to convert a generic directed graph into a DAG. The
+solution found is to build the graph of strongly connected
+components (SCC) corresponding to cyclic dependencies.
+The resulting graph in which each SCC has been con-
+tracted into a single vertex is a DAG. We use Tarjan’s SCC
+algorithm (Tarjan, 1972) (used in many Modelica tools) to
+identify each SCC in the dependency graph (runs in lin-
+ear time). Following the order obtained with a topological
+sorting on the contracted SCC graph:
+1. for nodes which were not contracted, simply propa-
+gate their values
+2. for nodes which were contracted (they correspond
+to cyclic dependencies), we solve the initialisation
+problem using an iterative algorithm called JNRA
+(Jacobian based Newton-Raphson Algorithm) in-
+spired by traditional Newton-Raphson algorithms of-
+ten used for electric load flow computation.
+\end{verbatim}
+}

### 2020-07-01 background.tex
Fix underscore in ref and merge residue
Updates from Overleaf

@@
 The following definitions correspond to the operations that are permitted in the initialization phase of a co-simulation.
-
-\begin{definition}[Step]\label{def:cosim_step}
-  Given a scenario $\tuple{\fmus, \coupling}$, a co-simulation step, or just step, is a finite ordered sequence of FMU function calls $\sequence{\functioncall_i}_{i \in \setnat} = \functioncall_0, \functioncall_1, \ldots$ with
-  $\functioncall_i \in \allfunctioncalls = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}} \cup (\bigcup_{l \in loops} \fixedpoint{l}),$
-  and $i$ denoting the order of the function call.
-  Fixed point is defined in \cref{def:fixedpoint} and loop in \cref{def:}.
-\end{definition}
-\claudio{The above definition should not be called Step, because it can be confused with co-simulation step.
-Maybe call it Operations?
-Note that in the sentence before the definition, you say that these defs only refer to the initialization.}
-
-\begin{definition}[Initialization]\label{def:initialization}
-  Given a scenario $\tuple{\fmus, \coupling}$, we define the initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ in the same way as a step, with $\initcall_i \in \allfunctioncalls$.
-\end{definition}
-
-\claudio{I'm now confused by the above definition, as it's trying to use the step definition. But the step definition is the same as the INitialization definition....}
-
-\begin{definition}[Feed-through]\label{def:feedthrough}
-  The input $\inputvar{c} \in \inputs{c}$ feeds through to output $\outputvar{c} \in \outputs{c}$, that is, $(\inputvar{c},\outputvar{c}) \in \feedthrough{c}$, when there exists $v_1, v_2 \in \values$ and $\state{c} \in \stateset{c}$, such that
-  $
-  \fget{c} (\fset{c}(\state{c}, \inputvar{c}, v_1), \outputvar{c}) \neq \fget{c} (\fset{c}(\state{c}, \inputvar{c}, v_2), \outputvar{c}).
-  $
-\end{definition}
-
 \begin{definition}[Output Computation]\label{def:getout}
@@
 
+\begin{definition}[Initialization]\label{def:initialization}
+  Given a scenario $\tuple{\fmus, \coupling}$, we define the initialization procedure $\sequence{\initcall_i}_{i \in \setnat}$ as is a finite ordered sequence of FMU function calls that needs to be performed in the initialization of a co-simulation scenario.
+The ordered sequence is defined as: $\sequence{\functioncall_i}_{i \in \setnat} = \functioncall_0, \functioncall_1, \ldots$ with
+  $\functioncall_i \in \initcall_{} = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}} \cup (\bigcup_{l \in loops} \fixedpoint{l}),$
+  and $i$ denoting the order of the function call.
+  Fixed point is defined in \cref{def:fixedpoint} and loop in \cref{def:}.
+\end{definition}
+
+\begin{definition}[Feed-through]\label{def:feedthrough}
+  The input $\inputvar{c} \in \inputs{c}$ feeds through to output $\outputvar{c} \in \outputs{c}$, that is, $(\inputvar{c},\outputvar{c}) \in \feedthrough{c}$, when there exists $v_1, v_2 \in \values$ and $\state{c} \in \stateset{c}$, such that
+  $
+  \fget{c} (\fset{c}(\state{c}, \inputvar{c}, v_1), \outputvar{c}) \neq \fget{c} (\fset{c}(\state{c}, \inputvar{c}, v_2), \outputvar{c}).
+  $
+\end{definition}
+
 \claudio{I think the above two definitions should come before the initialization definition, as the later uses the former (I prefer a bottom up approach.).
-You can also, at the beginning of sectioin 2.1, explain that you're going to ultimately define what the initialization procedure and algebraic loops are, but to do that, you have to define a couple of small things first.
+You can also, at the beginning of section 2.1, explain that you're going to ultimately define what the initialization procedure and algebraic loops are, but to do that, you have to define a couple of small things first.
 This allows the reader to understand why you define these small operations before getting to the bigger definitions.}
@@
 The graph is the foundation for the calculation of the initialization procedure and is therefore referred to as the Initialization Graph.
-\claudio{The graph construction is similar to the one in \cite{Gomes2019c} except that the later focuses on the co-simulation step, while we here focus on the initialization phase.}
+The graph construction is similar to the one in \cite{Gomes2019c} except that the later focuses on the co-simulation step, while this work focus on the initialization phase.
 
@@
 
-The following definitions will formalize \claudio{Simon, please avoid the future tense in the text.
-This is because the present tense is used to describe an action that is eternal...
-and the text in the paper is eternal.} the concept of an algebraic loop in a co-simulation scenario, and define the problem these algebraic loops are introducing.
+The following definitions formalizes the concept of an algebraic loop in a co-simulation scenario, and define the problem these algebraic loops are introducing.
 The definition of strongly connected components is adapted from the semantics of Causal Block Diagrams (see \cite{Gomes2020} for an overview).
@@
 An algebraic loop is defined as a non-trivial strongly connected component of the graph in \cref{def:initialization_graph}.
-\claudio{Using mathit tells latex that the text is a single block and avoids formatting problems.
-See \url{https://tex.stackexchange.com/questions/482743/typesetting-multi-letter-variable-names-in-math-mode}.}
 Formally, a strong connected component satisfies $\set{a,b \in SCC: \mathit{Path}(a,b)}$, where $\mathit{Path}(a,b)$ is true when there's a path (including an empty path) between nodes $a$ and $b$ ($\mathit{Path}(a,a)$ is always true).
@@
 \end{definition}
-
-%\begin{definition}[Challenge of Algebraic loops]\label{def:challenge}
-%The algebraic dependency will lead to the following difference between performing to following :
-%\todo{Claudio check the other definitions and add a formalization of the challenge introduced}
-%\end{definition}
 

### 2020-07-01 initializationorder.tex
Updates from Overleaf

@@
 \end{itemize}
-In each of the two states, different groups of FMU variables is potientially assigned a value.
+In each of the two states, different groups of FMU variables are potentially assigned a value.
 The groups are defined by FMI based on rules of the characteristics of the variables (\textit{causality}, \textit{initial} and \textit{variability}).
@@
 Since these variables have no connections to other FMU variables - meaning they are not represented in the graph of \cref{def:initialization_graph}, the order is insignificant.
+\claudio{The above sentence is not entirely correct: variables with initial approx may still depend on other variables.
+The initial approx means that their values should be used as initial guesses in algebraic loop computations.
+Therefore, they may still be modified after entering initialization mode.
+To make it correct, maybe you need to ommit the condition on initial approx.}
+\claudio{Also, the reader may have no idea what does initial refer to, etc...
+That stuff is not on the background section.
+So there are two approaches to solve this: you either explain what variability and initial mean in the background, or you omit them here and rewrite the paragraph in a way that the reader does not need to understand the fmi standard.
+Perhaps the second option is the best one here, as this seems to be a minor detail.
+All you seem to want to say is: there are variables and parameters whose value does not depend on other variables.
+These can be set before entering the initialization mode and we will ignore them.}
 However, all variables of each FMU are grouped to perform the fewest possible operations in the initialization. 
+\claudio{Why is the above a "However" sentence? Is it contradicting the previous sentence?}
 
@@
 All these constraints must be satisfied by the initialization procedure of the interconnected variables.
+\claudio{I feel like the previous two sentences are a bit contradictory, and are probably constructed like so because you did not deal with algebraic loops upfront.
+When algebraic loops are not there, there must be an order.
+But when algebraic loops are there, it's not that there's more constraints...
+it's just that one has to isolate the strong components from the rest.
+The result is then an order between strongly connected components, but no order within each component}
 
@@
 
+\claudio{I like the way in which you've structured this subsection...
+but perhaps you don't need to make this structure explciit in the latex..
+just leave the subsubsection comments commented out, but still follow the structure.}
 \subsubsection{Structure of the graph}
 The initialization algorithm starts by building a directed graph of the dependency between the interconnected variables of the FMUs.
-The graph is constructed based on the interconnected variables and internal connections (feed-through).
-Each interconnected variable in the system represents a node, and the edges are based on these connections.
+The graph is constructed based on the interconnected variables and internal connections (feed-through), as in \cref{def:initialization_graph}.
+%Each interconnected variable in the system represents a node, and the edges are based on these connections.
 The edges of this graph represent precedence constraints based on the algebraic dependencies of the interconnected variables.
@@
 
-As described earlier, not all co-simulation scenarios are suitable, and these invalid scenarios need to be identified in this phase to avoid wasting valuable development.
+%As described earlier, not all co-simulation scenarios are suitable, and these invalid scenarios need to be identified in this phase to avoid wasting valuable development.
 This is accomplished by monitoring convergence of all algebraic loops.
 A valid co-simulation scenario must convergence by \cref{def:convergence}.
+%\claudio{Wait a second...
+you can only monitor convergence once you have an initialization order, and you start solving the loops.
+Why is paragraph here if the calculation of an initialization order is still to be explained?
+Maybe move this explanation to after that part.}
 
 \subsubsection{Calculation of an initialization order}
-The topological ordering of the graph defined in \cref{def:initialization_graph} is the initialization order of the interconnected FMU variables.
-The elements of the topological order are the strongly connected components of the graphs.
-The strongly connected components are potentially algebraic loops of the system.
-The loops are easily identified as the strongly connected components of more than a single element.
-The single element members of the topological order are standard interconnected FMU variables, whose port operation should only be performed only once during the initialization procedure.
-\\
+The topological ordering or the strongly connected components of the graph defined in \cref{def:initialization_graph} is the initialization order of the interconnected FMU variables. 
+The non-trivial strongly connected components are algebraic loops of the system.
+The trivial ones are standard interconnected FMU variables, whose port operation should only be performed only once during the initialization procedure.
 The calculation of an initialization order is performed in linear time based on the number of both external and internal connections using Tarjan's algorithm \cite{tarjan_1972}. 
-This algorithm is selected due to its properties.
-It solves two of the central issues of the initialization-phase of the co-simulation.
-\begin{itemize}
-    \item Identifies algebraic loops between interconnected variables (strongly connected components)
-    \item Performs a topological sorting of the Strongly Connected Components
-\end{itemize}
-The algorithm is furthermore well-established, and there exist formal proofs of its correctness and properties\cite{stefanMerz}.
-The algorithm is among the most efficient graph algorithms for accomplishing the defined goals.
-Tarjan's algorithm is performing a topological sorting of the strongly connected components of a graph. Moreover, it can handle both graphs with and without algebraic loops.
+%This algorithm is selected due to its properties. It solves two of the central issues of the initialization-phase of the co-simulation.
+%\begin{itemize}
+%    \item Identifies algebraic loops between interconnected variables (strongly connected components)
+%    \item Performs a topological sorting of the Strongly Connected Components
+%\end{itemize}
+The algorithm is well-established, and there exist formal proofs of its correctness and properties\cite{stefanMerz}. 
+% The algorithm is among the most efficient graph algorithms for accomplishing the defined goals.
+% Tarjan's algorithm is performing a topological sorting of the strongly connected components of a graph. Moreover, it can handle both graphs with and without algebraic loops.
 
@@
 The strategy for managing algebraic loops is to identify and initialize them using a fixed point iteration until convergence.
-Since convergence is not guaranteed, this property is monitored.
+Since convergence is not guaranteed, this property is monitored using \cref{def:convergence}.
 If convergence is not established within a finite number of iteration, the co-simulation is rejected to avoid running an invalid simulation.
@@
 The pseudo-code in \cref{alg:initialization} formulates the entire initialization strategy of the interconnected variables of a co-simulation scenario.
-\begin{figure}[htb]
+\begin{figure}[H]
   \centering

### 2020-07-01 background.tex
Started looking at Claudios comments

@@
   and $i$ denoting the order of the function call.
-  Fixed point is defined in \cref{def:fixedpoint} and loop in \cref{def:}.
+  Fixed point is defined in \cref{def:fixedpoint} and loop in \cref{def:loop}.
 \end{definition}
@@
 
-\claudio{I think the above two definitions should come before the initialization definition, as the later uses the former (I prefer a bottom up approach.).
+%\claudio{I think the above two definitions should come before the initialization definition, as the later uses the former (I prefer a bottom up approach.).
 You can also, at the beginning of section 2.1, explain that you're going to ultimately define what the initialization procedure and algebraic loops are, but to do that, you have to define a couple of small things first.
@@
 
-The interconnections of FMU variables can lead to circular dependencies between them, as seen in \cref{fig:fmu_cycle} showing a co-simulation scenario containing an algebraic loop and its Initialization Graph.
+The interconnections of FMU variables can lead to circular dependencies between the variables. An example of this is presented in the example in \cref{sec:case_study}.
+
+as seen in \cref{fig:fmu_cycle} showing a co-simulation scenario containing an algebraic loop and its Initialization Graph.
 \claudio{Simon, can you update the above paragraph to use the co-simulation scenario presernted in the case study section?
@@
 
-\begin{definition}[Algebraic loops] 
+\begin{definition}[Algebraic loops] \label{def:loop}
 An algebraic loop is defined as a non-trivial strongly connected component of the graph in \cref{def:initialization_graph}.
@@
 An $SCC$ is non trivial when it has more than one node.
-%$\LoopVariables = \{v | v \in V : Path(v,v)\}$ \\
-%An algebraic loop is defined as the set $\{p_1, p_2 | p_1, p_2 \in \LoopVariables: Path(p_1, p_2) \land Path(p_2, p_1)\}$/
-%Path is defined as the transitive closure of the edges of the graph denoted by \cref{def:initialization_graph}.
 \end{definition}
@@
 % The initialization of the system requires the application of fixed point iteration, as defined \cref{def:fixedpoint}.
-\begin{definition}[Fixed point iteration of an Initialization procedure]\label{def:fixedpoint}
-A fixed point iteration of given loop $l$ consist of the order sequence of functions calls:
-$\forall v \in l: \exists op \in \fixedpoint{l} : op = \fget{}(\dontcare, v) \lor op = \fset{}(\dontcare, v, \dontcare)$.
-Performing a iteration on a co-simulation state leads to a new state to $\fixedpoint{l}(\state{n}) = \state{n + 1}$
-The fixed point iteration is performed in order to find a convergent initialization state as defined in \cref{def:convergence}.
-\end{definition}
+%\begin{definition}[Fixed point iteration of an Initialization procedure]\label{def:fixedpoint}
+%A fixed point iteration of given loop $l$ consist of the order sequence of functions calls:
+%$\forall v \in l: \exists op \in \fixedpoint{l} : op = \fget{}(\dontcare, v) \lor op = \fset{}(\dontcare, v, \dontcare)$.
+%Performing a iteration on a co-simulation state leads to a new state to $\fixedpoint{l}(\state{n}) = \state{n + 1}$
+%The fixed point iteration is performed in order to find a convergent initialization state as defined in \cref{def:convergence}.
+%\end{definition}
 

### 2020-07-01 conclusion.tex
Started looking at Claudios comments

@@
 \section{Concluding remarks}\label{sc:summary}
-This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU variable connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario.
-\claudio{You forgot to mention algebraic loops.}
+This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU variable connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario potentially containing algebraic loops.
 The plugin optimizes the calculated initialization order by grouping variables with similar characteristics to perform the fewest possible operations in the initialization procedure.

### 2020-07-01 initializationorder.tex
Started looking at Claudios comments

@@
 \end{itemize}
-In each of the two states, different groups of FMU variables are potentially assigned a value.
-The groups are defined by FMI based on rules of the characteristics of the variables (\textit{causality}, \textit{initial} and \textit{variability}).
+In each of the two states, different groups of FMU variables and parameters are potentially assigned a value.
+The groups are defined by FMI based on rules of the characteristics of the variables.
 These rules have been extracted as predicates and used in the implementation.
-An example of a group from the FMI specification is the \textit{INI}-group that consists of FMU variables with $initial = exact\, \lor initial = \,approx $  and $variability \neq constant$.
-All variables of this group are set in the \textit{Instantiated}-phase of a co-simulation.
+Some groups consists of variables and parameters whose value does not depend on other variables.
+These can be set before entering the \textit{Initialization Mode}.
 Since these variables have no connections to other FMU variables - meaning they are not represented in the graph of \cref{def:initialization_graph}, the order is insignificant.
-\claudio{The above sentence is not entirely correct: variables with initial approx may still depend on other variables.
-The initial approx means that their values should be used as initial guesses in algebraic loop computations.
-Therefore, they may still be modified after entering initialization mode.
-To make it correct, maybe you need to ommit the condition on initial approx.}
-\claudio{Also, the reader may have no idea what does initial refer to, etc...
-That stuff is not on the background section.
-So there are two approaches to solve this: you either explain what variability and initial mean in the background, or you omit them here and rewrite the paragraph in a way that the reader does not need to understand the fmi standard.
-Perhaps the second option is the best one here, as this seems to be a minor detail.
-All you seem to want to say is: there are variables and parameters whose value does not depend on other variables.
-These can be set before entering the initialization mode and we will ignore them.}
-However, all variables of each FMU are grouped to perform the fewest possible operations in the initialization. 
-\claudio{Why is the above a "However" sentence? Is it contradicting the previous sentence?}
+The operations are on the variables of each FMU are grouped to perform the fewest possible operations in the initialization.
 
 In the \textit{Initialization Mode} state, all variables of all FMUs should be defined.
-The variables with \textit{causality = parameter} of each FMU are set first, and the order they are set is again insignificant as they are independent.
+The parameters of each FMU are set first, and the order they are set is again insignificant as they are independent.
 Afterwards the interconnected variables should be defined, but as stated by the \cref{def:feedthrough,def:getout,def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops places even more constraints on the initialization order.
@@
 
-\claudio{I like the way in which you've structured this subsection...
+%\claudio{I like the way in which you've structured this subsection...
 but perhaps you don't need to make this structure explciit in the latex..
 just leave the subsubsection comments commented out, but still follow the structure.}
-\subsubsection{Structure of the graph}
+%\subsubsection{Structure of the graph}
 The initialization algorithm starts by building a directed graph of the dependency between the interconnected variables of the FMUs.
@@
 
-\subsubsection{Calculation of an initialization order}
+%\subsubsection{Calculation of an initialization order}
 The topological ordering or the strongly connected components of the graph defined in \cref{def:initialization_graph} is the initialization order of the interconnected FMU variables. 
@@
 
-\subsubsection{Handling of algebraic loops}
+%\subsubsection{Handling of algebraic loops}
 As described earlier sections, it is essential to handle the algebraic loops by a particular initialization strategy since they otherwise would invalidate the result of the co-simulation.

### 2020-07-01 relatedwork.tex
Started looking at Claudios comments

@@
 
-Amalio et al. \cite{Amalio2016CheckingCo-simulation} has been investigating 
-\claudio{Also use present tense here, since it's the paper that we're talking about, and the paper is eternal.}
-how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS.
+Amalio et al.
+\cite{Amalio2016CheckingCo-simulation} investigate how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS.
 The publication's purpose is like ours to avoid invalid co-simulation scenarios.
-Nevertheless, they achieve this by excluding scenarios containing algebraic loops.
-Their method is like ours realized in a real co-simulation tool, INTO-SysML\cite{Miyazawa2016INtegratedModelling}.
-Formal methods form the basis of their work, where they have used different kinds of formal methods (Theorem Proving and Model-checking).
+Nevertheless, they achieve this by excluding co-simulation scenarios containing algebraic loops.
+Their method is realized in a co-simulation tool, INTO-SysML\cite{Miyazawa2016INtegratedModelling}.
+Formal methods form the basis of their work (Theorem Proving and Model-checking).
 It will be an inspiration for the future work of formally verifying the plugin and other parts of Maestro 2.

### 2020-07-01 casestudy.tex
Started looking at Claudios comments
Added repository of model

@@
 We consider a co-simulation of a quarter car model \cite[Section 6.4]{Schramm2014}, illustrated in \cref{fig:quarter_car}.
-We omit the equations that each FMU is solving but note that gravity acts on both wheel and chassis masses, and that the origin of each mass is when the springs are not displaced.
-The equations and simulation model for this example are available online.
-\claudio{Simon, could you please make the QuarterCarCosimScenario.mo, QuarterCarMass.mo, and Suspension.mo, files available online?
-They're the right under the case study folder.
-Then place a link to those here.
-You might want to also add a readme file describing how to open them (using Open Modelica).}
+We omit the equations that each FMU is solving but note that gravity acts on both wheel and chassis masses and that the origin of each mass is when the springs are not displaced.
+The equations and simulation model for this example are available online\footnote{\url{https://github.com/SimplisticCode/QuarterCarCaseStudy}}.
 
@@
     \includegraphics[width=0.8\textwidth]{images/quarter_car.pdf}
-    \caption{Quarter car model co-simulation. Adapted from \cite[Section 6.4]{Schramm2014}. \claudio{Simon, please improve the figure with maybe some color coding for the different components.}}
+    \caption{Quarter car model co-simulation. Adapted from \cite[Section 6.4]{Schramm2014}.}
     \label{fig:quarter_car}
@@
 
-The FMUs need initial conditions that are specified by equations that restrict the possible initial values for the position and velocity of the wheel and chassis masses.
+The FMUs need initial conditions specified by equations that restrict the possible initial values for the position and velocity of the wheel and chassis masses.
 \Cref{fig:init_state_0_sim} illustrates what happens when we simply set those positions and velocities to zero.
@@
 This is most likely an invalid scenario, as the suspension of the car might not be rated to be displaced that much.
-In any case, the purpose of simulation studies involving quarter car models is to understand how well a suspension systems absorbs shock when the car goes over a bump, not when the car is \emph{falls on the road}, which is what the simulation results in \cref{fig:init_state_0_sim} resemble.
+In any case, the purpose of simulation studies involving quarter car models is to understand how well a suspension system absorbs shock when the car goes over a bump, not when the car is \emph{falls on the road}, which is what the simulation results in \cref{fig:init_state_0_sim} resemble.
 
@@
 
-To make the above explanation concrete, we now show the equations that are active at the initial time for each FMU, for a correct initialization, and we show that there is an algebraic loop.
+To make the above explanation concrete, we now show the equations that are active at the initial time for each FMU for a correct initialization, and we show that there is an algebraic loop.
 
-For the road FMU, the initial equation is simply the initial height of the road surface, which is this case is zero, i.e., $z_s=0$.
+For the road FMU, the initial equation is simply the initial height of the road surface, which in this case is zero, i.e., $z_s=0$.
 For the suspension FMU, the following equations are active:
@@
 
-To see that there's an algebraic loop, note that the output $z_A$ of the chassis FMU is not restricted directly, but instead has to be computed from the acceleration equations $a_A = 0 = (1/m_A) * (- F_A - F_{gA})$.
-The later contain the output $F_A$ of the Suspension FMU.
+To see that there is an algebraic loop, note that the output $z_A$ of the chassis FMU is not restricted directly, but instead has to be computed from the acceleration equations $a_A = 0 = (1/m_A) * (- F_A - F_{gA})$.
+The later contains the output $F_A$ of the Suspension FMU.
 This output, in turn, depends on $z_A$, thus yielding an algebraic loop.
-\Cref{fig:init_state_correct_sim} shows the simulation results when the algebraic loops is properly solved during initialization.
+\Cref{fig:init_state_correct_sim} shows the simulation results when the algebraic loop is properly solved during initialization.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{images/init_state_correct_sim.png}
+    \includegraphics[width=0.8\textwidth]{images/init_state_correct_sim.pdf}
     \caption{Simulation results starting from a correct initial state (a steady state).

### 2020-07-01 relatedwork.tex
Added repository of model

--- 2020-06-30 relatedwork.tex
@@
 Amalio et al.
-\cite{Amalio2016CheckingCo-simulation} has been investigating how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS.
+\cite{Amalio2016CheckingCo-simulation} investigate how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS.
 The publication's purpose is like ours to avoid invalid co-simulation scenarios.
-Nevertheless, they achieve this by excluding scenarios containing algebraic loops.
-Their method is like ours realized in a real co-simulation tool, INTO-SysML\cite{Miyazawa2016INtegratedModelling}.
-Formal methods form the basis of their work, where they have used different kinds of formal methods (Theorem Proving and Model-checking).
+Nevertheless, they achieve this by excluding co-simulation scenarios containing algebraic loops.
+Their method is realized in a co-simulation tool, INTO-SysML\cite{Miyazawa2016INtegratedModelling}.
+Formal methods form the basis of their work (Theorem Proving and Model-checking).
 It will be an inspiration for the future work of formally verifying the plugin and other parts of Maestro 2.
+
+The work by \cite{EvoraGomez2019a} in of a similar nature to ours. They use Tarjan’s SCC algorithm to generate a sorted DAG of strongly connected components to solve the initialization problem.
+Even though their work is very similar to ours, we extend their approach with a verification against the simulation semantics resulting in a formal more sounds approach.
+However further work will look into further improvements of the current approach.

### 2020-07-01 background.tex
Updated background section

@@
 
-The interconnections of FMU variables can lead to circular dependencies between the variables. An example of this is presented in the example in \cref{sec:case_study}.
-
-as seen in \cref{fig:fmu_cycle} showing a co-simulation scenario containing an algebraic loop and its Initialization Graph.
-\claudio{Simon, can you update the above paragraph to use the co-simulation scenario presernted in the case study section?
-You can then reuse the space and the reader will already get some familiarity with the case study.
-Maybe you can even ditch the \cref{fig:fmu_cycle}.}
+The interconnections of FMU variables can lead to circular dependencies between the variables.
+An example of this behavior is the car suspension system that is presented in \cref{sec:case_study}.
+\cref{fig:fmu_cycle} shows the co-simulation scenario of the and the Initialization Graph of the system.
+The Initialization Graph in \cref{fig:fmu_cycle} is annotated with the strongly connected components.
 

### 2020-07-01 initializationorder.tex
Updated background section

@@
 In the \textit{Initialization Mode} state, all variables of all FMUs should be defined.
-The parameters of each FMU are set first, and the order they are set is again insignificant as they are independent.
-Afterwards the interconnected variables should be defined, but as stated by the \cref{def:feedthrough,def:getout,def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops places even more constraints on the initialization order.
-All these constraints must be satisfied by the initialization procedure of the interconnected variables.
-\claudio{I feel like the previous two sentences are a bit contradictory, and are probably constructed like so because you did not deal with algebraic loops upfront.
+The parameters of each FMU are set first, and the order in which they are set is again insignificant as they are independent.
+Afterwards the interconnected variables should be defined, but as stated by the \cref{def:feedthrough,def:getout,def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops place even more requirements on the initialization strategy.
+Since each non simple strongly connected components need to be isolated from the other parts on the system in able to apply the fixed point iteration technique.
+
+%\%claudio{I feel like the previous two sentences are a bit contradictory, and are probably constructed like so because you did not deal with algebraic loops upfront.
 When algebraic loops are not there, there must be an order.

### 2020-07-01 background.tex
Updates from Overleaf

@@
   and $i$ denoting the order of the function call.
-  Fixed point is defined in \cref{def:fixedpoint} and loop in \cref{def:loop}.
+  Fixed point is defined in \cref{def:fixedpoint} and
+  loops in defined as the set of all non trivial SCC see \cref{def:loop}.
 \end{definition}
@@
 This means that algebraic loops need to be handled using fixed point iterations\cite{Gomes2018}.
-% It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step.
-The number of repetitions the operations should be performed depends on the characteristics of the scenario.
-The operations should be performed until the system converge.
-An example of applying a fixed point iteration can be seen in \cref{def:fixedpoint} where a system containing an algebraic loop has to be initialized using fixed point iteration.
-\claudio{Perhaps later you can ditch \cref{fig:fixedpont} and refer to the case study section, to shorten the text.}
-\claudio{You should avoid forcing Latex to position pictures in a particular place.
-It's bad practice because it causes too much blank space.
-Also it's a lot of work for you to care about the specific placement of figures.}
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth]{images/fixedpoint.pdf}
-    \caption{Fixed point iteration in a co-simulation scenario}
-    \label{fig:fixedpont}
-\end{figure}
+An example of a co-simulation scenario where fixed point iteration ia needed can be seen in \cref{fig:fmu_cycle} where the Initialization Graph of the quarter car system from \cref{sec:case_study} is shown.
 
@@
 
-\claudio{The above defintions is strange.
+%\claudio{The above defintions is strange.
 If there's an algebraic loop, you cannot have an initialization procedure.

### 2020-07-01 background.tex
Updated the background section. Now I nede to read through the paper and fix the graphs.

@@
 The following definitions correspond to the operations that are permitted in the initialization phase of a co-simulation.
+
 \begin{definition}[Output Computation]\label{def:getout}
@@
 
+\begin{definition}[Fixed Point Computation]\label{def:fixedpoint}
+The $\fixedpoint{l}$ represents an order sequence of the setting or getting of all input and output variables of a given non-trivial SCC $l$.
+\end{definition}
+
 \begin{definition}[Initialization]\label{def:initialization}
@@
   and $i$ denoting the order of the function call.
-  Fixed point is defined in \cref{def:fixedpoint} and
   loops in defined as the set of all non trivial SCC see \cref{def:loop}.
@@
 The graph is the foundation for the calculation of the initialization procedure and is therefore referred to as the Initialization Graph.
-The graph construction is similar to the one in \cite{Gomes2019c} except that the later focuses on the co-simulation step, while this work focus on the initialization phase.
+The graph construction is similar to the one in \cite{Gomes2019c}, except the later focuses on a general co-simulation step, while this work focus on the initialization phase.
 
@@
 \cref{fig:fmu_cycle} shows the co-simulation scenario of the and the Initialization Graph of the system.
-The Initialization Graph in \cref{fig:fmu_cycle} is annotated with the strongly connected components.
+The Initialization Graph in \cref{fig:fmu_cycle} is annotated with the strongly connected components of the graph.
 
@@
     \centering
-    \begin{minipage}{0.55\textwidth}
-        \centering
-    \includegraphics[width=1\textwidth]{images/fmu_cycle.pdf}
-    \end{minipage}\hfill
-    \begin{minipage}{0.35\textwidth}
-        \centering
-    \includegraphics[width=1\textwidth]{images/SCC.pdf}
-    \end{minipage}
-    \caption{An FMU co-simulation scenario and its Initialization Graph}
+    \includegraphics[width=1\textwidth]{images/quarter_car_SCC.pdf}
+    \caption{An FMU co-simulation scenario of the Quarter car and its Initialization Graph denoted with SCCs}
     \label{fig:fmu_cycle}
@@
 
-The following definitions formalizes the concept of an algebraic loop in a co-simulation scenario, and define the problem these algebraic loops are introducing.
+The following definitions formalize the concept of an algebraic loop in a co-simulation scenario and define the problem these algebraic loops are introducing.
 The definition of strongly connected components is adapted from the semantics of Causal Block Diagrams (see \cite{Gomes2020} for an overview).
@@
 \begin{definition}[Algebraic loops] \label{def:loop}
-An algebraic loop is defined as a non-trivial strongly connected component of the graph in \cref{def:initialization_graph}.
+An algebraic loop is defined as a non-trivial, strongly connected component of the graph in \cref{def:initialization_graph}.
 Formally, a strong connected component satisfies $\set{a,b \in SCC: \mathit{Path}(a,b)}$, where $\mathit{Path}(a,b)$ is true when there's a path (including an empty path) between nodes $a$ and $b$ ($\mathit{Path}(a,a)$ is always true).
-An $SCC$ is non trivial when it has more than one node.
+An $SCC$ is non-trivial when it has more than one node.
 \end{definition}
 
-Since the edges of the graph represent dependencies between variables, the value of every variable in a non trivial strong component depends on itself.
+Since the edges of the graph represent dependencies between variables, the value of every variable in a non-trivial strong component depends on itself.
 Let $X$ denote a vector of one or more variables whose value depends on itself.
-Then the non trivial strong component forms an equation with the form $F(X, U) = X$, where $F$ denotes the relations between the variables in the loop, and $U$ denotes the variables whose values are calculated elsewhere.
+The non-trivial strong component forms an equation with the form $F(X, U) = X$, where $F$ denotes the relations between the variables in the loop and $U$ denotes the variables whose values are calculated elsewhere.
 This means that algebraic loops need to be handled using fixed point iterations\cite{Gomes2018}.
 
-An example of a co-simulation scenario where fixed point iteration ia needed can be seen in \cref{fig:fmu_cycle} where the Initialization Graph of the quarter car system from \cref{sec:case_study} is shown.
+An example of a co-simulation scenario where fixed point iteration is needed can be seen in \cref{fig:fmu_cycle} where the Initialization Graph of the quarter car system from \cref{sec:case_study} is shown.
 
@@
 This means that an upper bound of the number of repetitions needs to be established to ensure termination.
-In case of a non-converging algebraic loop the simulation should be stopped since the result of the co-simulation scenario would not be trustworthy.
-The criteria of a valid co-simulation scenario is specified in \cref{def:convergence}.
+In the case of a non-converging algebraic loop, the simulation should be stopped since the result of the co-simulation scenario would not be trustworthy.
+The criteria of a valid co-simulation scenario are specified in \cref{def:convergence}.
 

### 2020-07-01 initializationorder.tex
Updated the background section. Now I nede to read through the paper and fix the graphs.

@@
 These rules have been extracted as predicates and used in the implementation.
-Some groups consists of variables and parameters whose value does not depend on other variables.
+Some groups consist of variables and parameters whose value does not depend on other variables.
 These can be set before entering the \textit{Initialization Mode}.
@@
 Afterwards the interconnected variables should be defined, but as stated by the \cref{def:feedthrough,def:getout,def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops place even more requirements on the initialization strategy.
-Since each non simple strongly connected components need to be isolated from the other parts on the system in able to apply the fixed point iteration technique.
+Since each non-trivial strongly connected component needs to be isolated from the other variables of the system to obtain their initial values using fixed point iteration.
 

### 2020-07-02 background.tex
Updated graph

@@
 \begin{definition}[Fixed Point Computation]\label{def:fixedpoint}
-The $\fixedpoint{l}$ represents an order sequence of the setting or getting of all input and output variables of a given non-trivial SCC $l$.
+The $\fixedpoint{l}$ represents an order sequence of the setting or getting of all input and output variables of a given SCC $l$.
 \end{definition}
@@
 The ordered sequence is defined as: $\sequence{\functioncall_i}_{i \in \setnat} = \functioncall_0, \functioncall_1, \ldots$ with
-  $\functioncall_i \in \initcall_{} = \bigcup_{c \in \fmus} \set{\fset{c},\fget{c}} \cup (\bigcup_{l \in loops} \fixedpoint{l}),$
+  $\functioncall_i \in \initcall_{} = \bigcup_{l \in loops} \fixedpoint{l},$
   and $i$ denoting the order of the function call.
-  loops in defined as the set of all non trivial SCC see \cref{def:loop}.
+  loops in defined as the set of all SCC see \cref{def:loop}.
 \end{definition}

### 2020-07-02 casestudy.tex
Updated graph

@@
 \centering
-    \includegraphics[width=0.8\textwidth]{images/init_state_0_sim.png}
-    \caption{Simulation results when position and velocity of the chassis mass is zero. \claudio{Simon, please improve plot (I have exported an svg and also the csv with the simulation data).}}
+\begin{tikzpicture}
+    \begin{axis}[
+        %at={(0,0)},
+        width= 12cm,
+        height = 8cm,
+        ymin=-0.2,
+        ymax=0.05,
+        xmin=0,
+        xmax=4.1,
+        grid=both,
+        grid style={line width=.1pt, draw=gray!10},
+        major grid style={line width=.2pt,draw=gray!50},
+        axis lines=middle,
+        minor tick num =5,
+        axis line style={latex-latex},
+        ticklabel style={font=\tiny,fill=white},
+        minor tick style={draw=none},
+        minor grid style={thin,color=black!10},
+        ylabel= Car position,
+        xlabel= Time (s),
+        tick align=outside,
+        x label style={at={(axis description cs:0.5,-0.1)},anchor=north},
+        y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=south},
+        xlabel style={color=blue!50!cyan},
+        ylabel style={align=center,rotate=-90,color=blue!50!cyan},
+        x tick label style={
+            /pgf/number format/assume math mode, font=\sf\scriptsize}
+        ]
+    \addplot table [x=a, y=b, col sep=comma] {incorrect.csv};
+\end{axis}
+\end{tikzpicture}
+    \caption{Simulation results when position and velocity of the chassis mass is zero.}
     \label{fig:init_state_0_sim}
@@
 \centering
-    \includegraphics[width=0.8\textwidth]{images/init_state_correct_sim.pdf}
-    \caption{Simulation results starting from a correct initial state (a steady state).
-\claudio{Simon, please improve plot (I have exported an svg and also the csv with the simulation data).
-Perhaps even merging the two plots might make sense.}}
+\begin{tikzpicture}
+    \begin{axis}[
+        %at={(0,0)},
+        width= 12cm,
+        height = 8cm,
+        ymin=-0.18,
+        ymax=-0.05,
+        xmin=0,
+        xmax=4.1,
+        grid=both,
+        grid style={line width=.1pt, draw=gray!10},
+        major grid style={line width=.2pt,draw=gray!50},
+        axis lines=middle,
+        minor tick num =5,
+        axis line style={latex-latex},
+        ticklabel style={font=\tiny,fill=white},
+        minor tick style={draw=none},
+        minor grid style={thin,color=black!10},
+        x label style={at={(axis description cs:0.5,-0.1)},anchor=north},
+        y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=south},
+        ylabel= Car position,
+        xlabel= Time (s),
+        tick align=outside,
+        xlabel style={color=blue!50!cyan},
+        ylabel style={align=center,rotate=-90,color=blue!50!cyan},
+        x tick label style={
+            /pgf/number format/assume math mode, font=\sf\scriptsize}
+            ]
+    \addplot table [x=a, y=b, col sep=comma] {correct.csv};
+\end{axis}
+\end{tikzpicture}
+    \caption{Simulation results starting from a correct initial state (a steady state).}
     \label{fig:init_state_correct_sim}

### 2020-07-02 initializationorder.tex
Updated graph

@@
 \end{definition}
-Since an Initialization procedure is defined in the same way as other co-simulation steps (see \cref{def:initialization}), the optimization criteria described in \cref{def:optimization} is valid for an arbitrary co-simulation step.
+%Since an Initialization procedure is defined in the same way as other co-simulation steps (see \cref{def:initialization}), the optimization criteria described in \cref{def:optimization} is valid for an arbitrary co-simulation step.
 \\
-The correctness of this optimization is established by the proof of using the Initialization Graph's topological ordering as the initialization order by Gomes et al.
+The correctness of the optimization in \cref{def:optimization} is established by the proof of using the Initialization Graph's topological ordering as the initialization order by Gomes et al.
 \cite{Gomes2019}.

### 2020-07-02 casestudy.tex
Updated line plots in co-simulation section

@@
     \begin{axis}[
-        %at={(0,0)},
+        at={(0,0)},
         width= 12cm,
@@
         ]
-    \addplot table [x=a, y=b, col sep=comma] {incorrect.csv};
+    \addplot [line width=2.5pt, red] table [x=a, y=b, col sep=comma] {incorrect.csv};
 \end{axis}
@@
             ]
-    \addplot table [x=a, y=b, col sep=comma] {correct.csv};
+    \addplot [line width=2.5pt, red] table [x=a, y=b, col sep=comma] {correct.csv};
 \end{axis}

### 2020-07-02 background.tex
Updates based on comments from Stefan

@@
 \begin{definition}[Fixed Point Computation]\label{def:fixedpoint}
-The $\fixedpoint{l}$ represents an order sequence of the setting or getting of all input and output variables of a given SCC $l$.
+The $\fixedpoint{l}$ represents an order sequence of the setting or getting of all input and output variables of a given SCC $l$, see \cref{def:loop} for a definition of SCC.
 \end{definition}
@@
 
-\begin{definition}[Interconnected variable]
-An interconnected variable v of a co-simulation scenario $\tuple{\fmus, \coupling}$ is defined as $v \in \allinputs \cup \alloutputs$, then $\coupling : \allinputs \to \alloutputs$.
-The set all all interconnected variables is denoted: $V = \allinputs \cup \alloutputs$,
-\end{definition}
+%\begin{definition}[Interconnected variable]
+%An interconnected variable v of a co-simulation scenario $\tuple{\fmus, \coupling}$ is defined as $v \in \allinputs \cup \alloutputs$, then $\coupling : \allinputs \to \alloutputs$.
+%The set all all interconnected variables is denoted: $V = \allinputs \cup \alloutputs$,
+%\end{definition}
 
@@
   \begin{compactenum}
-    \item For each $c \in \fmus$ and $\inputvar{c} \in \inputs{c}$, if $\coupling(\inputvar{c}) = \outputvar{d}$, add an edge $\outputvar{d} -> \inputvar{c}$.
-    \item For each $c \in \fmus$ and $(\inputvar{c},\outputvar{c}) \in \feedthrough{c}$, add an edge $\inputvar{c} -> \outputvar{c}$.
+    \item For each $c \in \fmus$ and $\inputvar{c} \in \inputs{c}$, if $\coupling(\inputvar{c}) = \outputvar{d}$, add an edge $\outputvar{d} -> \inputvar{c}$ (output to input).
+    \item For each $c \in \fmus$ and $(\inputvar{c},\outputvar{c}) \in \feedthrough{c}$, add an edge $\inputvar{c} -> \outputvar{c}$ (input to output).
   \end{compactenum}
@@
 An example of this behavior is the car suspension system that is presented in \cref{sec:case_study}.
-\cref{fig:fmu_cycle} shows the co-simulation scenario of the and the Initialization Graph of the system.
+\cref{fig:fmu_cycle} shows the co-simulation scenario of the example and the Initialization Graph of the system.
 The Initialization Graph in \cref{fig:fmu_cycle} is annotated with the strongly connected components of the graph.
@@
 A fixed point iteration technique is not guaranteed to convergence if the system is unstable.
-This means that an upper bound of the number of repetitions needs to be established to ensure termination.
+The fixed point is as a numerical fixed point that approximates a limit if such a value exist (the system is stable).
+It means that an upper bound of the number of repetitions needs to be established to ensure termination.
 In the case of a non-converging algebraic loop, the simulation should be stopped since the result of the co-simulation scenario would not be trustworthy.
@@
 
-\subsection{INTO-CPS Maestro 2}\todo{We can have some more in this section - Ask Casper if he can do it?}
-INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}}\cite{Thule2019b} is an FMI-based co-simulation framework set to supersede Maestro\cite{Maestro}.
-The philosophy of the framework is to apply plugins to generate co-simulation specifications expressed in the domain specific language called Maestro Base Language (MaBL).
-Such specifications are then interpreted and executed, resolving in the execution of a co-simulation.
+\subsection{INTO-CPS Maestro 2}
+INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}}~\cite{Thule2019b} is a framework for creating simulation specifications and executing such specifications.
+The framework is FMI-based and set to supersede Maestro~\cite{Maestro} with the main goal of supporting research into co-simulation based on FMI.
+
+The philosophy of the framework is to separate the specification of a co-simulation and the execution of a co-simulation.
+This allows one to inspect and verify, manually or automatically, how a given co-simulation is to be executed.
+
+A specification is expressed in the domain-specific language called Maestro Base Language (MaBL), and it is explicit, such that the application of i.e., FMUs are transparent.
+In order to assist in the creation of such MaBL specifications, one can apply expansion plugins that, in turn, generate MaBL code.
+The plugin described in this paper is such an expansion plugin.
+The application of a plugin is evident in a MaBL specification.
+Upon processing of the specification, a new specification is created where the application of a plugin is replaced with the MaBL code generated by the given plugin.
+This process is referred to as expansion, and a specification without any expansions remaining is referred to as a fully expanded MaBL specification.
+
+To conduct a co-simulation, Maestro2 also features an interpreter that can execute a fully expanded MaBL specification, resulting in the execution of the given co-simulation.

### 2020-07-03 background.tex
Updated plots

@@
 
-\begin{definition}[Fixed Point Computation]\label{def:fixedpoint}
+\begin{definition}[Fixed Point]\label{def:fixedpoint}
 The $\fixedpoint{l}$ represents an order sequence of the setting or getting of all input and output variables of a given SCC $l$, see \cref{def:loop} for a definition of SCC.
+The $\fixedpoint{l} \subseteq \bigcup_{c \in \fmus} \set{\fget{c},\fset{c}}$ 
 \end{definition}
@@
 \end{definition}
+
+It should be noted that a trivial SCC (\see \cref{def:loop}) is only a single get or set action and is not regarded as a fixed point outside \cref{def:initialization}, but just a simple computation.
 

### 2020-07-03 casestudy.tex
Updated plots

--- 2020-07-01 casestudy.tex
@@
 \centering
-    \includegraphics[width=0.8\textwidth]{images/init_state_0_sim.png}
-    \caption{Simulation results when position and velocity of the chassis mass is zero. \claudio{Simon, please improve plot (I have exported an svg and also the csv with the simulation data).}}
+\begin{tikzpicture}
+    \begin{axis}[
+        at={(0,0)},
+        width= 12cm,
+        height = 8cm,
+        ymin=-0.2,
+        ymax=0.05,
+        xmin=0,
+        xmax=4.1,
+        grid=both,
+        grid style={line width=.1pt, draw=gray!10},
+        major grid style={line width=.2pt,draw=gray!50},
+        axis lines=middle,
+        minor tick num =5,
+        axis line style={latex-latex},
+        ticklabel style={font=\tiny,fill=white},
+        minor tick style={draw=none},
+        minor grid style={thin,color=black!10},
+        ylabel= Car chassis position (m),
+        xlabel= Time (s),
+        tick align=outside,
+        x label style={at={(axis description cs:0.5,-0.1)},anchor=north, color=blue!50!cyan},
+        y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=south, color=blue!50!cyan},
+        x tick label style={
+            /pgf/number format/assume math mode, font=\sf\scriptsize}
+        ]
+    \addplot [line width=2.5pt, red] table [x= a, y=b, col sep=comma] {incorrect.csv};
+\end{axis}
+\end{tikzpicture}
+    \caption{Simulation results when position and velocity of the chassis mass is zero.}
     \label{fig:init_state_0_sim}
@@
 \centering
-    \includegraphics[width=0.8\textwidth]{images/init_state_correct_sim.pdf}
-    \caption{Simulation results starting from a correct initial state (a steady state).
-\claudio{Simon, please improve plot (I have exported an svg and also the csv with the simulation data).
-Perhaps even merging the two plots might make sense.}}
+\begin{tikzpicture}
+    \begin{axis}[
+        %at={(0,0)},
+        width= 12cm,
+        height = 8cm,
+        ymin=-0.18,
+        ymax=-0.05,
+        xmin=0,
+        xmax=4.1,
+        grid=both,
+        grid style={line width=.1pt, draw=gray!10},
+        major grid style={line width=.2pt,draw=gray!50},
+        axis lines=middle,
+        minor tick num =5,
+        axis line style={latex-latex},
+        ticklabel style={font=\tiny,fill=white},
+        minor tick style={draw=none},
+        minor grid style={thin,color=black!10},
+        ylabel= Car chassis position (m),
+        xlabel= Time (s),
+        tick align=outside,
+        x label style={at={(axis description cs:0.5,-0.1)},anchor=north, color=blue!50!cyan},
+        y label style={at={(axis description cs:-0.1,.5)},rotate=90,anchor=south, color=blue!50!cyan},
+        x tick label style={
+            /pgf/number format/assume math mode, font=\sf\scriptsize}
+            ]
+    \addplot [line width=2.5pt, red] table [x=a, y=b, col sep=comma] {correct.csv};
+\end{axis}
+\end{tikzpicture}
+    \caption{Simulation results starting from a correct initial state (a steady state).}
     \label{fig:init_state_correct_sim}

### 2020-07-03 initializationorder.tex
Updated plots

@@
 Since these variables have no connections to other FMU variables - meaning they are not represented in the graph of \cref{def:initialization_graph}, the order is insignificant.
-The operations are on the variables of each FMU are grouped to perform the fewest possible operations in the initialization.
+The setting and getting operations are of each FMU are grouped to perform the fewest possible operations in the initialization.
 
@@
 %\subsubsection{Calculation of an initialization order}
-The topological ordering or the strongly connected components of the graph defined in \cref{def:initialization_graph} is the initialization order of the interconnected FMU variables. 
+The topological ordering of the strongly connected components of the graph defined in \cref{def:initialization_graph} is the initialization order of the interconnected FMU variables. 
 The non-trivial strongly connected components are algebraic loops of the system.
-The trivial ones are standard interconnected FMU variables, whose port operation should only be performed only once during the initialization procedure.
+The trivial ones are standard interconnected FMU variables, whose port operation should be performed only once during the initialization procedure.
 The calculation of an initialization order is performed in linear time based on the number of both external and internal connections using Tarjan's algorithm \cite{tarjan_1972}. 
@@
 %\subsubsection{Handling of algebraic loops}
-As described earlier sections, it is essential to handle the algebraic loops by a particular initialization strategy since they otherwise would invalidate the result of the co-simulation.
+As described in earlier sections, it is essential to handle the algebraic loops by a particular initialization strategy since they otherwise would invalidate the result of the co-simulation.
 The strategy for managing algebraic loops is to identify and initialize them using a fixed point iteration until convergence.

### 2020-07-03 realization.tex
Started looking at Claudios comments
Updated plots

@@
 It calculates the specification based on a list of FMU-components of a co-simulation scenario, and a specific plugin-configuration to let the user supply initial values of FMU variables with $causality=parameter$.
-A correction initialization specification can be calculated by the plugin if the co-simulation scenario is adhering to the behavior dictated by definition given in \cref{def:convergence}.
+A correction initialization specification can be calculated by the plugin if the co-simulation scenario is adhering to the behavior dictated by the definition given in \cref{def:convergence}.
 
@@
 The Prolog integration is not applied if the graph contains algebraic loops since the Prolog database does not support these scenarios.
-
-The Prolog code is capable of generating a valid initialization order, but this functionality is not used for several reasons.
-The main reasons are based on performance considerations and the desire to handle the initialization of co-simulation scenarios containing strongly connected components.

### 2020-07-03 relatedwork.tex
Updated background section
Updated plots

@@
 
-The work by \cite{EvoraGomez2019a} in of a similar nature to ours. They use Tarjan’s SCC algorithm to generate a sorted DAG of strongly connected components to solve the initialization problem.
-Even though their work is very similar to ours, we extend their approach with a verification against the simulation semantics resulting in a formal more sounds approach.
-However further work will look into further improvements of the current approach.
+The work by Gomez et al. .\cite{EvoraGomez2019a} is similar to ours. They use Tarjan's SCC algorithm to generate a sorted DAG of strongly connected components to solve the initialization problem.
+Even though their work is very similar to ours, we extend their approach with verification against the simulation semantics resulting in a formally more sound approach.
+However, further work will look into further improvements and formal verification of the current approach.

### 2020-08-24 abstract.tex
Updated plots
Changes based on comments from external reviewers

@@
 \begin{abstract}
-The accuracy of the result in a co-simulation is dependent on the correct initialization of all the simulation units.
+The accuracy of the result of a co-simulation is dependent on the correct initialization of all the simulation units.
 In this work, we consider co-simulation where the simulation units are described as Functional Mock-up Units (FMU).
-The Functional Mock-up Interface specification specifies constraints to the initialization of variables in the scope of a single FMU.
+The Functional Mock-up Interface (FMI) specification specifies constraints to the initialization of variables in the scope of a single FMU.
 However, it does not consider the initialization of interconnected variables between instances of FMUs.
@@
 The approach taken to calculate a correct initialization order is based on predicates from the FMI specification and the topological ordering of both internal connections and interconnected variables.
-The approach supports the initialization of algebraic loops using fixed point iteration.
+The approach supports the initialization of co-simulation scenarios containing algebraic loops using fixed point iteration.
 %  dependencies between FMU variables are dismissed.

### 2020-08-24 background.tex
Changes based on comments from external reviewers

@@
   \begin{inparadesc}
-    \item $\stateset{c}$ represents the state space;
+    \item $\stateset{c}$ represents the state space of FMU c;
     \item $\inputs{c}$ and $\outputs{c}$ the set of input and output variables, respectively;
@@
 \end{definition}
-
+Note it is possible for a single output to connect to a multiple inputs, but a single input can only rely on a single output.
+%In Defn. 2, it seems that L is a function U --> Y, does that mean that each input variable feeds-through only one output variable?
 The following definitions correspond to the operations that are permitted in the initialization phase of a co-simulation.
@@
 \end{definition}
+%A faulty check will incur TODO
 
@@
 
-The philosophy of the framework is to separate the specification of a co-simulation and the execution of a co-simulation.
+The philosophy of the framework is to separate the specification of a co-simulation from the execution.
 This allows one to inspect and verify, manually or automatically, how a given co-simulation is to be executed.
 
-A specification is expressed in the domain-specific language called Maestro Base Language (MaBL), and it is explicit, such that the application of i.e., FMUs are transparent.
-In order to assist in the creation of such MaBL specifications, one can apply expansion plugins that, in turn, generate MaBL code.
+A specification is expressed in the domain-specific language called Maestro Base Language (MaBL), and it is explicit, such that the application of, i.e., FMUs are transparent.
+Expansion plugins can assist in creating such MaBL specifications, and one can apply expansion plugins that, in turn, generate the MaBL code.
 The plugin described in this paper is such an expansion plugin.
 The application of a plugin is evident in a MaBL specification.
-Upon processing of the specification, a new specification is created where the application of a plugin is replaced with the MaBL code generated by the given plugin.
-This process is referred to as expansion, and a specification without any expansions remaining is referred to as a fully expanded MaBL specification.
+Upon processing of the specification, a new specification is created where the application of a plugin is replaced by the MaBL code generated by the plugin.
+This process is known as expansion, and a specification without any expansions remaining is a fully expanded MaBL specification.
 
-To conduct a co-simulation, Maestro2 also features an interpreter that can execute a fully expanded MaBL specification, resulting in the execution of the given co-simulation.
+To conduct a co-simulation, Maestro2 also features an interpreter that can execute a fully expanded MaBL specification, resulting in the execution of the co-simulation.

### 2020-08-24 casestudy.tex
Changes based on comments from external reviewers

@@
         height = 8cm,
-        ymin=-0.2,
-        ymax=0.05,
+        ymin=-20,
+        ymax=5,
         xmin=0,
@@
         minor grid style={thin,color=black!10},
-        ylabel= Car chassis position (m),
+        ylabel= Car chassis position (cm),
         xlabel= Time (s),
@@
         ]
-    \addplot [line width=2.5pt, red] table [x= a, y=b, col sep=comma] {incorrect.csv};
+    \addplot [line width=2.5pt, red] table [x= a, y=c, col sep=comma] {incorrect.csv};
 \end{axis}
@@
 
-\begin{figure}[htb]
+\begin{figure}[H]
 \centering
@@
         height = 8cm,
-        ymin=-0.18,
-        ymax=-0.05,
+        ymin=-18,
+        ymax=-5,
         xmin=0,
@@
             ]
-    \addplot [line width=2.5pt, red] table [x=a, y=b, col sep=comma] {correct.csv};
+    \addplot [y filter/.code={\pgfmathparse{\pgfmathresult*100.}\pgfmathresult}][line width=2.5pt, red] table [x=a, y=b, col sep=comma] {correct.csv};
 \end{axis}

### 2020-08-24 conclusion.tex
Changes based on comments from external reviewers

@@
 \section{Concluding remarks}\label{sc:summary}
-This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU variable connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario potentially containing algebraic loops.
-The plugin optimizes the calculated initialization order by grouping variables with similar characteristics to perform the fewest possible operations in the initialization procedure.
+This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario potentially containing algebraic loops.
+The initialization procedure optimizes the initialization order by grouping variables with similar characteristics to perform the fewest possible operations in the initialization procedure.
 This approach supports the initialization of a co-simulation scenario containing algebraic loops by using fixed point iteration. 
 %The approach discards all co-simulation scenarios, not adhering to the law of convergence defined in \cref{def:convergence}.
-Our approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobi \cite{Palensky2017}. 
-The approach is realized as a plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\
+The approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobi \cite{Palensky2017}. 
+The approach is realized as an expansion plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\
 Future work includes formal verification of the plugin using the Logika framework\cite{inbook}.

### 2020-08-24 initializationorder.tex
Changes based on comments from external reviewers

@@
 The FMI specification defines certain information about the initialization order described through different states of a co-simulation.
-The initialization phase covers the two states (in chronological order) defined in the specification:
+The initialization phase covers the two states (in chronological order) defined in the FMI specification:
 \begin{itemize}
@@
 In each of the two states, different groups of FMU variables and parameters are potentially assigned a value.
-The groups are defined by FMI based on rules of the characteristics of the variables.
-These rules have been extracted as predicates and used in the implementation.
+The groups are defined by FMI based on the characteristics of the FMU variables.
+The rules have been extracted as predicates and used in the implementation.
 Some groups consist of variables and parameters whose value does not depend on other variables.
-These can be set before entering the \textit{Initialization Mode}.
-Since these variables have no connections to other FMU variables - meaning they are not represented in the graph of \cref{def:initialization_graph}, the order is insignificant.
-The setting and getting operations are of each FMU are grouped to perform the fewest possible operations in the initialization.
+These independent variables and parameters can be set in the \textit{Instantiated} phase of the Initialization.
+Since these variables have no connections to other FMU variables - meaning they are not represented in the graph of \cref{def:initialization_graph}, the order their value is set in is insignificant.
+The setting and getting operations of each FMU are grouped to perform the fewest possible FMU-operations during the Initialization.
 
-In the \textit{Initialization Mode} state, all variables of all FMUs should be defined.
-The parameters of each FMU are set first, and the order in which they are set is again insignificant as they are independent.
-Afterwards the interconnected variables should be defined, but as stated by the \cref{def:feedthrough,def:getout,def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops place even more requirements on the initialization strategy.
-Since each non-trivial strongly connected component needs to be isolated from the other variables of the system to obtain their initial values using fixed point iteration.
+In the \textit{Initialization Mode} state all the interconnected variable is being defined, but as stated by the \cref{def:feedthrough,def:getout,def:setin} the operations \textit{get} and \textit{set} \textbf{require} that the operations are performed in a specific order.
+Furthermore, algebraic loops place even more requirements on the initialization strategy.
+Since each non-trivial strongly connected component (algebraic loop) needs to be isolated from the other variables of the system to calculate their initial values using fixed point iteration as described in \cref{def:fixedpoint}.
+After the \textit{Initialization Mode} state, all variables of all FMUs in the co-simulation scenario should be defined, and the co-simulation should be ready to enter the \textit{modelInitialized} state.
 
@@
 The approach is based on the strategy proposed in Gomes et al.
-\cite{Gomes2019b, BromanCompositionCo-Simulation}, but the approach in this work is extended with the ability to handle the initialization of algebraic loops.
+\cite{Gomes2019b, BromanCompositionCo-Simulation}, but the approach in this work is extended with the ability to handle the Initialization of algebraic loops.
 
@@
 %\subsubsection{Structure of the graph}
-The initialization algorithm starts by building a directed graph of the dependency between the interconnected variables of the FMUs.
-The graph is constructed based on the interconnected variables and internal connections (feed-through), as in \cref{def:initialization_graph}.
+The initialization algorithm starts by building a directed graph of the dependencies between the interconnected variables of the FMUs.
+The graph is constructed based on the interconnected variables and internal connections (feed-through); please see \cref{def:initialization_graph} for a formal definition of the graph.
 %Each interconnected variable in the system represents a node, and the edges are based on these connections.
@@
 The trivial ones are standard interconnected FMU variables, whose port operation should be performed only once during the initialization procedure.
-The calculation of an initialization order is performed in linear time based on the number of both external and internal connections using Tarjan's algorithm \cite{tarjan_1972}. 
+The calculation of an initialization order is performed in linear time based on the number of external and internal connections using Tarjan's algorithm \cite{tarjan_1972}. 
 %This algorithm is selected due to its properties. It solves two of the central issues of the initialization-phase of the co-simulation.
@@
 %\end{itemize}
-The algorithm is well-established, and there exist formal proofs of its correctness and properties\cite{stefanMerz}. 
+%The algorithm is well-established, and there exist formal proofs of its correctness and properties\cite{stefanMerz}. 
 % The algorithm is among the most efficient graph algorithms for accomplishing the defined goals.
@@
 %\subsubsection{Handling of algebraic loops}
-As described in earlier sections, it is essential to handle the algebraic loops by a particular initialization strategy since they otherwise would invalidate the result of the co-simulation.
-The strategy for managing algebraic loops is to identify and initialize them using a fixed point iteration until convergence.
+As described in earlier sections, it is essential to handle the algebraic loops by a particular initialization strategy since non-converging loops otherwise would invalidate the co-simulation result.
+The procedure for managing algebraic loops is identifying and initializing them using fixed point iteration until convergence.
 Since convergence is not guaranteed, this property is monitored using \cref{def:convergence}.
-If convergence is not established within a finite number of iteration, the co-simulation is rejected to avoid running an invalid simulation.
+Suppose convergence is not established within a finite number of iterations\footnote{We have chosen XX due to ---}, since the difference between the values of the SCC variables of two following iterations never approaches zero.
+In that case, the co-simulation is rejected to avoid running an invalid simulation.
 
@@
 An initialization procedure can be optimized since the FMI specification allows multiple \textit{set} or \textit{get} operations of the same FMU to be performed in bulk by grouping them together to a single operation over multiple variables with similar characteristic.
-This criteria of optimization is formalized in \cref{def:optimization}
+This criteria of optimization is formalized in \cref{def:optimization}.
 \begin{definition}[Optimization of a Initialization procedure]\label{def:optimization}
@@
 \cite{Gomes2019}.
-This proof is valid for this approach since the optimization does not change the structure of the Initialization Graph.
+Their proof is trivially shown to cover this approach since the presented optimization does not change the structure of the Initialization Graph.
 \\
@@
 Another solution is to apply this optimization strategy on the set of all valid co-simulation steps - yielding a potential very inefficient initialization algorithm.
+\todo{Describe efficiency of the initialization vs rest of the co-simulation}The Initialization of a co-simulation is typically
 
@@
 \end{figure}
+
+As seen from the algorithm in \cref{alg:initialization}, the algebraic loops are handled using a different strategy compared to the other trivial SCC of a single interconnected FMU variable.

### 2020-08-24 introduction.tex
Changes based on comments from external reviewers

@@
 One of the tools to manage the increasing complexity of such systems is co-simulation since it tackles their heterogeneous nature.
-Co-simulation is a technique to combine multiple black-box simulation units to compute the behavior of the combined models as a discrete trace (see, e.g., \cite{Kubler2000, Gomes2018}).
-The simulation units, often developed independently from each other, are coupled using a master algorithm, also often developed independently, that communicates with each simulation unit via its interface.
-This interface comprises functions for setting/getting inputs/outputs, and computing the associated model behavior over a given time interval.
+Co-simulation is a technique to combine multiple black-box simulation units to compute the combined models' behavior as a discrete trace (see, e.g., \cite{Kubler2000, Gomes2018}).
+The simulation units, often developed independently from each other, are coupled using a master algorithm, often developed independently, that communicates with each simulation unit via its interface.
+This interface comprises functions for setting/getting inputs/outputs and computing the associated model behavior over a given time interval.
 The Functional Mock-up Interface (FMI) standard \cite{Blochwitz2012, fmi_2019} is such an interface prescribing how to communicate with each simulation unit.
@@
 This work concentrates on the first.
-The FMI specifies criteria for how a single FMU shall be initialized.
-However, the FMI is not concerned with how a connected system of multiple FMUs is initialized correctly as a whole.
+The FMI standard specifies criteria for how a single FMU shall be initialized.
+However, FMI is not concerned with how a connected system of multiple FMUs is initialized correctly as a whole.
 
-The way a system of multiple FMUs should be initialized and interacted with depends on each FMUs implementation and interconnections to other FMUs \cite{gomes_lucio_vangheluwe_2019}, since these place precedence constraints between the FMU variables.
-These constraints can introduce algebraic loops, which places particular requirements on the initialization order to calculate the initial values of the variables in the algebraic loop\cite{Bastian2011a}.
+The way a system of multiple FMUs should be initialized and interacted with depends on each FMU's implementation and interconnections to other FMUs \cite{gomes_lucio_vangheluwe_2019}, since these place precedence constraints between the FMU variables.
+These precedence constraints can introduce algebraic loops between the FMU variables.
+An algebraic loop places particular requirements on the strategy for both the order of initialization and the method used to calculate the correct initial values of the variables in the algebraic loop\cite{Bastian2011a}.
 Algebraic loops occur whenever an interconnected FMU variable indirectly depends on itself.
 Not solving an algebraic loop can lead to a prohibitively high error in the co-simulation result \cite{Arnold2014}, and invalid results, as shown in \cref{sec:case_study}.
-For variables that do not belong in an algebraic loop, the initialization has to ensure that a variable is never read before it is set like the classical \textit{readers–writers problem}.
-For variable within an algebraic loop, the initialization has to make sure that all initial values have converged to a fixed point.
+It is crucial for all interconnected variables that the initialization procedure ensures that a variable is never read before it is set.
+For variables within an algebraic loop, the initialization must ensure that all initial values have converged to a fixed point before entering the next phase of the co-simulation.
 
@@
 This choice is driven by the fact that not all co-simulation scenarios containing algebraic loops are valid since those algebraic loops never converge, or might converge to unexpected solutions.
-However, as shown in \cref{sec:case_study}, algebraic loops can be essential to obtaining valid simulation results, and a well-established co-simulation framework should be able to handle these scenarios.
+However, as shown in \cref{sec:case_study}, solving algebraic loops can be essential to obtaining valid simulation results, and a well-established co-simulation framework should be able to handle these scenarios.
 
 \textit{Contribution:} This paper describes an approach for calculating the initialization order of an FMI-based co-simulation in linear time of the number of interconnected variables, even when algebraic loops are present.
-% The approach complies with the semantics of FMI and support the initialization of algebraic loops between interconnected FMU variables and identifies divergence in a co-simulation scenario. 
-The approach does not put any constraints on choosing a master algorithm that should be used to carry out the simulation. 
+% The approach complies with the semantics of FMI and supports the initialization of algebraic loops between interconnected FMU variables and identifies divergence in a co-simulation scenario. 
+The approach does not put any constraints on the master algorithm chosen to carry out the simulation. 
 The approach is realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2), introduced in \cite{Thule2019b}.
-The realized plugin has been tested for various co-simulation scenarios and compared to an existing approach that has been validated through academic and industrial applications. 
+The realized plugin has been tested for various co-simulation scenarios and compared to an existing Initializer that has been validated through academic and industrial applications. 
 Furthermore, the calculated initialization order is systematically verified by the semantics of co-simulation introduced in \cite{gomes_lucio_vangheluwe_2019,Gomes2019c}.

### 2020-08-24 paper.tex
Added some based on the feedback from Christian
add seprarte case study file
Changed the order of the initialization algorithm
case study equations (needs to be done by hand)
example gen bib and comments
Updated graph
Changes based on comments from external reviewers

@@
 \usepackage{cite}
+\usepackage[capitalise,nameinlink]{cleveref}
 \usepackage{url}
+\usepackage{pgfplots}
+\usepackage{tikz}
+\usepackage{environ}
+\usepackage{filecontents}
 \usepackage{todonotes}
+\usepackage{cleveref}
 % Used for displaying a sample figure. If possible, figure files should
@@
 \input{commands}
+\input{case_study_results}
 
 \begin{document}
+
+\NewEnviron{scaletikzpicturetowidth}[1]{%
+  \def\tikz@width{#1}%
+  \def\tikzscale{1}\begin{lrbox}{\measure@tikzpicture}%
+  \BODY
+  \end{lrbox}%
+  \pgfmathparse{#1/\wd\measure@tikzpicture}%
+  \edef\tikzscale{\pgfmathresult}%
+  \BODY
+}
 %
-\title{An FMI-Based Initialization Plugin for INTO-CPS Maestro 2}
+\title{An FMI-Based Initialization Plugin for INTO-CPS Maestro 2\thanks{We are grateful to the Poul Due Jensen Foundation, which has supported the establishment of a new Centre for Digital Twin Technology at Aarhus University.
+Finally, we thank the reviewers for the thorough feedback.}}
+
 %
@@
 Casper Thule\inst{1} \and
-Claudio Gomes \inst{1}}
+Cláudio Gomes \inst{1}}
 %
@@
 %
+
 \maketitle              % typeset the header of the contribution
@@
 
-%This paper's main contribution is to calculate an initialization order of a co-simulation scenario potentially containing algebraic loops.
-The approach make the circular dependencies between the interconnected converge in the initialization, so the initial values of the interconnected variables in the system being simulated is stable at the time the co-simulation is started.
-
-\subsection{Case study}
-Claudio writes this section
+\input{casestudy.tex}
 
@@
 \bibliographystyle{splncs04}
-\bibliography{gen_bib}
+\bibliography{gen_bib,gen_bib_claudio}
 

### 2020-08-24 realization.tex
Changes based on comments from external reviewers

@@
 \section{Realization of a Maestro 2 Plugin}\label{sc:implementation}
-This approach has been realized as a Maestro 2 plugin that generates the \textit{Initialization}-phase of a co-simulation specification expressed in MaBL.
-It calculates the specification based on a list of FMU-components of a co-simulation scenario, and a specific plugin-configuration to let the user supply initial values of FMU variables with $causality=parameter$.
-A correction initialization specification can be calculated by the plugin if the co-simulation scenario is adhering to the behavior dictated by the definition given in \cref{def:convergence}.
+The presented approach has been realized as a Maestro 2 expansion plugin that generates the \textit{Initialization}-phase of a co-simulation specification expressed in MaBL.
+It calculates the MABL-specification based on a list of FMU-components of a co-simulation scenario and a specific plugin-configuration to let the user supply the initial values of  FMU parameters and fine-tune the initialization of the system.
+The plugin can calculate a correct initialization specification if the co-simulation scenario adheres to the behavior dictated by the definition given in \cref{def:convergence} that all algebraic loops in the scenario convergences within a finite number of iterations.
 
-The plugin optimizes the initialization order by grouping operations that can be executed in \textit{parallel} to take advantage of FMI's ability to \textit{set} or \textit{get} multiple variables in bulk from the same FMU.
+The plugin optimizes the initialization order by grouping operations that can be executed in \textit{parallel} to take advantage of FMI's ability to \textit{set} or \textit{get} multiple variables of the same FMU in bulk.
 The criteria for this optimization is defined in \cref{def:optimization}.
 The developed plugin has been tested on numerous co-simulation examples from the INTO-CPS universe\cite{Maestro} and compared with the existing \textit{Initializer} of Maestro.
-The plugin has been tested in the whole Maestro 2 pipeline to practically verify that it can be used in a co-simulation where the generated initialization procedure is integrated as a part of a complete co-simulation to verify the initialization procedure's integration with a master algorithm.
+The plugin has been tested as a part of the Maestro 2 pipeline.
 
 \subsection{Realization of the Topological Sorting}
-The topological sorting algorithm (Tarjan's Algorithm) is implemented in Scala.
-The motivation for choosing Scala is its relation to JVM and the connection to Slang and the Logika framework\cite{inbook}.
+The topological sorting algorithm (Tarjan's Algorithm) is implemented in Scala\cite{Scala}, an object-oriented programming language incorporating many features from the functional programming paradigm.
+The motivation for choosing Scala is its relation to JVM and the connection to Slang and the Sireum framework\cite{inbook}.
+Slang (Sireum Language)is a programming language based on Scala and developed at Kansas State University (KSU) to develop and reason about critical software systems.
+Sireum is a framework for performing programming language analysis, reasoning, and verification of CPS also developed at KSU.
+The tool in the Sireum framework for performing automated verification analysis of a piece of Slang code is called Logika.
 The connection to Slang and Logika will be investigated in the future.
 The Logika framework will be used to formally verify the implemented plugin and be used to explore how the contract-based nature of Slang can be used to obtain more reliable results of co-simulations.
-The topological sorting returns a topological order of strongly connected components.
-This order is the order of initialization, where the elements containing more than a single element denotes an algebraic loop that requires a particular initialization strategy.
+The topological sorting returns an order of strongly connected components.
+This order is the initialization order, where the elements containing more than a single element denotes an algebraic loop that requires a particular initialization strategy.
 
 \subsection{Verification of the Initialization Order}
-The realized plugin is verified in several ways using traditional proof methods and practical verification against an established co-simulation Verifier.
-The approach behind the plugin has been verified by Gomes et al.
-that in \cite{gomes_lucio_vangheluwe_2019} proved the correctness of using the topological order of a dependency graph of the interconnected variables to generate for the order of the operations that need to be performed in a co-simulation step (both the initialization procedure and an arbitrary step).
+The plugin is verified in several ways.
+The approach is established using traditional proof methods, and the plugin has been practically verified against an established co-simulation step verifier.
 Gomes et al.
-used a graph based on FMU-operations (\textit{Set, Get, doStep}) instead of interconnected variables, which is the approach described in this paper.
-The simplification of using the interconnected variables is valid since this approach only cares about initialization and, therefore, does not need to care about the time of each FMU.
-This does that we can omit all the \textit{doStep} nodes, it means that each interconnected variable can only perform one of the two operations \textit{get} or \textit{set} as described by the \cref{def:getout,def:setin}.
-This approach does, therefore, end up with a subgraph of the graph by Gomes et al.
-The proof from \cite{gomes_lucio_vangheluwe_2019} can trivially be modified to the graph/approach presented in this paper.
+has verified the approach in \cite{gomes_lucio_vangheluwe_2019} they proved the correctness of using the topological order of a dependency graph of the interconnected variables as the order of the operations that need to be performed in a co-simulation step (both the initialization procedure and an arbitrary step).
+Gomes et al.
+\cite{gomes_lucio_vangheluwe_2019} used a graph based on FMU-operations (\textit{Set, Get, doStep}) in their proof instead of interconnected variables, which is the approach described in this paper.
+The simplification of using the interconnected variables is valid and preserves the properties proved by Gomes et al.
+since this approach only considers the initialization phase of a co-simulation, making the timing aspect irrelevant.
+Due to this fact all the \textit{doStep} nodes can be omitted, meaning each interconnected variable can only perform one of the following two operations \textit{get} or \textit{set} as described by the \cref{def:getout,def:setin}.
+This approach, therefore, ends up with a subgraph of the graph by Gomes et al.\cite{gomes_lucio_vangheluwe_2019}, which allows the proof from \cite{gomes_lucio_vangheluwe_2019} to be modified to the approach presented in this paper trivially.
 
-\subsubsection{Practical verification against a Verifier} 
-Gomes et al.'s main contribution is an implementation of the criteria for a valid FMI based co-simulation formulated in Prolog freely available to be used in other projects\footnote{\url{http://msdl.cs.mcgill.ca/people/claudio/projs/PrologCosimGeneration.zip}}.
+\subsubsection{Practical verification against an established Verifier} 
+Gomes et al.'s \cite{gomes_lucio_vangheluwe_2019} main contribution is a Prolog implementation of the principles for a valid FMI based co-simulation scenario.
+The Prolog program is freely available to be used in other projects\footnote{\url{http://msdl.cs.mcgill.ca/people/claudio/projs/PrologCosimGeneration.zip}}.
 The Prolog implementation was used in their research to verify their approach for generating co-simulation algorithms formally.
 The Prolog realization encapsulates all the rules of a valid co-simulation step (both master-algorithm and an initialization algorithm).
-This work includes an integration from the developed plugin to the Prolog Verifier.
-The integration has been realized to systematically verify the correctness of the calculated initialization order against an established and recognized co-simulation Algorithm Verifier.
-The integration queries the Prolog database with a co-simulation environment and a calculated initialization order to verify the order's correctness.
+The realized Initializer includes an integration from the developed plugin to the Prolog Verifier.
+The integration is a Java program based on JIProlog \cite{JIProlog} - a library that allows calling Prolog predicates directly from Java.
+The integration queries the Prolog database by Gomes et al.
+with a co-simulation scenario and a calculated initialization order to verify the order's correctness.
 The integration performs all the necessary transformations of the dependency graph (see definition \ref{def:initialization_graph}) used in the Maestro plugin to a graph of FMU operations used in the Prolog database.
 The transformation is based on the definitions \ref{def:getout} and \ref{def:setin}.
-The Prolog integration is not applied if the graph contains algebraic loops since the Prolog database does not support these scenarios.
+The integration has been realized to systematically verify the calculated initialization order's correctness against an established and recognized co-simulation Algorithm Verifier.
+In co-simulation scenarios containing algebraic loop, the integration to the Prolog implementation is bypassed since Gomes et al. 's Prolog program does not support these scenarios.

### 2020-08-24 relatedwork.tex
Changes based on comments from external reviewers

@@
 Prior work \cite{Gomes2019, BromanCompositionCo-Simulation} is looking into the generation of co-simulation algorithms (both master and initialization algorithms) for FMI-based scenarios.
-Their generation technique is like ours based on a dependency graph of the operations of a co-simulation step.
+Their generation technique is like ours, based on a dependency graph of the operations of a co-simulation step.
 Both Gomes and Broman present an approach for using the topological order of a dependency graph to establish a correct order of operations in a co-simulation step of a given co-simulation scenario.
@@
 \cite{BromanCompositionCo-Simulation} also suggest to use the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of port-operations.
-Nevertheless, they explicitly specify the requirement for cycle freedom in the dependency graph as a precondition for the generation of a valid co-simulation.
+Nevertheless, they explicitly specify the requirement for cycle freedom in the dependency graph as a precondition for generating a valid co-simulation.
 It means they refuse all co-simulation scenarios containing algebraic loops.
@@
 \cite{Amalio2016CheckingCo-simulation} investigate how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS.
-The publication's purpose is like ours to avoid invalid co-simulation scenarios.
+The publication's purpose is like ours, to avoid invalid co-simulation scenarios.
 Nevertheless, they achieve this by excluding co-simulation scenarios containing algebraic loops.
@@
 
-The work by Gomez et al. .\cite{EvoraGomez2019a} is similar to ours. They use Tarjan's SCC algorithm to generate a sorted DAG of strongly connected components to solve the initialization problem.
-Even though their work is very similar to ours, we extend their approach with verification against the simulation semantics resulting in a formally more sound approach.
+The work by Gomez et al.\cite{EvoraGomez2019a} is similar to ours. They use Tarjan's SCC algorithm to generate a sorted DAG of strongly connected components to solve the initialization problem.
+Even though their work is very similar to ours, we extend their approach with the verification against the simulation semantics resulting in a formally more sound approach.
 However, further work will look into further improvements and formal verification of the current approach.

### 2020-11-10 background.tex
fix bib.bib

@@
 
-It should be noted that a trivial SCC (\see \cref{def:loop}) is only a single get or set action and is not regarded as a fixed point outside \cref{def:initialization}, but just a simple computation.
+It should be noted that a trivial SCC (see \cref{def:loop}) is only a single get or set action and is not regarded as a fixed point outside \cref{def:initialization}, but just a simple computation.
 
@@
 \subsection{INTO-CPS Maestro 2}
-INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}}~\cite{Thule2019b} is a framework for creating simulation specifications and executing such specifications.
+INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}}~\cite{Thule2020a} is a framework for creating simulation specifications and executing such specifications.
 The framework is FMI-based and set to supersede Maestro~\cite{Maestro} with the main goal of supporting research into co-simulation based on FMI.

### 2020-11-10 initializationorder.tex
fix bib.bib

@@
 The approach is based on the strategy proposed in Gomes et al.
-\cite{Gomes2019b, BromanCompositionCo-Simulation}, but the approach in this work is extended with the ability to handle the Initialization of algebraic loops.
+\cite{Gomes2020b, BromanCompositionCo-Simulation}, but the approach in this work is extended with the ability to handle the Initialization of algebraic loops.
 

### 2020-11-10 introduction.tex
fix bib.bib

@@
 
-A typical co-simulation consists of three phases: initialization, simulation, and teardown \cite{Thule2019b}.
+A typical co-simulation consists of three phases: initialization, simulation, and teardown \cite{Thule2020a}.
 This work concentrates on the first.
@@
 The approach does not put any constraints on the master algorithm chosen to carry out the simulation. 
-The approach is realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2), introduced in \cite{Thule2019b}.
+The approach is realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2), introduced in \cite{Thule2020a}.
 The realized plugin has been tested for various co-simulation scenarios and compared to an existing Initializer that has been validated through academic and industrial applications. 

### 2020-11-13 paper.tex
fix bib.bib
Updates from Overleaf

@@
 \usepackage{cleveref}
+\usepackage{listings}
+\newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\includegraphics[width=10pt]{images/orcid.png}}}
 % Used for displaying a sample figure. If possible, figure files should
@@
 \input{case_study_results}
+
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},   
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\tiny\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\ttfamily\footnotesize,
+    breakatwhitespace=false,         
+    breaklines=true,                 
+    captionpos=b,                    
+    keepspaces=true,                 
+    numbers=left,                    
+    numbersep=5pt,                  
+    showspaces=false,                
+    showstringspaces=false,
+    showtabs=false,                  
+    tabsize=2
+}
+\lstset{style=mystyle}
 
@@
 %
-\author{Simon Thrane Hansen\inst{1} \and
-Casper Thule\inst{1} \and
-Cláudio Gomes \inst{1}}
+\author{Simon Thrane Hansen\inst{1} \orcidID{0000-0002-3796-4319} \and
+Casper Thule\inst{1} \orcidID{0000-0001-6606-9236} \and
+Cláudio Gomes \inst{1} \orcidID{0000-0003-2692-9742}}
 %

### 2020-11-13 background.tex
Updates from Overleaf

@@
 
-\subsection{FMU definitions}
+\subsection{FMU Definitions}
 To describe the formalization of FMUs, we adopt the vocabulary from \cite{gomes_lucio_vangheluwe_2019}.
@@
 This paper is only concerned with the initialization-phase of a co-simulation, making time of an FMU irrelevant.
-The formalization from Gomes et al.
-is extended with new definitions regarding algebraic loops, and convergence of fixed point iteration.
+The formalization from Gomes et al.\cite{gomes_lucio_vangheluwe_2019} is extended with new definitions regarding algebraic loops, and convergence of fixed point iteration.
 \begin{definition}[FMU]\label{def:fmu}
@@
 \end{definition}
-Note it is possible for a single output to connect to a multiple inputs, but a single input can only rely on a single output.
-%In Defn. 2, it seems that L is a function U --> Y, does that mean that each input variable feeds-through only one output variable?
+Note a single output can connect to multiple inputs, but a single input can only rely on a single output.
 The following definitions correspond to the operations that are permitted in the initialization phase of a co-simulation.
@@
 \end{definition}
-%A faulty check will incur TODO
 
 \begin{definition}[Fixed Point]\label{def:fixedpoint}
-The $\fixedpoint{l}$ represents an order sequence of the setting or getting of all input and output variables of a given SCC $l$, see \cref{def:loop} for a definition of SCC.
+The $\fixedpoint{l}$ represents an ordered sequence of the setting or getting of all variables of a given SCC $l$, see \cref{def:loop} for a definition of SCC.
 The $\fixedpoint{l} \subseteq \bigcup_{c \in \fmus} \set{\fget{c},\fset{c}}$ 
@@
   and $i$ denoting the order of the function call.
-  loops in defined as the set of all SCC see \cref{def:loop}.
+  Loops is defined as the set of all SCC see \cref{def:loop}.
 \end{definition}
@@
     \includegraphics[width=1\textwidth]{images/quarter_car_SCC.pdf}
-    \caption{An FMU co-simulation scenario of the Quarter car and its Initialization Graph denoted with SCCs}
+    \caption{An FMU co-simulation scenario of the Quarter car and its Initialization Graph denoted with SCCs.}
     \label{fig:fmu_cycle}
@@
 An algebraic loop is defined as a non-trivial, strongly connected component of the graph in \cref{def:initialization_graph}.
-Formally, a strong connected component satisfies $\set{a,b \in SCC: \mathit{Path}(a,b)}$, where $\mathit{Path}(a,b)$ is true when there's a path (including an empty path) between nodes $a$ and $b$ ($\mathit{Path}(a,a)$ is always true).
+Formally, a strong connected component satisfies $\set{a,b \in SCC: \mathit{Path}(a,b)}$, where $\mathit{Path}(a,b)$ is true when there's a path (including an empty path from a node to itself) between nodes $a$ and $b$ ($\mathit{Path}(a,a)$ is always true).
 An $SCC$ is non-trivial when it has more than one node.
@@
 
-Since the edges of the graph represent dependencies between variables, the value of every variable in a non-trivial strong component depends on itself.
+Since the edges of the graph represent dependencies between the variables, the value of every variable in a non-trivial strong component depends on itself.
 Let $X$ denote a vector of one or more variables whose value depends on itself.
@@
 \subsection{INTO-CPS Maestro 2}
-INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}}~\cite{Thule2020a} is a framework for creating simulation specifications and executing such specifications.
+INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}.}~\cite{Thule2019b} is a framework for creating simulation specifications and executing such specifications.
 The framework is FMI-based and set to supersede Maestro~\cite{Maestro} with the main goal of supporting research into co-simulation based on FMI.
@@
 This process is known as expansion, and a specification without any expansions remaining is a fully expanded MaBL specification.
+An example of a part of the folded MaBL specification of the case study example of \cref{sec:case_study} can be seen below.
 
+\begin{lstlisting}[language=C++]
+simulation
+import Initializer;
+{
+FMI2 chassis = load("FMI2", "{8c4e810f-3df3-4a00-8276-176fa3c9f000}", "src/chassis-c.fmu");
+...
+IFmuComponent components[3]={chassis,suspension, road};
+expand initialize(components,START_TIME, END_TIME);
+...
+}
+\end{lstlisting}
 To conduct a co-simulation, Maestro2 also features an interpreter that can execute a fully expanded MaBL specification, resulting in the execution of the co-simulation.

### 2020-11-13 conclusion.tex
Updates from Overleaf

@@
-\section{Concluding remarks}\label{sc:summary}
+\section{Concluding Remarks}\label{sc:summary}
 This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario potentially containing algebraic loops.
@@
 
-\paragraph*{\textbf{Acknowlegements.}}We would like to thank Stefan Hallerstede, Christian Møldrup Legaard, and Peter Gorm Larsen for providing valuable input to this paper and the developed plugin.
+\subsubsection*{Acknowledgements} We would like to thank Stefan Hallerstede, Christian Møldrup Legaard, and Peter Gorm Larsen for providing valuable input to this paper and the developed plugin.

### 2020-11-13 casestudy.tex

@@
-\section{Case study}
+\section{Case Study}
 \label{sec:case_study}
@@
 We omit the equations that each FMU is solving but note that gravity acts on both wheel and chassis masses and that the origin of each mass is when the springs are not displaced.
-The equations and simulation model for this example are available online\footnote{\url{https://github.com/SimplisticCode/QuarterCarCaseStudy}}.
+The equations and simulation model for this example are available online\footnote{\url{https://github.com/SimplisticCode/QuarterCarCaseStudy}.}.
 
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{images/quarter_car.pdf}
+    \includegraphics[width=1\textwidth]{images/quarter_car_FMUs.pdf}
     \caption{Quarter car model co-simulation. Adapted from \cite[Section 6.4]{Schramm2014}.}
@@
 The FMUs need initial conditions specified by equations that restrict the possible initial values for the position and velocity of the wheel and chassis masses.
-\Cref{fig:init_state_0_sim} illustrates what happens when we simply set those positions and velocities to zero.
-Note that, because of gravity, the car chassis bounces on the suspension wheel, with a maximum compression of about 17cm.
-This is most likely an invalid scenario, as the suspension of the car might not be rated to be displaced that much.
-In any case, the purpose of simulation studies involving quarter car models is to understand how well a suspension system absorbs shock when the car goes over a bump, not when the car is \emph{falls on the road}, which is what the simulation results in \cref{fig:init_state_0_sim} resemble.
+\Cref{fig:init_state_0_sim} illustrates what happens when we set those positions and velocities to zero.
+Note that, because of gravity, the car chassis bounces on the suspension wheel, with a maximum compression of about 17cm compared to when the system's springs are uncompressed.
+This is most likely an invalid scenario, as the car's suspension might not be rated to be displaced that much.
+In any case, the purpose of simulation studies involving quarter car models is to understand how well a suspension system absorbs shock when the car goes over a bump, not when the car \emph{falls on the road}, which is what the simulation results in \cref{fig:init_state_0_sim} resemble.
 
@@
 & F_{\mathit{total}} = F_R + F_A - F_{gR} & \text{Total forces acting on tire} \\
-& a_R = (1/m_R) * F_{\mathit{total}}  & \text{Acceleration of tire}
+& a_R = (1/m_R) * F_{\mathit{total}}  & \text{Acceleration of tire}.
 \end{align}
@@
 & F_{gA} = 9.81 * m_A  & \text{Gravity on the chassis} \\
-& a_A = (1/m_A) * (- F_A - F_{gA})  & \text{Acceleration of chassis}
+& a_A = (1/m_A) * (- F_A - F_{gA})  & \text{Acceleration of chassis}.
 \end{align}

### 2020-11-13 initializationorder.tex

--- 2020-08-24 initializationorder.tex
@@
 
-\subsection{Method to calculate the initialization order}
+\subsection{Method to Calculate the Initialization Order}
 This section describes the approach taken to calculate the initialization order of the interconnected FMU variables.
@@
 %\subsubsection{Handling of algebraic loops}
-As described in earlier sections, it is essential to handle the algebraic loops by a particular initialization strategy since non-converging loops otherwise would invalidate the co-simulation result.
-The procedure for managing algebraic loops is identifying and initializing them using fixed point iteration until convergence.
-Since convergence is not guaranteed, this property is monitored using \cref{def:convergence}.
-Suppose convergence is not established within a finite number of iterations\footnote{We have chosen XX due to ---}, since the difference between the values of the SCC variables of two following iterations never approaches zero.
-In that case, the co-simulation is rejected to avoid running an invalid simulation.
+As described in earlier sections, it is essential to handle algebraic loops by a particular initialization strategy since the loops otherwise would invalidate the co-simulation result.
+The procedure for initializing algebraic loops is identifying and initializing them using a fixed point iteration strategy until convergence.
+Since convergence is not guaranteed, this property is monitored using \cref{def:convergence} to see if the difference between all the output variables of two successive iterations is below a defined threshold.
+Suppose convergence is not established within a finite number of iterations\footnote{5 iterations is the default in our approach.
+This number is based on experience.}, the co-simulation scenario is rejected to avoid running an invalid simulation.
 
 \subsection{Optimization of a Initialization Procedure}
-An initialization procedure can be optimized since the FMI specification allows multiple \textit{set} or \textit{get} operations of the same FMU to be performed in bulk by grouping them together to a single operation over multiple variables with similar characteristic.
+An initialization procedure can sometimes be optimized since the FMI specification allows multiple \textit{set} or \textit{get} operations of the same FMU to be performed in bulk by grouping them together to a single operation over multiple variables with similar characteristic.
 This criteria of optimization is formalized in \cref{def:optimization}.
@@
 \cite{Gomes2019}.
-Their proof is trivially shown to cover this approach since the presented optimization does not change the structure of the Initialization Graph.
+Their proof is trivially shown to cover this approach since the optimization does not change the structure of the Initialization Graph.
 \\
@@
 Another solution is to apply this optimization strategy on the set of all valid co-simulation steps - yielding a potential very inefficient initialization algorithm.
-\todo{Describe efficiency of the initialization vs rest of the co-simulation}The Initialization of a co-simulation is typically
+The initialization of a co-simulation is typically not the most time consuming or computational heaviest part of the co-simulation.
+However, it is still considered a low hanging fruit to apply this optimization to optimize the initialization-
 
-\subsection{The entire Initialization Strategy}
+\subsection{The Complete Initialization Strategy}
 The pseudo-code in \cref{alg:initialization} formulates the entire initialization strategy of the interconnected variables of a co-simulation scenario.
@@
 
-As seen from the algorithm in \cref{alg:initialization}, the algebraic loops are handled using a different strategy compared to the other trivial SCC of a single interconnected FMU variable.
+As seen from the algorithm in \cref{alg:initialization}, the algebraic loops are handled using a different initialization strategy compared to the other trivial SCC of a single interconnected FMU variable.

### 2020-11-13 realization.tex

@@
 The presented approach has been realized as a Maestro 2 expansion plugin that generates the \textit{Initialization}-phase of a co-simulation specification expressed in MaBL.
-It calculates the MABL-specification based on a list of FMU-components of a co-simulation scenario and a specific plugin-configuration to let the user supply the initial values of  FMU parameters and fine-tune the initialization of the system.
-The plugin can calculate a correct initialization specification if the co-simulation scenario adheres to the behavior dictated by the definition given in \cref{def:convergence} that all algebraic loops in the scenario convergences within a finite number of iterations.
+The plugin calculates the MaBL-specification based on the FMUs of a co-simulation scenario and a specific plugin-configuration to let the user supply the initial values of FMU parameters and fine-tune the initialization of the system.
+The plugin can calculate a correct initialization specification if the co-simulation scenario adheres to the behavior dictated by the definition given in \cref{def:convergence} meaning all algebraic loops in the scenario convergences within a finite number of iterations.
 
-The plugin optimizes the initialization order by grouping operations that can be executed in \textit{parallel} to take advantage of FMI's ability to \textit{set} or \textit{get} multiple variables of the same FMU in bulk.
+The plugin optimizes the initialization order by grouping operations that can be executed in \textit{parallel} to take advantage of FMI's ability to \textit{set} or \textit{get} multiple variables of a single FMU in bulk.
 The criteria for this optimization is defined in \cref{def:optimization}.
-The developed plugin has been tested on numerous co-simulation examples from the INTO-CPS universe\cite{Maestro} and compared with the existing \textit{Initializer} of Maestro.
-The plugin has been tested as a part of the Maestro 2 pipeline.
+The developed plugin has been tested on numerous co-simulation scenarios from the INTO-CPS universe\cite{Maestro} and compared with the existing \textit{Initializer} of Maestro.
+The plugin has been tested as a part of the complete Maestro 2 pipeline.
 
@@
 The topological sorting algorithm (Tarjan's Algorithm) is implemented in Scala\cite{Scala}, an object-oriented programming language incorporating many features from the functional programming paradigm.
-The motivation for choosing Scala is its relation to JVM and the connection to Slang and the Sireum framework\cite{inbook}.
-Slang (Sireum Language)is a programming language based on Scala and developed at Kansas State University (KSU) to develop and reason about critical software systems.
+The motivation for choosing Scala\cite{Scala} is its relation to JVM and the connection to Slang and the Sireum framework\cite{inbook}.
+Slang (Sireum Language) is a programming language based on Scala, developed at Kansas State University (KSU), to develop and reason about critical software systems.
 Sireum is a framework for performing programming language analysis, reasoning, and verification of CPS also developed at KSU.
-The tool in the Sireum framework for performing automated verification analysis of a piece of Slang code is called Logika.
-The connection to Slang and Logika will be investigated in the future.
-The Logika framework will be used to formally verify the implemented plugin and be used to explore how the contract-based nature of Slang can be used to obtain more reliable results of co-simulations.
-The topological sorting returns an order of strongly connected components.
-This order is the initialization order, where the elements containing more than a single element denotes an algebraic loop that requires a particular initialization strategy.
+Logika is one of the tools in the Sireum framework used for performing automated formal verification of a piece of Slang code using the theorem prover Z3\cite{Z3prover2020Sep}.
+The connection of the implementation to Slang and Logika will be investigated in future work.
+The plan is to use the Logika framework to formally verifying the plugin.
+This will also be used to explore how Slang's contract-based nature can be used to obtain more reliable results of co-simulations.
+Tarjan's algorithm returns a topological order of strongly connected components.
+The returned order is the initialization order, where the non-trivial strongly connected components denote an algebraic loop requiring a particular initialization strategy.
 
 \subsection{Verification of the Initialization Order}
-The plugin is verified in several ways.
-The approach is established using traditional proof methods, and the plugin has been practically verified against an established co-simulation step verifier.
+The plugin is verified using several methods.
+The plugin approach is established using traditional proof methods, and the plugin has been practically verified against an established co-simulation step verifier.
 Gomes et al.
-has verified the approach in \cite{gomes_lucio_vangheluwe_2019} they proved the correctness of using the topological order of a dependency graph of the interconnected variables as the order of the operations that need to be performed in a co-simulation step (both the initialization procedure and an arbitrary step).
+have verified the approach in \cite{gomes_lucio_vangheluwe_2019}; they proved the correctness of using the topological order of a dependency graph of the interconnected FMU-variables as the order of the operations in a co-simulation step (both the initialization procedure and an arbitrary step).
 Gomes et al.
-\cite{gomes_lucio_vangheluwe_2019} used a graph based on FMU-operations (\textit{Set, Get, doStep}) in their proof instead of interconnected variables, which is the approach described in this paper.
-The simplification of using the interconnected variables is valid and preserves the properties proved by Gomes et al.
-since this approach only considers the initialization phase of a co-simulation, making the timing aspect irrelevant.
-Due to this fact all the \textit{doStep} nodes can be omitted, meaning each interconnected variable can only perform one of the following two operations \textit{get} or \textit{set} as described by the \cref{def:getout,def:setin}.
-This approach, therefore, ends up with a subgraph of the graph by Gomes et al.\cite{gomes_lucio_vangheluwe_2019}, which allows the proof from \cite{gomes_lucio_vangheluwe_2019} to be modified to the approach presented in this paper trivially.
+\cite{gomes_lucio_vangheluwe_2019} used a graph of FMU-operations (\textit{Set, Get, doStep}) in their proof instead of interconnected FMU-variables, which is the approach of this paper.
+The simplification of using the interconnected FMU-variables is valid and preserves the properties proved by Gomes et al.
+since this approach only considers the initialization phase of a co-simulation.
+This makes it possible to omit all the \textit{doStep} nodes from Gomes et al.'s graph, eventually ending up with a graph similar to the initialization graph described in \cref{def:initialization_graph}.
+This approach is a subgraph of the graph by Gomes et al.\cite{gomes_lucio_vangheluwe_2019}, which allows their proof to be modified to the approach presented in this paper.
 
-\subsubsection{Practical verification against an established Verifier} 
-Gomes et al.'s \cite{gomes_lucio_vangheluwe_2019} main contribution is a Prolog implementation of the principles for a valid FMI based co-simulation scenario.
-The Prolog program is freely available to be used in other projects\footnote{\url{http://msdl.cs.mcgill.ca/people/claudio/projs/PrologCosimGeneration.zip}}.
-The Prolog implementation was used in their research to verify their approach for generating co-simulation algorithms formally.
+\subsubsection{Practical Verification against an Established Verifier} 
+Gomes et al.'s \cite{gomes_lucio_vangheluwe_2019} main contribution is a Prolog implementation of the principles for a valid FMI based co-simulation step \footnote{\url{http://msdl.cs.mcgill.ca/people/claudio/projs/PrologCosimGeneration.zip}.}.
+Gomes et al.
+use the Prolog implementation in their research to verify their approach for generating different co-simulation algorithms.
 The Prolog realization encapsulates all the rules of a valid co-simulation step (both master-algorithm and an initialization algorithm).
-The realized Initializer includes an integration from the developed plugin to the Prolog Verifier.
+The Initializer includes an integration to the Prolog Verifier.
 The integration is a Java program based on JIProlog \cite{JIProlog} - a library that allows calling Prolog predicates directly from Java.
-The integration queries the Prolog database by Gomes et al.
-with a co-simulation scenario and a calculated initialization order to verify the order's correctness.
+The integration is used to check the initialization order against the rules in the Prolog database.
 The integration performs all the necessary transformations of the dependency graph (see definition \ref{def:initialization_graph}) used in the Maestro plugin to a graph of FMU operations used in the Prolog database.
@@
 The integration has been realized to systematically verify the calculated initialization order's correctness against an established and recognized co-simulation Algorithm Verifier.
-In co-simulation scenarios containing algebraic loop, the integration to the Prolog implementation is bypassed since Gomes et al. 's Prolog program does not support these scenarios.
+The Prolog implementation does support co-simulation scenarios containing algebraic loop, so these scenarios are not tested against the Prolog database.

### 2020-11-13 background.tex
Updated report to handin

@@
 The graph is the foundation for the calculation of the initialization procedure and is therefore referred to as the Initialization Graph.
-The graph construction is similar to the one in \cite{Gomes2019c}, except the later focuses on a general co-simulation step, while this work focus on the initialization phase.
+The graph construction is similar to the one in \cite{Gomes2020b}, except the later focuses on a general co-simulation step, while this work focus on the initialization phase.
 
@@
 \subsection{INTO-CPS Maestro 2}
-INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}.}~\cite{Thule2019b} is a framework for creating simulation specifications and executing such specifications.
+INTO-CPS Maestro 2\footnote{currently in alpha \url{https://github.com/INTO-CPS-Association/maestro/tree/2.0.0-alpha}.}~\cite{Thule2020a} is a framework for creating simulation specifications and executing such specifications.
 The framework is FMI-based and set to supersede Maestro~\cite{Maestro} with the main goal of supporting research into co-simulation based on FMI.

### 2020-11-13 conclusion.tex
Updated report to handin

@@
 The approach is realized as an expansion plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\
-Future work includes formal verification of the plugin using the Logika framework\cite{inbook}.
+Future work includes formal verification of the plugin using the Logika framework\cite{Robby2018}.
 We will also look into the generation of a verification strategy for the whole Maestro 2 framework to examine how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.

### 2020-11-13 introduction.tex
Updated report to handin

@@
 One of the tools to manage the increasing complexity of such systems is co-simulation since it tackles their heterogeneous nature.
-Co-simulation is a technique to combine multiple black-box simulation units to compute the combined models' behavior as a discrete trace (see, e.g., \cite{Kubler2000, Gomes2018}).
+Co-simulation is a technique to combine multiple black-box simulation units to compute the combined models' behavior as a discrete trace (see, e.g., \cite{Kubler2000,Gomes2018}).
 The simulation units, often developed independently from each other, are coupled using a master algorithm, often developed independently, that communicates with each simulation unit via its interface.
 This interface comprises functions for setting/getting inputs/outputs and computing the associated model behavior over a given time interval.
-The Functional Mock-up Interface (FMI) standard \cite{Blochwitz2012, fmi_2019} is such an interface prescribing how to communicate with each simulation unit.
+The Functional Mock-up Interface (FMI) standard \cite{Blochwitz2012,FMI2014} is such an interface prescribing how to communicate with each simulation unit.
 The interface is used to connect different simulation units, called Functional Mock-up Units (FMUs), exchange values between them, and make them progress in time.
@@
 
-Other approaches for the generation of co-simulation algorithms have avoided co-simulation scenarios containing algebraic loops since their presence reduces the chance of obtaining a deterministic co-simulation result\cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation, Gomes2019c}.
+Other approaches for the generation of co-simulation algorithms have avoided co-simulation scenarios containing algebraic loops since their presence reduces the chance of obtaining a deterministic co-simulation result\cite{Amalio2016,Broman2013,Gomes2020b}.
 This choice is driven by the fact that not all co-simulation scenarios containing algebraic loops are valid since those algebraic loops never converge, or might converge to unexpected solutions.
@@
 The realized plugin has been tested for various co-simulation scenarios and compared to an existing Initializer that has been validated through academic and industrial applications. 
-Furthermore, the calculated initialization order is systematically verified by the semantics of co-simulation introduced in \cite{gomes_lucio_vangheluwe_2019,Gomes2019c}.
+Furthermore, the calculated initialization order is systematically verified by the semantics of co-simulation introduced in \cite{gomes_lucio_vangheluwe_2019,Gomes2020b}.
 

### 2020-11-13 relatedwork.tex
Updated report to handin

@@
 \section{Related Work}
-Prior work \cite{Gomes2019, BromanCompositionCo-Simulation} is looking into the generation of co-simulation algorithms (both master and initialization algorithms) for FMI-based scenarios.
+Prior work \cite{Gomes2019,Broman2013} is looking into the generation of co-simulation algorithms (both master and initialization algorithms) for FMI-based scenarios.
 Their generation technique is like ours, based on a dependency graph of the operations of a co-simulation step.
@@
 Broman et al.
-\cite{BromanCompositionCo-Simulation} also suggest to use the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of port-operations.
+\cite{Broman2013} also suggest to use the topological sorting of a dependency graph of the interconnected variables to detect algebraic loops and discover the partial order of port-operations.
 Nevertheless, they explicitly specify the requirement for cycle freedom in the dependency graph as a precondition for generating a valid co-simulation.
@@
 Amalio et al.
-\cite{Amalio2016CheckingCo-simulation} investigate how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS.
+\cite{Amalio2016} investigate how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS.
 The publication's purpose is like ours, to avoid invalid co-simulation scenarios.
 Nevertheless, they achieve this by excluding co-simulation scenarios containing algebraic loops.
-Their method is realized in a co-simulation tool, INTO-SysML\cite{Miyazawa2016INtegratedModelling}.
+Their method is realized in a co-simulation tool, INTO-SysML\cite{Miyazawa2016}.
 Formal methods form the basis of their work (Theorem Proving and Model-checking).
